### 2024-06-04 segalsugawara.tex
merge

\documentclass[11pt]{amsart}

\usepackage{macros-master,amsaddr,physics}
\usepackage{mathbbol}

\addbibresource{refs}

\renewcommand{\div}{\del_{\Omega}}
\renewcommand{\PV}{\mathrm{PV}}
\renewcommand{\op}{\operatorname}

\newcommand{\sfa}{\mathsf{a}}
\newcommand{\sfb}{\mathsf{b}}
\newcommand{\sfc}{\mathsf{c}}
\newcommand{\bfa}{\mathbf{a}}
\newcommand{\bfc}{\mathbf{c}}
\newcommand{\bfk}{\mathbf{k}}

\newcommand{\fields}{\cC}
\newcommand{\Vir}{\sV\op{ir}}
\newcommand{\vir}{\lie{vir}}
\setcounter{tocdepth}{1}

%\linespread{1.2} %for editing
%\usepackage{mathpazo}

\begin{document}

\title{A higher dimensional Segal--Sugawara construction}
\author{Brian R. Williams}
\thanks{Boston University, Department of Mathematics and Statistics}
\email{bwill22@bu.edu}
\maketitle

Let $X$ be a three-dimensional complex manifold. Denote by $\Omega^1_X$ the sheaf of holomorphic one-forms and by $\del \cO_X$ the sheaf of exact holomorphic one-forms.

\section{Virasoro factorization algebras}

Let $X$ be a complex manifold of dimension $n$.
The sheaf of holomorphic vector fields has the natural structure of a sheaf of Lie algebras with bracket the Lie bracket of vector fields.
Since this bracket involves only holomorphic differential operators, it extends to a bracket on the Dolbeault complex $\Omega^{0,\bu}(X,\T_X)$ of the holomorphic tangent bundle.
This bracket endows the Dolbeault complex $\Omega^{0,\bu}(X, \T_X)$ with coefficients in the holomorphic tangent bundle with the structure of a dg Lie algebra where the differential is $\dbar$.

As defined in \cite{CG2}, a local dg Lie algebra is a $\Z$-graded complex of vector bundles whose sheaf of sections is equipped with the structure of a dg Lie algebra.
Let $\cT_X$ be the local dg Lie algebra whose underlying complex of vector bundles is
\beqn
\Omega^{0,\bu}(X, \T_X) .
\eeqn
The differential is the $\dbar$-operator associated to the holomorphic bundle $\T_X$.
The bracket is the Lie bracket of holomorphic vector fields extended to the Dolbeault complex as described above.
By Dolbeault's theorem, for $U \subset X$ a Stein open set there is a quasi-isomorphism $\cT_X(U) \simeq \op{Vect}^{hol}(U)$, the Lie algebra of holomorphic vector fields on~$U$.
When $X = \C^n$ we denote $\cT_X = \cT$ for simplicity.

%There is also the following relationship between $\cT$ and formal vector fields, which will be used subsequently.
%Let \(E \to M\) denote a $\Z$-graded vector bundle on \(M\).
%We consider the pro vector bundle of $\infty$-jets which we will denote by $j^\infty E$, see \cite{Anderson} or \cite[\S 5.6]{CostelloBook} for instance.
%The sheaf of smooth sections of this pro vector bundle carries the natural structure of a $D_M$-module.
%If $\cL = \Gamma(L)$ is a local $L_\infty$ algebra then $j^\infty L$ is a bundle of $L_\infty$ algebras.
%
%\begin{prop}
%The central charge of the
%\end{prop}
%
%\begin{prop}
%Let $X$ be a complex manifold of dimension $n$ and $\mathbf{c} \in H^{2n+2}(BU(n))$.
%Then, there exists a unique factorization algebra $X$ with the property that the restriction of it to any coordinatized open set $U$ is equivalent to the Virasoro factorization algebra $\cV\op{ir}_{\mathbf{c}}$ on $U$.
%\end{prop}
%
%As a consequence, we see that for any such central charge $\mathbf{c} \in H^{2n+2}(BU(n))$ the factorization algebra $\cV \op{ir}_{\mathbf{c}}$ is defined on the entire \textit{site} of complex manifolds of dimension $n$.

In particular, the dg Lie algebra $\cT(\C - \{0\})$ is quasi-isomorphic to holomorphic vector fields on $\C^\times$.
Replacing $\C^\times$ by the formal punctured disk gives the Witt algebra $\Vect(D^\times) = \C((z)) \del_z$ whose unique nontrivial central extension is the Virasoro Lie algebra.

For an example of a complex manifold which is not Stein consider $X = \C^n - \{0\}$.
There is an embedding of dg Lie algebras
\beqn
\Vect^{hol}(\C^n - \{0\}) \hookrightarrow \cT(\C^n - \{0\})
\eeqn
which is no longer a quasi-isomorphism.
This map does define an isomorphism in $H^0$ cohomology, but $\cT(\C^n-\{0\})$ also has cohomology in degree $(n-1)$. 
In standard coordinates, cochain representatives for this cohomology are given by expressions of the form
\beqn
\sum_j \left(\sum_{k_1 \cdots k_n} a^j_{k_1\cdots k_n} L_{\del_{z_1}^{k_1}} \cdots L_{\del_{z_n}^{k_n}} \omega_{BM}\right) \frac{\del}{\del z_j} 
\eeqn
Here $a^j_{k_1\cdots k_n}$ are constants and $\omega_{BM} \in \Omega^{0,n-1}(\C^n-\{0\})$ is the Bochner--Martinelli form which is characterized by the formula $\oint_{S^{2n-1}} \omega_{BM} \wedge \d^n z= 1$ with $S^{2n-1}$ the sphere of radius one centered at $0 \in \C^n$.

Here we make the distinction between $\C^n$ and affine space $\A^n$; the latter is the algebraic variety with functions $\C[z_1,\ldots,z_n]$.
There is an algebraic version of $\cT(\C^n - \{0\})$ with $\C^n - \{0\}$ replaced by punctured $n$-dimensional algebraic affine space $\A^n - \{0\}$.
Using a dg model for the punctured $n$-space presented in \cite{FHK}, in appendix \ref{appx:A} we construct a dg model for the derived global sections of the tangent bundle over punctured affine space which we will denote by $\lie{witt}(n)$ and refer to as the \defterm{$n$-dimensional Witt algebra}.
Here is a list of important properties of the dg Lie algebra $\lie{witt}(n)$:
\begin{itemize}
\item The underlying cochain complex $\lie{witt}(n)$ is concentrated in cohomological degrees $0,\ldots,n-1$.
\item Its cohomology is concentrated in degrees $0$ and $n-1$.
There is an inclusion of the Lie algebra of vector fields on $\A^n$ (thought of as a dg Lie algebra concentrated in degree zero):
\beqn
\lie{vect}^{alg}(n) = \C[z_1,\ldots,z_n]\{\del_{z_1},\ldots,\del_{z_n}\} \hookrightarrow 
\lie{witt}(n)
\eeqn
which induces an isomorphism in zeroth cohomology.
\item In degree $(n-1)$ \brian{finish}
\end{itemize}

The Virasoro Lie algebra is the unique nontrivial central extension of the Witt algebra $\lie{witt}(1)$.
This central extension admits an interpretation in terms of the Lie algebra cohomology of  vector fields $\lie{vect}(1)$ on the $1$-disk via the isomorphisms
\beqn
H^3(\lie{vect}(1); \C) \cong H^2(\lie{vect}(1); \Omega^1) \cong H^2(\lie{witt}(1);\C) \cong \C .
\eeqn
In the last part of this section we will construct an injective map
\beqn
H^{2n+1}(\lie{vect}(n);\C) \to H^2(\lie{witt}(n);\C), 
\eeqn
thus providing a source of central extensions for the $n$-dimensional Witt algebra.
Our construction of central extensions uses factorization algebras.

\subsection{Central extensions from local cohomology}

Such central extensions originate from the so-called local cohomology of holomorphic vector fields.
We briefly recall the definition of local cohomology from \cite{CG2}.

For $E$ a vector bundle on a manifold $M$, define the space of local functionals to be 
\beqn
\oloc(E) \define {\rm Dens}_M \otimes_{D_M} {\rm Lag} (E) .
\eeqn
Here $\op{Dens}_X$ is the bundle of densities on $M$ and $\op{Lag}(E)$ is the left $D_M$-module of Lagrangians
\beqn
\op{Lag} (E) \define \prod_{n > 0} {\rm Hom}_{C^\infty_M} \left(\op{jet} (E) , C^\infty_M\right) .
\eeqn
Concretely, a Lagrangian is a $C^\infty_M$-valued functional which only depends on jets of sections of $E$, and a local functional is a Lagrangian defined up to total derivatives.
Given a Lagrangian $L = L(\phi)$ we will denote its corresponding local functional by~$\int L(\phi)$.

If $E$ is a complex of vector bundles then $\oloc(E)$ is a sheaf of cochain complexes.
If $\cL = \Gamma(M, L)$ is a local Lie algebra then $\oloc(L[1])$ is equipped with the Chevalley--Eilenberg differential, hence giving a local version of Lie algebra cohomology.
We denote this sheaf of complexes by $C^\bu_{loc}(\cL)$.
Note that for every open set $U \subset M$ there is an embedding map
\beqn\label{eqn:localtocompact}
C^\bu_{loc}(\cL)(U) \hookrightarrow C^\bu(\cL_c(U)) 
\eeqn
where the right hand side is the Chevalley--Eilenberg complex computing the Lie algebra cohomology of compactly supported sections of $L$ on $U$.

The local cohomology for $\cL=\cT_X$ the local Lie algebra of holomorphic vector fields on a complex manifold $X$ has been characterized in \cite{BWgf}.
In the theorem below,~$Fr_X$ denotes the principal $U(n)$-bundle of unitary frames on $X$.

\begin{thm}
Let $Y_n$ be the restriction of the universal principal $U(n)$-bundle to the $2n$-skeleton of $BU(n)$.
Then
\beqn
H^\bu_{loc} (\cT(X)) \cong H^\bu(Fr_X \times^{U(n)} Y_n)[2n] .
\eeqn

In particular, when $X = \C^n$ there are isomorphisms
\beqn
H^\bu_{loc} (\cT(\C^n)) \cong H^\bu(\lie{vect}(n))[2n] \cong H^\bu(Y_n)[2n] .
\eeqn
\end{thm}

We are most interested in the degree one local cohomology.
A simple application of the Serre spectral sequence reveals that in this case 
\beqn
H^1_{loc}(\cT(\C^n)) = H^{2n+1}(\lie{vect}(n)) = H^{2n+2} (BU(n)) .
\eeqn
So, degree one local cohomology classes for $\cT(\C^n)$ are in one-to-one correspondence with degree $2n+2$ polynomials in the universal Chern classes $c_1,\ldots,c_n$.

\subsection{Higher Virasoro Lie algebras}

At this point, we can see how central extensions of the $n$-dimensional Witt algebra appear.
We have pointed out in \eqref{eqn:localtocompact} how local cohomology classes of a local Lie algebra $\cL$ supported on $U$ determine Lie algebra cohomology classes for the Lie algebra of compactly supported sections $\cL_c(U)$.
We recall in appendix \cite{appx:model}, the $n$-dimensional Witt algebra $\lie{witt}(n)$ admits a homomorphism of dg Lie algebras
\beqn
j \colon \lie{witt}(n) \hookrightarrow \Omega^{0,\bu} (\C^n - \{0\}, \T) = \cT(\C^n - \{0\}),
\eeqn
which has the property that in cohomology $H^\bu(j)$ is a dense embedding of topological vector spaces.

We consider the local dg Lie algebra $\Omega^\bu(\R) \otimes \lie{witt}(n)$ defined on the manifold $\R$.
The differential is 
\beqn
\d_{dR} \otimes \id + \id \otimes \dbar_{\lie{witt}},
\eeqn
where the first term is the de Rham operator on $\R$ and the second is the internal differential to the dg Lie algebra $\lie{witt}(n)$.
The bracket is
\beqn\label{eqn:tensorbracket}
[\eta \otimes X, \theta \otimes Y] = (\eta \theta) \otimes [X,Y] , \quad \eta,\theta \in \Omega^\bu(\R), \;\; X,Y \in \lie{witt}(n)
\eeqn
where $[-,-]$ is the Lie bracket in $\lie{witt}(n)$.
Using $j$ we will construct a map (up to homotopy) of the form
\beqn
\til j \colon \Omega^\bu_c (\R) \otimes \lie{witt}(n) \to \cT_c (\C^n - 0)
\eeqn
as follows.

Introduce the following local dg Lie algebra $\cL_{log}$ on $\R$ which is the same underlying complex of vector bundles as $\Omega^\bu (\R) \otimes  \lie{witt}(n)$, except with the Lie bracket defined by the formulas
\begin{align*}
\left[f \otimes \alpha \frac{\del}{\del z_i} , g \otimes \beta \frac{\del}{\del z_j}\right]_{\cL_{log}} & = fg \otimes \left[\alpha \frac{\del}{\del z_i}, \beta \frac{\del}{\del z_j}\right] +  f g' \otimes \lambda_i \alpha \beta \frac{\del}{\del z_j} - (-1)^{\alpha \beta} f' g \otimes \lambda_j \alpha \beta  \frac{\del}{\del z_i}  \\
\left[f \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j}\right]_{\cL_{log}} & = fg \d t \otimes \left[\alpha \frac{\del}{\del z_i}, \beta \frac{\del}{\del z_j}\right] + f g' \d t \otimes \lambda_i \alpha \beta \frac{\del}{\del z_j} - (-1)^{\alpha \beta} f' g \d t \otimes \lambda_j \alpha \beta  \frac{\del}{\del z_i} \\
& + fg \otimes \alpha (\dbar \lambda_i) \beta \frac{\del}{\del z_j} , \\ 
\left[f \d t \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j}\right]_{\cL_{log}} & = 0 .
\end{align*}
Here $\alpha, \beta \in \sfA_n$, $f,g \in C^\infty(\R)$, and we have used the notation from the appendix $\lambda_i = \frac{\zbar_i}{z \zbar}$.\footnote{When $n=1$ we set $\lambda = \frac{1}{z}$, and the brackets in $\cL_{log}$ simplify to
\[
[f \otimes L_n, g \otimes L_m ] = (m-n) fg \otimes L_{n+m} + (fg' - f'g) \otimes L_{n+m} ,
\] 
for example.  }
Notice that the first terms on the right hand sides of the expressions above agree with the Lie bracket in \eqref{eqn:tensorbracket}.
We also remark that the second line of the second equation is identically zero when $n = 1$.

We now construct an $L_\infty$ equivalence 
\beqn
\Phi = (\Phi^{(1)}, \Phi^{(2)}) \colon \Omega^\bu(\R) \otimes \lie{witt}(n) \rightsquigarrow \cL_{log} .
\eeqn
Let $\Phi^{(1)} = \id$ and 
\begin{align*}
\Phi^{(2)}\left(f \d t\otimes \alpha \frac{\del}{\del z_i} , g \otimes \beta \frac{\del}{\del z_j} \right) & = fg \otimes \lambda_i \alpha \beta \frac{\del}{\del z_j} \\
\Phi^{(2)}\left(f \d t \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j} \right) & = fg \d t \otimes \alpha \beta \left(\lambda_i \frac{\del}{\del z_j} + \lambda_j \frac{\del}{\del z_i} \right) .
\end{align*}
To see that $\Phi = (\Phi^{(1)}, \Phi^{(2)})$ is an $L_\infty$ morphism we observe the following relations:
\begin{multline}
\Phi^{(2)}\left(\d f \otimes \alpha \frac{\del}{\del z_i} , g \otimes \beta \frac{\del}{\del z_j}\right) - (-1)^{\alpha} \Phi^{(2)}\left(f \otimes \alpha \frac{\del}{\del z_i} , \d g \otimes \beta \frac{\del}{\del z_j}\right) \\ = f g' \otimes \lambda_i \alpha \beta \frac{\del}{\del z_j} - (-1)^{\alpha \beta} f' g \otimes \lambda_j \alpha \beta  \frac{\del}{\del z_i} ,
\end{multline}
and
\begin{multline}
- (\d + \dbar_{\lie{witt}}) \Phi^{(2)}\left(f \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j}\right) + \Phi^{(2)}\left(\d f \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j}\right) \\ + \Phi^{(2)}\left(f \otimes \dbar \alpha \frac{\del}{\del z_i} , g \d t \otimes \beta \frac{\del}{\del z_j}\right) - (-1)^\alpha \Phi^{(2)}\left(f \otimes \alpha \frac{\del}{\del z_i} , g \d t \otimes \dbar \beta \frac{\del}{\del z_j}\right)  \\ = f g' \d t \otimes \lambda_i \alpha \beta \frac{\del}{\del z_j} - (-1)^{\alpha \beta} f' g \d t \otimes \lambda_j \alpha \beta  \frac{\del}{\del z_i} + fg \otimes \alpha (\dbar \lambda_i) \beta \frac{\del}{\del z_j} ,
\end{multline}
where $f,g \in C^\infty(\R)$ and $\alpha \frac{\del}{\del z_i}, \beta \frac{\del}{\del z_j} \in \lie{witt}(n)$.

The $L_\infty$-map $\Phi$ clearly is given by differential operators, so it defines a homomorphism of \textit{local} dg Lie algebras on the manifold $\R$.
We have shown the following.

\begin{prop}
The local dg Lie algebras $\Omega^\bu_\R \otimes \lie{witt}(n)$ and $\cL_{log}$ are $L_\infty$-equivalent.
In particular, the map $\Phi$ defines a quasi-isomorphism of commutative dg algebras
\beqn
\Phi^* \colon C^\bu(\cL_{log,c}(\R)) \xto{\simeq} C^\bu(\Omega^{\bu}_c(\R) \otimes \lie{witt}(n))
\eeqn
which restricts to a quasi-isomorphism
\beqn
\Phi^* \colon C_{loc}^\bu(\cL_{log}) \xto{\simeq} C_{loc}^\bu(\Omega^\bu(\R) \otimes \lie{witt}(n)) .
\eeqn
\end{prop}

Next we define a homomorphism of dg Lie algebras
\beqn
\til j \colon \cL_{log}(\R) \to \cT(\C^n - \{0\})
\eeqn
by the formulas
\begin{align*}
\til j \left(f(t) \otimes \alpha \frac{\del}{\del z_i}\right) & = f(\log z \zbar) \alpha \frac{\del}{\del z_i} \\
\til j \left(f(t) \d t \otimes \alpha \frac{\del}{\del z_i}\right) & = f(\log z \zbar) \dbar (\log z \zbar )\alpha \frac{\del}{\del z_i} .
\end{align*}
It is immediate to verify that this is a cochain map and it is compatible with Lie brackets. (In fact, the complicated form of the Lie bracket defining $\cL_{log}$ was motivated by this embedding.)

\begin{lem}
The cochain map
\beqn
\til j^* \colon C^\bu (\cT_c(\C^n - 0)) \to C^\bu \left(\cL_c(\R) \right)
\eeqn
given by restriction along $\til j$ preserves local cochains. 
Furthermore, if $\phi$ is a local cochain for $\cT(\C^n - 0)$ then $\til j^* \phi$ is translation invariant as a local cochain on $\R$. 
Thus, $\til j$ determines a homomorphism
\beqn
\til j^* \colon C^\bu_{loc}(\cT(\C^n-0)) \to C^\bu_{loc}\left(\cL_{log}\right)^{\R} .
\eeqn
\end{lem}

Finally, we have the following relationship between translation invariant local cohomology classes for the local Lie algebra $\Omega^\bu \otimes \lie{witt}(n)$ and Lie algebra cohomology classes for $\lie{witt}(n)$.

\begin{lem}
Let $\lie{g}$ be any dg Lie algebra and consider the resulting local Lie algebra $\Omega^\bu_\R \otimes \lie{g}$ on the manifold $\R$.
Then
\beqn
H_{loc}^\bu\left(\Omega^\bu_\R \otimes \lie{g}\right)^\R \cong H^{\bu+1}(\lie{g}) .
\eeqn
\end{lem}

Combining all of these results, we see that the composition
\beqn
C_{loc}^\bu (\cT) \xto{\til j^*} C^\bu_{loc}(\cL_{log})^{\R} \xto{\Phi^*} C^\bu_{loc}(\Omega^\bu_\R \otimes \lie{witt}(n))^{\R} 
\eeqn
defines, at the level of degree one cohomology, a linear map
\beqn
H^{2n+2}(BU(n)) \to H^{2} (\lie{witt}(n)) .
\eeqn

\begin{dfn}
Every degree $2n+2$ polynomial $\bfc \in H^{2n+2}(BU(n))$ in the universal Chern classes $c_1,\ldots,c_n$ determines a central extension of the dg Lie algebra $\lie{witt}(n)$.
We denote this central extension
\beqn
0 \to \C \to \lie{vir}_{\bfc}(n) \to \lie{witt}(n) \to 0 ,
\eeqn
and refer to it as the $n$-dimensional Virasoro Lie algebra of central charge $\bfc$.
\end{dfn}

We can be explicit about the correspondence between universal characteristic classes and central extensions of $\lie{witt}(n)$ for small values of $n$.
When $n = 1$ we have $\lie{witt}(1) = \C[z^\pm] \del_z$.
Following \cite{BWgf}, the class $c_1^2 \in H^4(BU(1))$ corresponds to the local cocycle
\beqn
\int_{\C} J \mu \del J \mu
\eeqn
where $\mu = \alpha (z,\zbar) \del_z$ is a section of $\cT$ and $J \mu = \del_z \alpha(z,\zbar)$.
Following the above restrictions and equivalences, we see that this corresponds to the usual Virasoro cocycle
\beqn
(f \del_z, g \del_z) \mapsto \op{Res}_z f'(z) g''(z) \d z , \quad f,g \in \C[z^\pm]
\eeqn
Of course, in this case, all Virasoro Lie algebras corresponding to a nonzero central charge are isomorphic.

Next consider $n=2$, so that the possible central charges are linear combinations of $c_1^3, c_1 c_2 \in H^4(BU(2))$.
For simplicity, consider the class $c_1^3$.
It is shown in \cite{BWgf} that a local cocycle representative corresponding to this class is a multiple of
\beqn
\int_{\C^2} \op{Tr}(J \mu) \del \op{Tr}(J \mu) \del \op{Tr}(J \mu) .
\eeqn
The corresponding degree two cocycle of $\lie{witt}(2)$ is
\beqn
c_1^3 \colon (\mu_0,\mu_1,\mu_2) \mapsto \op{Res}_z \op{Tr}(J \mu_0) \del \op{Tr}(J \mu_1) \del \op{Tr}(J \mu_2)
\eeqn
where $\mu_i \in \lie{witt}(2)$.
Here $\op{Res}_z \colon H^1(\sfA_2) \to \C$ is the higher residue as defined in appendix \ref{appx:model}.
We observe that sense the residue carries degree one, and that the cocycle above is of polynomial degree three, that $c_1^3$ of $\lie{witt}(2)$ is of total degree two as desired.
As another example, the $2$-dimensional Virasoro algebra of central charge $c_1\op{ch}_2 = \frac12 (c_1^3 - 2 c_1 c_2)$ is determined by the degree two cocycle
\beqn
c_1 \ch_2 \colon (\mu_0,\mu_1,\mu_2) \mapsto \op{Res}_z \op{Tr}(J \mu_0) \op{Tr}(\del J \mu_1 \del J \mu_2) + \cdots ,
\eeqn
where the $\cdots$ denote appropriate anti-symmetrization.

\subsection{Enveloping factorization algebras}

Let $\cE$ be a vector bundle on a manifold $M$ and let $\cE_c$ denote its cosheaf of compactly supported sections.
It is shown how the assignment of the graded vector space
\beqn
\Sym \, \cE_c(U) = \oplus_{n \geq 0} \Gamma_c(U, \Sym^n E)
\eeqn
to an open set $U \subset M$ assemble into a factorization algebra on $M$.

Now, let $\cL = \Gamma(M,L)$ be a local dg Lie algebra on a manifold $M$.
Applying the above construction to $E[-1] = L$ gives rise to the factorization algebra which assigns to an open set $U \subset M$ the graded vector space 
\beqn
\Sym \, \cL_c (U) [1] .
\eeqn
For each open set $U$ this graded vector space is equipped with a differential $\d_{CE}$ whose cohomology computes the Lie algebra homology of the dg Lie algebra $\cL_c(U)$.
The resulting dg factorization algebra is denoted by $C_\bu(\cL_c)$ and is called the \defterm{enveloping factorization algebra} associated to the local Lie algebra $\cL$.

Next, we recall shifted central extensions of dg Lie algebras.
Suppose that $(\lie{g},\d_{\lie{g}})$ is a dg Lie algebra and consider its Chevalley--Eilenberg complex $C^\bu(\lie{g};\C)$ computing its Lie algebra cohomology.
This complex is bigraded with the first grading being the internal degree to $\lie{g}$ and the second grading being the graded polynomial degree.
Suppose $\phi$ is a cochain of totalized degree $k$; we assume that it is concentrated in graded polynomial degree $\geq 1$.
Then $\phi$ can be expressed as
\beqn
\phi = \phi_1 + \phi_2 + \cdots 
\eeqn
where $\phi_i$ carries polynomial degree $i$ and internal cohomological degree $k-i$.

Suppose now that $\phi$ is a cocycle, meaning it is closed for the totalized Chevalley--Eilenberg differential.
It then defines an $L_\infty$-algebra central extension
\beqn
0 \to \C K [k-2] \to  \til{\lie{g}} \to \lie{g} \to 0
\eeqn
with $\ell$-ary brackets defined by
\begin{itemize}
\item $\ell = 1$
The differential is $[-]_1 = \d_{\lie{g}} + K \phi_1$ where $K \phi_1 \colon \lie{g} \to \C K$ is the first term in the expansion of $\phi$.
\item $\ell=2$. 
The bracket is $[x,y] = [x,y]_{\lie{g}} + K \phi_2(x,y)$, where $x,y \in \lie{g}$.
\item $\ell > 2$.
The $\ell$-ary bracket is
\beqn
[x_1,\ldots,x_\ell]_\ell = K \phi_\ell(x_1,\ldots,x_\ell) .
\eeqn
\end{itemize}
The central summand of $\til{\lie{g}}$ appears in cohomological degree $2-k$. 
The Chevalley--Eilenberg complex computing Lie algebra homology $C_\bu(\til{\lie{g}})$ is a dg $\C[K]$-module where~$K$ carries cohomological degree $k-1$.

For any local Lie algebra $\cL$ on $M$ we recalled how to construct its enveloping factorization algebra $C_\bu(\cL_c)$ on $M$.
Given a local cocycle $\phi$ of cohomological degree $+1$, there is a $\phi$-twisted version of the enveloping factorization algebra $C_\bu^\phi(\cL_c)$ which we will now recall. 
For more details we refer to \cite[\S 11]{CG2}.

For every open set $U \subset M$ there is a cochain map
\beqn
C^\bu_{loc}(\cL)(U) \to C^\bu(\cL_c(U))
\eeqn
So local cocycles define cocycles for the cosheaf of dg Lie algebras $U \mapsto \cL_c(U)$.
In particular, $\phi$ defines a precosheaf of $L_\infty$ algebras
\beqn
0 \to \ul \C[-1] \to \til \cL_c \to \cL_c \to 0 ,
\eeqn
where $\ul \C[-1]$ is the constant precosheaf which assigns $\C[-1]$ in degree $+1$ to every open set.
In \cite{CG2} it is shown that the assignment
\beqn
U \subset M \mapsto C_\bu(\til \cL_c (U)) 
\eeqn
defines a factorization algebra on $M$ in $\C[K]$-modules (where, now $K$ has degree zero).
This is the \defterm{$\phi$-twisted} factorization enveloping algebra which we will denote by $C^\phi_\bu(\cL_c)$.
It has the property that the $K=0$ specialization is the (untwisted) enveloping factorization algebra $C_\bu(\cL_c)$.

\subsection{Virasoro factorization algebras}

\begin{dfn}\label{dfn:vir}
Fix a complex dimension $n$ and let
\beqn
\bfc \in H^{2n+2}(BU(n)) \cong H^1_{loc}(\cT_{\C^n}) .
\eeqn
The \defterm{Virasoro factorization algebra} on $\C^n$ is the twisted enveloping factorization algebra of $\cT_{\C^n}$ corresponding to this local cohomology class
\beqn
\Vir_{\bfc} \define C_\bu^{\bfc}(\cT_{\C^n,c})|_{K=1} .
\eeqn
\end{dfn}

The primary motivation for this terminology is the main result of \cite{BWvir} which exhibits the relationship between the $n=1$ Virasoro factorization algebra and the Virasoro vertex algebra.
Recall that there is a systematic relationship between (algebro-geometric) factorization algebras on $M = \C$ and vertex algebras \cite{BD}.
In \cite{CG1}, this relationship is made precise in the form of a functor $\VV$ from a certain category of `tame' holomorphic factorization algebras on $M = \C$ to the category of ($\Z$-graded) vertex algebras.

\begin{thm}[\cite{BWvir}]
For $c \in \C$ consider the class
\beqn
\frac{c}{24} c_1^2 \in H^4(BU(1)) 
\eeqn
and the associated Virasoro factorization algebra $\Vir_{c c_1^2/24}$ on $\C$.
This is a tame holomorphic factorization algebra and its associated vertex algebra $\VV(\Vir_{c c_1^2/24})$ is equivalent to the Virasoro vertex algebra of central charge $c$.
\end{thm}

We now arrive at the main definition of this section.
To set it up, we recall some notions.

\begin{dfn}
A \textit{holomorphic structure} on a factorization algebra $\cF$ on $\C^n$ of central $\bfc \in H^{2n+2}(BU(n))$ is a map of factorization algebras
\beqn
\bT \colon \Vir_{\bfc} \to \cF .
\eeqn
\end{dfn}

\subsection{Relationship to higher Virasoro Lie algebras}

In this section we show how to produce central extensions of $\lie{witt}(n)$ using factorization algebras.
Let $\bfc$ be as in definition \ref{dfn:vir} and consider the associated Virasoro factorization algebra on $\C^n$ by $\Vir_{\sfc}$.

\begin{lem}
There is an $T^n = S^1\times \cdots \times S^1$-action on the factorization algebra $\Vir_{\sfc}$ which covers the $T^n$ action on $\C^n$ rotating each coordinate plane.
\end{lem}
\begin{proof}
There's a natural action of $T^n$ on the Dolbeault complex
\beqn
\cT = \Omega^{0,\bu}(\C^n, T)
\eeqn
induced by pullback of forms.
Since rotation is holomorphic, this is equivariant for the $\dbar$-operator and is compatible with the Lie bracket of vector fields.
This implies that there is a $T^n$ action on the untwisted factorization enveloping algebra $\Vir_{0}$.

For the case $\bfc \ne 0$ we need to see that the corresponding local functional is invariant under such rotations.
If $\sum_i g_i(z) \del_{z_i}$ is a vector field then rotation by $\lambda \in S^1$, the $i$th circle, gives the vector field $\sum_i \lambda_i^{-1} g_i(\lambda_i z) \del_{z_i}$ \brian{A little stuck} 
\end{proof}

We restrict the factorization algebra $\Vir_{\bfc} |_{\C^n - \{0\}}$ to define a factorization algebra the punctured plane $\C^n - \{0\}$.
Let 
\beqn
\rho \colon \C^n - \{0\} \to \R_+
\eeqn
be the square of the radius $(z_1,\ldots,z_n) \mapsto |z_1|^2 + \cdots + |z_n|^2$, and consider the resulting factorization algebra 
\beqn
\rho_* \left(\Vir_{\bfc} |_{\C^n - \{0\}}\right)
\eeqn
on $\R_+$ whose value on an open interval $I \subset \R_+$ is the value of $\Vir_{\bfc}$ on the open annular region $\rho^{-1}(I) \subset \C^n$.

For $\bfk = (k_1,\ldots,k_n)\in \Z^n$, denote by $\cF_{\bfc}^{(\bfk)}$ the $\bfk$-eigenspace for this $T^n$ action.
Define the factorization algebra
\beqn
\cF_{\bfc} \define \oplus_{\bfk \in \Z^m} \cF_{\bfc}^{(\bfk)} .
\eeqn

\begin{prop}
The factorization algebra $\cF_{\bfc}$ is a locally constant factorization algebra on~$\R_+$. 
Its associated $\mathbb{E}_1$-algebra is the $\mathbb{E}_1$-enveloping algebra of the dg Lie algebra $\vir_{\bfc}$ given by the central extension
\beqn
0 \to \C \to \lie{vir}_{\bfc} (n) \to \lie{witt}(n) \to 0
\eeqn
determined by the degree two cocycle which is the image of $\bfc$ 
\beqn
H^1_{loc}(\cT
\eeqn
\end{prop}

\subsubsection{No central extension}

\subsubsection{Turning on the central extension}

\section{Deligne truncations of de Rham cohomology}

\subsection{Closed forms in complex geometry}

If $X$ is a complex manifold, and $k$ a non-negative integer, let 
\beqn
\Omega^{k,\bu}(X) = \Omega^{0,\bu}(X, \wedge^p \T_X)
\eeqn
be the graded vector space of $(k,\bu)$ forms on $X$, where the space of $(p,q)$ forms sit in cohomological degree $q$.
This graded vector space is equipped with the natural $\dbar$ operator turning $\Omega^{p,\bu}(X)$ into a dg $\Omega^{0,\bu}(X)$-module.

For $U \subset X$ any open set, we can also consider the complex of $(p,\bu)$-forms supported on $U$.
In fact, $U \mapsto \Omega^{p,\bu}(U)$ defines a sheaf of cochain complex which by Dolbeault's theorem is quasi-isomorphic to the sheaf of holomorphic $p$-forms $\Omega^{p,hol}_X$.

The holomorphic de Rham operator is of the form
\beqn
\del \colon \Omega^{p,\bu}_X \to \Omega^{p+1,\bu}_X .
\eeqn
The total complex
\beqn
\left(\Omega^{\bu,\bu}_X , \dbar + \del\right) = \left(\oplus_{p} \Omega^{p,\bu}_X [-p], \dbar + \del \right) 
\eeqn
is quasi-isomorphic to the (complexified) smooth de Rham complex $\Omega^\bu_X$ equipped with the smooth de Rham differential.

We are interested in a truncation of the full de Rham complex.
Define the following sheaf of cochain complexes 
\beqn
\Omega^{\geq p, \bu}_X \define \left(\Omega^{p,\bu} \xto{\del} \Omega^{p+1,\bu}[-1] \xto{\del} \cdots \right) 
\eeqn
where the $\dbar$ operator is left implicit.
Explicitly, a section of this sheaf of cohomological degree $k$ is a sum of $(p',q)$ forms where $p' + q = k$ and $p' \geq p$.

\begin{prop}
The complex of sheaves $\Omega^{\geq p, \bu}_X$ is a free resolution of the sheaf of $\del$-closed, holomorphic $p$-forms on $X$.
\end{prop}

\begin{dfn}
Let $X$ be an $(2n+1)$-dimensional complex manifold, define $\cB_X$ to be the sheaf of cochain complexes 
\beqn
\fields_X \define \Omega^{\geq n+1, \bu}_X [n] .
\eeqn
This is the complex resolving the sheaf of closed $(n+1)$-forms placed in cohomological degree $-n$.
\end{dfn}

\section{Free-field factorization algebras}

\subsection{Weyl factorization algebras}
\label{ss:weyl}

Suppose that $V$ is a symplectic vector space with symplectic form $\omega$.
The Heisenberg Lie algebra is the central extension of $V$ (viewed as an abelian Lie algebra) defined by $\omega$, viewed as a $2$-cocycle.
The non-degeneracy of $\omega$ is not important for this construction, any $\omega \in \wedge^2 V^*$ defines a central extension of~$V$.
The Weyl algebra associated to $V$ is the universal enveloping algebra of this central extension where the central parameter is set to the unit.
In this section we review a factorization algebra enhancement of this construction.

Let $(E,Q)$ be a complex of vector bundles on a manifold $M$ and consider the precosheaf of commutative algebras
\beqn
\Sym(\cE_c) \colon U \subset M \mapsto \Sym(\cE_c(U)) .
\eeqn
If $\sqcup U_i \hookrightarrow V$ is a collection of disjoint open sets embedded inside of another open set then multiplication on this precosheaf determines a morphism
\beqn\label{eqn:freefactmaps}
\otimes \Sym(\cE_c(U_i)) \to \Sym(\cE_c(V)) .
\eeqn
By \cite[??]{CG1} this endows $\Sym(\cE_c)$ with the structure of a factorization algebra.
We recalled in section \ref{sec:enveloping} how a deformation of this in the case that $E[-1] = L$ is a local Lie algebra on $M$ gives rise to the enveloping factorization algebra associated to $L$.

A generalization of this construction involves the data of a local functional 
\beqn
\omega \in \oloc(E)
\eeqn
of cohomological degree $+1$ which satisfies $Q \omega = 0$.
For each open set $U \subset M$, there is a natural inclusion $\cO_{loc}(E) (U) \hookrightarrow \cO(\cE_c(U))$ so that we can view $\omega$ as a functional
\beqn
\omega \colon \Sym(\cE_c(U)) \to \C .
\eeqn 
Let $\omega_{[k]}$ be the $k$th homogenous part of $\omega$ so that 
\beqn
\omega_{[k]} \colon \Sym^k (\cE_c(U)) \to \C
\eeqn
We extend $\omega$ to a map $Q_{\omega_{[k]}} \colon \Sym(\cE_c(U)) \to \Sym(\cE_c(U))[1]$ of cohomological degree one by declaring that for each $k$ $\omega_{[k]}$  \brian{finish} and we let $Q_{\omega} = \sum Q_{\omega_{[k]}}$.

\begin{prop}[\cite{CG1}]
Let $K$ be a parameter of cohomological degree zero.
The assignment
\beqn
\cW_{E,\omega} \colon U \subset M \mapsto \left(\Sym(\cE_c(U))[K], Q + K Q_\omega \right)
\eeqn
has the structure of a factorization algebra in the category of dg $\C[K]$-modules with structure maps \eqref{eqn:freefactmaps}.
We refer to this as the \defterm{Weyl factorization algebra} associated to $E,\omega$.
\end{prop}

\begin{eg}
Let $V$ be an ordinary vector space and $\omega_V \in \wedge^2 V^*$ a symplectic form.
Consider the complex of vector bundles on the real line
\beqn
\Omega^0(\R) \otimes V \xto{\d \otimes \id} \Omega^1 (\R) \otimes V ,
\eeqn
where $\Omega^0$ is placed in degree zero.
Then $\omega = \int_\R \omega_V$ defines a local functional of degree $+1$ on this complex which satisfies~$\d \omega = 0$.
The Weyl factorization algebra in this case is locally constant on $\R$ and its associated $\EE_1$-algebra is equivalent to the ordinary Weyl associative algebra on the symplectic vector space~$V$.
More generally, if $V$ is an $n$-shifted symplectic vector space then the corresponding local functional on the complex of vector bundles $\Omega^\bu(\R^n) \otimes V$ is also degree $+1$.
The associated Weyl factorization algebra is locally constant and is a $\mathbb{E}_n$-algebra analog of the ordinary Weyl algebra.
\end{eg}

\subsection{Quantization in the BV formalism}

The Weyl algebra is the result of deformation quantization of the simplest symplectic space.
In this section we show that the Weyl factorization algebra is also the result of a sort of quantization in the context of the Batalin--Vilkovisky (BV) formalism.
In the case that $\omega \in \oloc(E)$ arises from a bundle morphism
\beqn\label{eqn:nondeg}
\omega \colon E \otimes E \to \op{Dens}_M
\eeqn
which is fiberwise non-degenerate then the data $(E,\omega,Q)$ defines a free BV theory in the sense of \cite[definition 4.2.0.2]{CG2}.
In this case, the associated factorization algebra of quantum observables is quasi-isomorphic to the Weyl factorization algebra \cite[Proposition 8.1.3.1]{CG2}.
In this section, we introduce a generalization of the notion of a free BV theory whose BV quantization is captured by the Weyl factorization algebras of the previous section.

First, we recall some notation.
The $!$-dual (or Serre dual) of a vector bundle $E$ is the bundle $E^! = E^* \otimes \op{Dens}_M$ where $E^*$ is the ordinary dual vector bundle and $\op{Dens}_M$ is the density bundle on $M$ (an orientation is an isomorphism $\op{Dens}_M \cong \wedge^n \T_M^*$).
The linear dual of $\cE = \Gamma(M,E)$ is $\br \cE^!_c = \br \Gamma_c(M, E^!)$ where $\br \Gamma_c$ denotes compactly supported distributional sections.
There is hence a natural map of cosheaves
\beqn
\cE^!_c = \Gamma_c(M,E^!) \hookrightarrow \cE^\vee ,
\eeqn
which includes the smooth (non-distributional) sections.
If $E$ is an elliptic complex of vector bundles then the above map is a quasi-isomorphism.
In particular, one has the following.

\begin{prop}[see theorem 5.4.0.1 of \cite{CG}]
Let $(E,Q)$ be an elliptic complex of vector bundles.
Then the inclusion
\beqn
\left(\Sym(\cE_c), Q\right) \hookrightarrow \left(\cO(\cE^!) , Q\right)
\eeqn
is an equivalence of factorization algebras.
If $\omega \in \oloc(E)$ is non-degenerate of the form \eqref{eqn:nondeg} then this is an equivalence of $\PP_0$-factorization algebras.
\end{prop}

The following paragraph is a review of ideas that appear in \cite{PavelPoisson}.
Let $(P,\d)$ be a cochain complex. Consider the following commutative dg algebra
\beqn
\op{Pol}(P,-1) \define \Sym(P^*) \otimes \Sym(P) .
\eeqn
We consider two additional gradings on this algebra.
The first is by polynomial degree where $P^*$ carries weight $+1$.
The second endows $P$ with weight $+1$, we refer to this as the weight grading.
The (shifted) Schouten bracket $[-,-]_{Sch}$ endows this with the structure of a graded (unshifted) Lie algebra. 
It is defined on this usual way on vector fields $\Sym(P^*) \otimes P \subset \op{Pol}(P,-1)$ and extended to the full algebra by the condition that it is a graded derivation with respect to multiplication.
A $(-1)$-shifted Poisson structure on $P$ is an element
\beqn
\pi \in \op{Pol}(P,-1) [1]
\eeqn
of cohomological degree $+1$, concentrated in weights $\geq 2$, which satisfies the Maurer--Cartan equation
\beqn
\d \pi + \frac12 [\pi,\pi]_{Sch} = 0 .
\eeqn
Such an element can be decomposed $\pi = \pi_2 + \pi_3 + \cdots$ where $\pi_k$ has weight $k$ with respect to the weight grading.
Contraction with $\pi$ endows the commutative dg algebra $\cO(P)$ with a sequence of brackets $\{-,-\}, \{-,-\}_3, \ldots$ endowing it with the structure of a \textit{homotopy $\PP_0$ algebra} \cite{??}.
In this paper we only consider $(-1)$-shifted Poisson structures with weight $2$, hence $\cO(P)$ is an ordinary, or strict, $\PP_0$-algebra with bracket we denote by $\{-,-\}$.
In physics, this is the BV anti-bracket.

Given such a $\pi$ we construct an operator $\triangle_\pi$ acting on $\cO(P)$ defined as follows.
Let 
\beqn
\triangle_{\pi_k} \colon \Sym^k(P^*) \to \C 
\eeqn
be contraction with $\pi_k$; extend this to ... \brian{finish}

\begin{prop}
Let $(P,\d)$ be a cochain complex and suppose that $\pi$ is a constant coefficient $(-1)$-shifted Poisson structure on $P$.
Then $\triangle_\pi \circ \triangle_\pi = 0$.
\brian{BD quantization??}
\end{prop}

\begin{dfn}\label{dfn:free}
A \defterm{free BV theory of Poisson type} on a manifold $M$ is an elliptic complex of vector bundles $(\cE,Q)$ on $M$ together with a local, constant coefficient, $(-1)$-shifted local Poisson tensor
\beqn
\pi \in ??
\eeqn
which satisfies $Q \pi = 0$.
\end{dfn}

Now we return to the relationship to Weyl factorization algebras.
A $\PP_0$-structure $\pi$ as in definition \eqref{dfn:free} 
The factorization algebra of classical observables of a free BV theory of Poisson type is simply $\cO(\cE) = \Sym\left(\cE^\vee\right)$.

\subsection{The higher-dimensional free boson}

Let $X$ be a $(2n+1)$-dimensional complex manifold and consider the complex of vector bundle $\cA = \cA_X$ from definition \ref{dfn:??}.
As a graded vector bundle recall that $\cA = \Omega^{\leq n, \bu} [n+1]$.

Define the following pairing on the complex of vector bundles $\cA_{X,c}$:
\beqn
\omega(\beta, \gamma) = \int_X \beta \del \gamma .
\eeqn
One can immediately check that $\omega$ carries degree $+1$ as required for the construction of the Weyl factorization algebra.
Importantly, for each open $U \subset X$ the pairing $\omega$ defines the operator $\triangle$ acting on 
\beqn
\Sym \left(\cA_c(U) [n+1] \right)
\eeqn
by the following rules:
\begin{itemize}
\item If $\Phi \in \Sym^{\leq 1}$ then $\triangle \Phi = 0$.
\item If $\Phi = \beta \gamma \in \Sym^2$ then define
\beqn
\triangle (\beta \gamma) = \omega|_{U} (\beta, \gamma) = \int_U \beta \del \gamma .
\eeqn
\item \brian{FINISH}.
\end{itemize}

\begin{dfn}
Let $X$ be a complex manifold of dimension $2n+1$.
The \defterm{free boson factorization algebra} on $X$ is
\beqn
\cF \define \left(\Sym \left(\Omega^{\leq n}_{X,c} [n+1] \right) \; , \; Q + \triangle \right) ,
\eeqn
where $\triangle$ is defined as in items (1)-(3) above.
In the notation of section \ref{ss:weyl}, $\cF = \cW_{\cA,\omega}$.
\end{dfn}

Finally, we frame this factorization algebra as a quantization of a free BV theory.
First, let
\beqn
\delta_\Delta \in \br\Omega^{2n+1,2n+1}(X \times X)
\eeqn
be the $\delta$-distribution along the diagonal $X \hookrightarrow X \times X$.
This is a distributional form of Hodge type $(2n+1,2n+1)$ on $X \times X$.
Applying the holomorphic de Rham operator along one of the directions yields a distribution
\beqn\label{eqn:fullbcov}
(\del \otimes \id) \delta_{\Delta} \in \br\Omega^{2n+2,2n+1}(X \times X) .
\eeqn
This is the full BCOV propagator as introduced in \cite{CLbcov1,CLbcov2}.
We are only interested in a particular component of this distributional section.
There is a K\"unneth decomposition
\beqn
\br\Omega^{2n+2,2n+1}(X \times X) = \bigoplus_{k=1}^{2n+1} C^k ,
\eeqn
where $C^k = \oplus_{q+q'=2n+1} \br \Omega^{k,q}(X) \hotimes \br \Omega^{2n+2-k,q'}(X)$.
We let
\beqn\label{eqn:poisson1}
\pi \in C^{n+1} = \bigoplus_{q+q'=2n+1} \br \Omega^{n+1,q}(X) \hotimes \br \Omega^{n+1,q'}(X) 
\eeqn
be the projection of \eqref{eqn:fullbcov} to the component $C^{n+1}$.

\begin{lem}
This $\pi$ determines a section
\beqn
\pi \in \br \fields_X \hotimes \br \fields_X [-1]
\eeqn
which satisfies $\d_{\fields} \pi = 0$.
Thus $\pi$ endows $\fields$ with the structure of a free BV theory of Poisson type.
\end{lem}

\begin{prop}
Let $X$ be a complex manifold of dimension $2n+1$.
The free boson factorization algebra $\cF$ is the BV quantization of the free BV theory of Poisson type whose fields are
\beqn
\fields = \Omega^{\geq n+1, \bu}_X [n]
\eeqn
and whose $(-1)$-shifted local Poisson structure is $\pi$ as in \eqref{eqn:poisson1}.
More precisely, there is an equivalence of factorization algebras
\beqn
\cF \xto{\simeq} \Obs^q (\fields)|_{\hbar = 1} .
\eeqn
\end{prop}

\begin{prop}[\cite{GRWcs}]
This free theory of Poisson type is a boundary theory for $(4n+3)$-dimensional abelian $(2n+1)$-form Chern--Simons theory on the product manifold $X \times \R_+$.
The boundary factorization algebra of quantum observables is equivalent to $\cF$.
\end{prop}

\section{Segal--Sugawara construction}

\begin{thm}
Let $X$ be a complex manifold of dimension $2n+1$ and let
\beqn
\mathbf{c} \define \sum^{n}_{k = 0} (-1)^k \op{Td} \cdot \op{ch}(\wedge^k T)|_{4n+4} \in H^{4n+4}(BU(2n+1)) .
\eeqn
Then the current $\int \alpha \iota_X \alpha$ extends to a map of factorization algebras on $X$:
\beqn
\cV\op{ir}_{\mathbf{c}} \to \cB .
\eeqn
\end{thm}

\subsection{Equivariant master equations}

Suppose that $P$ is a $(-1)$-shifted Poisson dg vector space.
Then we have seen that the (BV) bracket endows $\cO(P)[-1]$ with the structure of a dg Lie algebra (generally this is just an $L_\infty$ algebra if the Poisson structure $\pi$ has components of weight $\geq 3$).
A strict Hamiltonian action of a dg Lie algebra $\lie{g}$ on $P$ is the data of a map of dg Lie algebra
\beqn\label{eqn:moment}
T \colon \lie{g} \to \cO(P)[-1]\footnote{Alternatively, this can be thought of as arising from a shifted version of the moment map $P \to \lie{g}^*[-1]$, where the $(-1)$-shifted Poisson structure on $\lie{g}^*[-1]$ is, like the Kostant--Kirillov Poisson structure, determined by the Lie bracket of $\lie{g}$.}.
\eeqn
The (BV) bracket is a map of dg Lie algebras $\{-,-\} \colon \cO(P)[-1] \to \op{Vect}(P)$; hence a Hamiltonian action defines, in particular, an infinitesimal $\lie{g}$-action on $P$.

Hamiltonian actions of the above type can be classified as follows.
Recall that the Chevalley--Eilenberg cochain complex $C^\bu(\lie{g})$ is a commutative dg algebra whose cohomology is the Lie algebra cohomology of $\lie{g}$ (with trivial coefficients).
Consider the dg Lie algebra
\beqn\label{eqn:babycme}
C^\bu(\lie{g}) \otimes \cO(P)[-1] 
\eeqn
where the bracket uses the product on the Chevalley--Eilenberg complex and the bracket on $\cO(P)$.
Hamiltonian actions \eqref{eqn:moment} define Maurer--Cartan elements in this dg Lie algebra.
More generally, we define a \defterm{Hamiltonian action} of $\lie{g}$ on the $(-1)$-shifted Poisson space $P$ to be a Maurer--Cartan element in this dg Lie algebra.
Directly in terms of the Lie algebra $\lie{g}$ these correspond to $L_\infty$ morphisms from $\lie{g}$ to $\cO(P)[-1]$.
Strict Hamiltonian actions are those which are linear in $\lie{g}$.
The Maurer--Cartan element equation for \eqref{eqn:babycme} is
\beqn
\d_{CE} J + \d_{P} J + \frac12 \{J,J\}  = 0
\eeqn
where $\d_{CE}$ is the Chevalley--Eilenberg differential for $\lie{g}$, $\d_P$ is the internal differential to $P$, and $\{-,-\}$ is the $(-1)$-shifted Poisson bracket on $\cO(P)$.\footnote{If $\pi$ has components of higher weight then \eqref{eqn:babycme} is only an $L_\infty$ algebra and the MC equation will also involve the higher brackets.}

\subsection{Stress tensor}
In this section, we fix a complex manifold $X$ of dimension $2n+1$ on which all objects are defined.
For $\mu \in \cT$ define the local functional
\beqn
T(\mu) \in \oloc(\fields)
\eeqn
by the formula
\beqn
T(\mu) = \sum_{k \geq 1} f(k) \int \alpha \iota_\mu^k \alpha .
\eeqn

\begin{lem}
The functional
\beqn
T \in \op{Act}(\cT,\fields)^1 
\eeqn
satisfies the classical master equation
\beqn
\d_{\cT} T + \del T + \frac12 \{T,T\} = 0 .
\eeqn
\end{lem}
\begin{proof}
First we compute
\beqn
\d_{\cT} T = - \sum_{k \geq 1} k f(k) \int \alpha \iota_{[\mu,\mu]} \iota^{k-1}_\mu \alpha 
\eeqn
and
\beqn
\del T = \sum_{k \geq 1} \int \alpha \iota_\mu^k \del \alpha .
\eeqn

Next, we compute
\beqn
\{\int \alpha \iota_{\mu} \alpha, \int \alpha \iota_{\mu'} \alpha\} = \int \del 
\eeqn
\end{proof}

\subsection{Modified stress tensor}

\section{Examples}

\subsection{The ordinary Segal--Sugawara construction}

The most general stress tensor is
\beqn
T_a(X) = \int \alpha \iota_X \alpha + \hbar a \int \alpha (J X)  
\eeqn

The central charge is $c = 1 + \hbar^2 \frac{1}{24} a^2$.

\subsection{Coupling in topological string theory}

The most general stress tensor is
\beqn
T_{\bfa} (X) = \int \alpha \iota_X \alpha + a_1 \int \alpha \op{Tr}(J X \del J X) + a_2 \int \alpha \op{Tr}(J X) \op{Tr}(\del J X) .
\eeqn

\subsection{Coupling in type IIB string theory}

\newpage

\appendix

\section{A dg model for the punctured formal disk} \label{appx:A}
Let $\sfA'$ be the graded polynomial algebra
\beqn
\C[z_i, \lambda_j, \mu_k]
\eeqn
where $i,j,k=1,2,3$ and the cohomological degrees of the generators are:
\beqn
\op{deg}(z_i) = \op{deg}(\lambda_j) = 0, \quad \op{deg}(\mu_i) = 1 .
\eeqn
Define the degree $2$ element
\beqn
\omega \define \sum_{ijk} \eps_{ijk} z_i \mu_j \mu_k = z_1 \mu_2 \mu_3 - z_2 \mu_1 \mu_3 + z_3 \mu_1 \mu_2 .
\eeqn
Define the differential $\d$ on $\sfA'$ on generators as follows
\begin{align*}
\d z_i & = 0 \\
\d \lambda_i & = - \sum_{jk} \eps_{ijk} z_j \mu_k \\
\d \mu_i & = 2 z_i \omega .
\end{align*}
This is a differential, $\d^2 = 0$, since $\eps_{ijk} z_j z_k = 0$ for any $i=1,2,3$.
Thus, $(\sfA', \d)$ is a commutative dg algebra.
Notice that $\d (\sum_i z_i \lambda_i) = 0$ and $\d (\mu_i \mu_j) = \d (\sum_k \eps_{ijk} \lambda_k \omega)$.

We consider the quotient $\sfA$ of the graded algebra $\sfA'$ by the ideal generated by the relations
\begin{enumerate}
\item $\sum_i \lambda_i z_i = 1$.
\item $\sum_i \lambda_i \mu_i = 0$.
\item $\mu_1 \mu_2 \mu_3 = 0$. 
\end{enumerate}

\begin{lem}
The differential preserves the relations (1),(2), and (3).
Thus, $(\sfA, \d)$ is a commutative dg algebra which is concentrated in degrees zero, one, and two.
\end{lem}
\begin{proof}
The differential preserves (1) since $\sum_{jk} \eps_{ijk} z_j z_k = 0$.
Now
\begin{align*}
\dbar( \sum_i \lambda_i \mu_i ) & = - (\sum_{ijk} \eps_{ijk} z_j \mu_k \mu_i) + 2\sum_i \lambda_i z_i \omega \\
& = 
\end{align*} 
\end{proof}

%\begin{lem}
%In the graded algebra $\sfA$ one has the relations $\mu_1 \mu_2 \mu_3 = 0$ and 
%\beqn
%\sum_{ijk} \eps_{ijk} \mu_i \mu_j z_k = \omega .
%\eeqn
%\end{lem}
%\begin{proof}
%From relation (3) we have $\mu_1 \mu_2 \mu_3 = \lambda_i \mu_i \omega$ for $i=1,2,3$.
%Thus using relation (2) we have $3 \mu_1 \mu_2 \mu_3 = \sum_i \lambda_i \mu_i \omega = 0$.
%Similarly, using (3) we have 
%\beqn
%\sum_{ijk} \mu_i \mu_j z_k = \sum_k \lambda_k z_k \omega = \omega .
%\eeqn
%\end{proof}

%It follows from this lemma that the graded algebra $\sfA$ is concentrated in degrees $0,1,2$. 
%Indeed from the above lemma we see
%\beqn
%\omega^2 = \left(\sum_{ijk} \eps_{ijk} \mu_i \mu_j z_k \right)^2 = 0
%\eeqn
%and
%\beqn
%\mu_i \omega = 0.
%\eeqn

\begin{prop}
The dg algebra $(\sfA,\d)$ is a dg model for $\R \Gamma(\A^3 - 0, \cO)$.
\end{prop}
\begin{proof}
First we recall a commutative dg model for punctured affine space defined in \cite{FHK}.
Let $z_i,z_i^*$ be variables of cohomological degree zero and let $z z^* \define \sum_i z_i z_i^*$.
Let $A_{[3]}^\bu$ be the commutative graded algebra generated over the localized ring
\beqn
\C[z_i,z_i^*] [(z z^*)^{-1}]
\eeqn
by degree one generators $\d z_i^*$, $i=1,2,3$ subject to the conditions
\begin{itemize}
\item[(i)] Give $z^*_i, \d z^*_i$ weight $+1$.
An element $\alpha \in A_{[3]}$ is required to have total weight zero.
\item[(ii)] Let $Eu^* = \sum_i z_i^* \del_{z_i^*}$, then an element $\alpha \in A_{[3]}$ is required to satisfy $\iota_{Eu^*} \alpha = 0$.
\end{itemize}
Let $\dbar = \sum_i \d z_i^* \del_{z_i^*}$ be the degree one operator acting on $A_{[3]}$.
Then $\dbar^2 = 0$ and $\sfA_{[3]}$ is a model for $\R \Gamma(\A^3 - 0, \cO)$ by \cite{FHK}.

This model is isomorphic to $\sfA$ by the isomorphism
\begin{align*}
\lambda_i & \leftrightarrow z_i^* (zz^*)^{-1} \\
\mu_i & \leftrightarrow \sum_{jk} \eps_{ijk} (z_j^* \d z_k^*) (z z^*)^{-2}  \\
\d & \leftrightarrow \dbar .
\end{align*}

\end{proof}

%\begin{align*}
%\d (\sum_i \lambda_i \mu_i) & = \sum_{ijk} \left(- \eps_{ijk} z_j \mu_k \mu_i + 2 \lambda_i z_i \omega \right) \\
%\end{align*}

\section{Chiral Liouville theory}

Let $\alpha \in \Omega^{1,\bu}(\C)$ be a spin $1$ field and consider the non-local action
\beqn
\int_\C \alpha \dbar \del^{-1} \alpha .
\eeqn

\section{Free field realization}

Let $\psi^\pm(z)$ be the fields of the free fermion system with OPE
\beqn
\psi^+(z) \psi^-(w) \simeq \frac{1}{z-w} .
\eeqn
These fields generate a simple vertex algebra that we denote by $F$.
We will call the vacuum vector $|0\> \in F$.

There is a family of stress tensors
\beqn
T^\lambda (z) = (1-\lambda) \colon \del \psi^+(z) \psi^- (z) \colon  + \lambda \colon \del \psi^- (z)\psi^+(z) \colon ,
\eeqn
which have central charge
\beqn
c_\lambda = - 2 (6 \lambda^2 - 6 \lambda + 1) .
\eeqn

This free fermion system exhibits the simplest free field realization.
Define the field
\beqn
\alpha(z) \define \colon \psi^+(z) \psi^-(z) \colon 
\eeqn
This is a free boson field of level $1$ and $\psi^\pm(z)$ has charge $\pm 1$ with respect to $\alpha(z)$.
This endows $F$ with the structure of a representation for the Heisenberg, or oscillator, algebra
\beqn
0 \to \C K \to \Hat{\lie{s}} \to \C((t)) \to 0
\eeqn
where $\alpha_j = t^j$ and the commutation relations are $[\alpha_i, \alpha_j] = i \delta_{i,-j}$.
Moreover, the stress tensor can be written in terms of this field as
\beqn
T_\lambda(z) = \frac12 \colon \alpha(z)^2 \colon + \left(\frac12 - \lambda\right) \del \alpha (z) .
\eeqn

The operator $\alpha_0$ defines a weight decomposition $F = \oplus_{m \in \Z} F^{(m)}$ where $\alpha_0$ acts on $F^{(m)}$ with eigenvalue $m$.
For $m > 0$ define the state
\beqn
|m\> \define \psi^+_{(-m)} \cdots \psi_{(-2)}^+ \psi_{(-1)}^+ |0\> 
\eeqn 
and for $m < 0$ define the state
\beqn
|m\> \define \psi^-_{(m)} \cdots \psi_{(-2)}^- \psi_{(-1)}^- |0\>  .
\eeqn 
Then $|m\> \in F^{(m)}$.
Further, these states exhibit the irreducibility of $F^{(m)}$ as a representation for the Heisenberg algebra $\Hat{\lie{s}}$.
Indeed, if $v \in F^{(m)}$ is any state with the property that $\alpha_j v = 0$ for all $j > 0$ then $v \in \C |m\>$.

\section{Lattices}
The target here is $\R^\ell / Q$.

Let $Q$ be the free abelian group of rank $\ell$ and consider the group algebra $\C[Q]$ with basis $e^{\alpha}, \alpha \in Q$ and multiplication $e^{\alpha} e^{\beta} = e^{\alpha + \beta}$.
We assume $Q$ is an integral lattice, meaning we have a symmetric bilinear form $(\cdot | \cdot) \colon Q \times Q \to \Z$.
We assume this bilinear form is non-degenerate.

Let $\lie{h} = \C \otimes_\Z Q \cong \C^\ell$ be the complexification of $Q$ and extend $(\cdot|\cdot)$ by linearity.
Denote by $\Hat{\lie{h}}$ the corresponding affine Heisenberg algebra with central parameter $K$.
The weight $\mu$ Verma module is
\beqn
\til V (\vec{\mu}) = U(\Hat{\lie{h}}) \otimes_{U(\lie{h}[[t]] \oplus \C K)} \C_{\mu, 1}
\eeqn
where $\C_{\vec{\mu},1}$ is the one-dimensional module where $t^0$ acts by the vector $\vec{\mu}$ and $K$ acts by $1$.
As a vector space
\beqn
\til V (\vec{\mu}) \simeq S \left(\lie{h}^{<0}\right)
\eeqn
where $\lie{h}^{<0} = \oplus_{j < 0} \lie{h} \otimes t^j$.
Write $S$ for this vector space.
In the case $\vec{\mu} = 0$, the vacuum module $S$ is equipped with the structure of a vertex algebra.

Let 
\beqn
V_Q \define S \otimes \C[Q] .
\eeqn

\section{Virasoro TFT}

Let $\Sigma$ be a Riemann surface and $S$ a one-dimensional smooth manifold.
We consider the local Lie algebra
\beqn
\Omega^\bu(S) \hotimes \Omega^{0,\bu}(\Sigma, \T_{\Sigma}) 
\eeqn
controlling deformations of the THF.

This theory has fields
\begin{align*}
\sfc & \in \Omega^\bu(S) \hotimes \Omega^{0,\bu}(\Sigma, \T_\Sigma)[1] \\
\sfb & \in \Omega^\bu(S) \hotimes \Omega^{0,\bu}(\Sigma, K_\Sigma^{\otimes 2})
\end{align*}
where the classical action is 
\beqn
\int_{S \times \Sigma} \sfb (\d + \dbar) \sfc + \frac12 \int_{S \times \Sigma} \sfb [\sfc,\sfc] .
\eeqn
The central charge should introduce a coupling like
\beqn
\int_{S \times \C} J \sfc \del J \sfc .
\eeqn

I claim that this factorization algebra is locally constant, so on $\R \times \C = \R^3$ we get an $\EE_3$ algebra.
The complex of local operators is equivalent to
\beqn
C^\bu(\lie{vect}(1) \oplus F_{-2}[-1]) \simeq C^\bu(\lie{vect}(1) ; S^\bu \left(F^\vee_{-2}\right))
\eeqn
where $F_{-2} = \Gamma(D, K^{\otimes 2})$.
In other words we have polynomials in $\del^\bu \sfc$ and $\del^\bu \sfb$.
Since $\sfb$ is spin $2$ the cohomology of this is the same as the cohomology of just the $\sfc$'s:
\beqn
H^\bu(\lie{vect}(1)) = \C \oplus \C[-3] .
\eeqn
This is hopeful, it's the same as the cohomology of local operators in Chern--Simons theory for $\lie{sl}(2)$.

I think that the $\EE_3$ algebra $C^\bu(\lie{sl}(2))$ underlying Chern--Simons for $\lie{sl}(2)$ is trivializable.
But it is nontrivial as a filtered $\EE_3$ algebra where the filtration is by symmetric degree.
Can we identify this filtration in this theory?

\section{Holomorphic 3d-3d}

Consider compactification of the free tensor multiplet along
\beqn
C \times (\C^2 - \{0\})
\eeqn 
where $C$ is a Riemann surface.
Then
\beqn
\Omega^{2,\bu}(C \times (\C^2 - \{0\})) \simeq \Omega^{0,\bu}(C) \otimes \Omega^{2,\bu}(\C^2 -\{0\}) \oplus \Omega^{1,\bu}(C) \otimes \Omega^{1,\bu}(\C^2 - \{0\}) .
\eeqn

\end{document}

Let 
\beqn
\sfR = \C[z_i,\lamba_j,\mu_k]_{i=1,2,3} / (1-z_i \lambda_i, 
\eeq
where $z_i, \lambda_j$ have degree zero for $i,j=1,2,3$ and $\mu_k$ is degree one for $k=1,2,3$.
In particular $z_i \mu_j = \mu_j z_i$ and $\mu_i \mu_j = - \mu_j \mu_i$.

In degree zero we have polynomials in $z_i,\lambda_i$ where we identify polynomials according to the relation $z_i \lambda_i =1$.

### 2024-06-05 segalsugawara.tex
ipad edits

@@
 We have pointed out in \eqref{eqn:localtocompact} how local cohomology classes of a local Lie algebra $\cL$ supported on $U$ determine Lie algebra cohomology classes for the Lie algebra of compactly supported sections $\cL_c(U)$.
-We recall in appendix \cite{appx:model}, the $n$-dimensional Witt algebra $\lie{witt}(n)$ admits a homomorphism of dg Lie algebras
+We showed in appendix \ref{appx:A} that the $n$-dimensional Witt algebra $\lie{witt}(n)$ admits a homomorphism of dg Lie algebras
 \beqn
@@
 \end{lem}
+\begin{proof}
+Let $E$ be a vector bundle on $\R^n$.
+In \cite[??]{CostelloBook} it is shown that a choice of a flat connection on $E$ produces a quasi- isomorphism 
+\beqn
+\oloc(E)^{\R^n} \simeq \left(\cO(J_0 E) \slash \C\right) \otimes^{\mathbb{L}}_{\R[\del_1,\ldots,\del_n]} |\det|_{\R^n},
+\eeqn
+where $\del_i$ are the coordinate vector fields and $J_0 E$ denotes the fiber of the $\infty$-jet bundle of $E$ at the origin $0 \in \R^n$.
+We apply this to the case that $E[1] = L$ is a local Lie algebra, where we equip local functionals with the Chevalley--Eilenberg differential.
+Then, this result says that
+\beqn
+C^\bu_{loc}(\cL)^{\R^n} \simeq C^\bu_{red}(J_0 L) \otimes^{\mathbb{L}}_{\R[\del_1,\ldots,\del_n]} |\det|_{\R^n} 
+\eeqn
+where $J_0 L$ is the topological Lie algebra obtained by taking the $\infty$-jets of $L$ at $0 \in \R^n$, and is equipped with the bracket obtained by Taylor expanding the bracket on $L$.
+
+We apply this to the case $\cL = \Omega^\bu_\R \otimes \lie{g}$.
+Then, by the formal Poincar\'e lemma
+\beqn
+(J_0 L, \d_{dR}) \simeq \left(\C[[x,\d x]] \otimes \lie{g}, \d_{dR} \otimes \id\right) \simeq \left(\lie{g}, \d = 0\right) .
+\eeqn
+This implies the result.
+\end{proof}
 
@@
 \subsection{Enveloping factorization algebras}
-
+\label{s:enveloping}
+
+We recall the construction of the enveloping factorization algebra from \cite{CG2}.
 Let $\cE$ be a vector bundle on a manifold $M$ and let $\cE_c$ denote its cosheaf of compactly supported sections.
-It is shown how the assignment of the graded vector space
+It is shown in \cite{CG1} how the assignment of the graded vector space
 \beqn
@@
 Now, let $\cL = \Gamma(M,L)$ be a local dg Lie algebra on a manifold $M$.
-Applying the above construction to $E[-1] = L$ gives rise to the factorization algebra which assigns to an open set $U \subset M$ the graded vector space 
+Applying the above construction to $E[-1] = L$ gives rise \cite{CG2} to the factorization algebra which assigns to an open set $U \subset M$ the graded vector space 
 \beqn
@@
 
+In this section we introduce the sort of `free' factorization algebras which we will realize symmetries by the higher dimensional Virasoro algebras that we introduced in the last section.
+The contents of this section are only a mild generalization of \cite[\S 8.1]{CG2} which associates a factorization algebra of quantum observables to free quantum field theories.
+In \textit{loc.
+cit.} the definition of a free quantum field theory requires non-degeneracy of the two-form on the space of fields; in other words, it pertains to the Batalin--Vilkovisky (BV) quantization of a $(-1)$-shifted symplectic space.
+In this section we weaken non-degeneracy defining the free classical field theoruy; or equivalently, we start with a type of $(-1)$-shifted presymplectic structure.
+Because of the strict assumptions we place on the $(-1)$-shifted presymplectic structure, we can associate to it a $\PP_0$-factorization algebra.
+We then form the BV quantization of the associated $\PP_0$-factorization algebra of classical observables.
+
 \subsection{Weyl factorization algebras}
@@
 
-Let $(E,Q)$ be a complex of vector bundles on a manifold $M$ and consider the precosheaf of commutative algebras
+Consider a complex of vector bundles $(\cE,Q)$ on a manifold $M$.
+By applying the construction of the enveloping factorization algebra, recalled in \ref{s:enveloping}, to the abelian local Lie algebra $L = E[-1]$ we obtain the factorization algebra
 \beqn
@@
 \eeqn
-If $\sqcup U_i \hookrightarrow V$ is a collection of disjoint open sets embedded inside of another open set then multiplication on this precosheaf determines a morphism
-\beqn\label{eqn:freefactmaps}
-\otimes \Sym(\cE_c(U_i)) \to \Sym(\cE_c(V)) .
-\eeqn
-By \cite[??]{CG1} this endows $\Sym(\cE_c)$ with the structure of a factorization algebra.
-We recalled in section \ref{sec:enveloping} how a deformation of this in the case that $E[-1] = L$ is a local Lie algebra on $M$ gives rise to the enveloping factorization algebra associated to $L$.
-
-A generalization of this construction involves the data of a local functional 
+Now, fix the data of a local functional 
 \beqn
@@
 of cohomological degree $+1$ which satisfies $Q \omega = 0$.
-For each open set $U \subset M$, there is a natural inclusion $\cO_{loc}(E) (U) \hookrightarrow \cO(\cE_c(U))$ so that we can view $\omega$ as a functional
-\beqn
-\omega \colon \Sym(\cE_c(U)) \to \C .
-\eeqn 
-Let $\omega_{[k]}$ be the $k$th homogenous part of $\omega$ so that 
-\beqn
-\omega_{[k]} \colon \Sym^k (\cE_c(U)) \to \C
-\eeqn
-We extend $\omega$ to a map $Q_{\omega_{[k]}} \colon \Sym(\cE_c(U)) \to \Sym(\cE_c(U))[1]$ of cohomological degree one by declaring that for each $k$ $\omega_{[k]}$  \brian{finish} and we let $Q_{\omega} = \sum Q_{\omega_{[k]}}$.
+In other words, this is a local cocycle for the abelian local Lie algebra $L = E[-1]$ of degree $+1$.
+By applying the twisted factorization enveloping algebra construction to this local cocycle, we obtain the following.
 
 \begin{prop}[\cite{CG1}]
-Let $K$ be a parameter of cohomological degree zero.
 The assignment
 \beqn
-\cW_{E,\omega} \colon U \subset M \mapsto \left(\Sym(\cE_c(U))[K], Q + K Q_\omega \right)
-\eeqn
-has the structure of a factorization algebra in the category of dg $\C[K]$-modules with structure maps \eqref{eqn:freefactmaps}.
+\cW_{E,\omega} \colon U \subset M \mapsto \left(\Sym(\cE_c(U))[K] \,, \, \,Q + K Q_\omega \right)
+\eeqn
+has the structure of a factorization algebra in the category of dg $\C[K]$-modules, where $K$ is a variable of degree zero.
 We refer to this as the \defterm{Weyl factorization algebra} associated to $E,\omega$.
@@
 
-\subsection{The higher-dimensional free boson}
+\subsection{The higher-dimensional free chiral boson}
 
@@
 \beqn
-\cF \define \left(\Sym \left(\Omega^{\leq n}_{X,c} [n+1] \right) \; , \; Q + \triangle \right) ,
+\cF \define \left(\Sym \left(\Omega^{\leq n,\bu}_{X,c} [n+1] \right) \; , \; Q + \triangle \right) ,
 \eeqn
@@
 
-\section{A dg model for the punctured formal disk} \label{appx:A}
+\section{A dg model for punctured affine space} \label{appx:A}
+
+In this appendix we recall a commutative dg model for punctured affine space $\A^n - \{0\}$ defined in \cite{FHK}.
+Let $z_i,z_i^*$, $i=1,\ldots,n$ be variables of cohomological degree zero and let $z z^* \define \sum_{i=1}^n z_i z_i^*$.
+Let $\sfA_{[n]}^\bu$ be the commutative graded algebra generated over the localized ring
+\beqn
+\C[z_i,z_i^*] [(z z^*)^{-1}]
+\eeqn
+by degree one generators $\d z_i^*$, $i=1,\ldots,n$ subject to the conditions
+\begin{itemize}
+\item[(i)] Give $z^*_i, \d z^*_i$ weight $+1$ for $i=1,\ldots,n$.
+An element $\alpha \in \sfA_{[n]}$ is required to have total weight zero.
+\item[(ii)] Let $Eu^* = \sum_i z_i^* \del_{z_i^*}$, then an element $\alpha \in \sfA_{[n]}$ is required to satisfy $\iota_{Eu^*} \alpha = 0$.
+\end{itemize}
+
+Let $\dbar = \sum_i \d z_i^* \del_{z_i^*}$ be the degree one operator acting on $A_{[n]}$.
+Then $\dbar^2 = 0$ and $(\sfA_{[n]},\dbar)$ is a commutative dg algebra.
+
+\begin{thm}[\cite{FHK}]
+The dg algebra $(\sfA_{[n]},\d)$ is a dg model for $\R \Gamma(\A^n - \{0\}, \cO)$.
+\end{thm}
+
+We observe that any element of the form $f(z,z^*) \d^n z^* = f(z,z^*) \d z_1^* \cdots \d z_n^*$ does not satisfy the conditions (i),(ii).
+In particular, we see that $\sfA_{[n]}$ is concentrated in cohomological degrees $0,\ldots,n-1$.
+As a model for punctured affine space, the cohomology of $\sfA$ is concentrated in degrees zero and $n-1$.
+In degree zero the cohomology is simply globally defined algebraic functions on punctured affine space, which by Hartog's theorem is
+\beqn
+H^0(\sfA_{[n]}) = \C[z_1,\ldots,z_n] .
+\eeqn
+Next, define
+\beqn
+\omega_{BM} = \# \sum_{i=1}^n (-1)^{i+1} \frac{z_i^* \d z_1^* \cdots \Hat{\d z_i^*} \cdots \d z_n^* }{(z z^*)^n}
+\eeqn
+be the Bochner--Martenilli kernel.
+One can check that $\omega_{BM}$ is a degree $(n-1)$ element of $\sfA_{[n]}$
+Then a presentation for the degree $(n-1)$ cohomology is 
+\beqn
+H^{n-1}(\sfA_{[n]}) \cong \C[\del_{z_1},\ldots,\del_{z_n}] \omega_{BM} .
+\eeqn
+
+In the main text, we find it convenient to introduce the notation
+\beqn
+\lambda_i \define \frac{\zbar_i}{(zz^*)} .
+\eeqn
+When $n=1$ this is simpy $\lambda = \frac{1}{z}$.
+
+There is an embedding of commutative dg algebras \cite{FHK}:
+\beqn
+j \colon \sfA \hookrightarrow \Omega^{0,\bu}(\C^n - \{0\})
+\eeqn
+which sends $z_i \mapsto z_i$, $z_i^* \mapsto \zbar_i$, $\d z^*_i \mapsto \d \zbar_i$, which clearly interchanges the algebraic $\dbar$-operator with the usual one.
+This embedding becomes a dense inclusion at the level of cohomology.
+In the main text, we do not distinguish the polynomial variable $z_i^*$ with the anti-holomorphic coordinate $\zbar_i$.
+
+We will utilize a higher residue map.
+Let 
+\beqn
+\op{Res} \left(- \d^n z\right) \colon \sfA \to \C[-n+1]
+\eeqn
+be defined by the projection onto the component of $\omega_{BM} \in \sfA_{[n]}$, which is of degree $n-1$.
+As observed in \cite{FHK}, one has compatibility with usual integration over any $(2n-1)$-sphere centered at the origin as
+\beqn
+\Res_z(\alpha \d^n z) = \oint_{S^{2n-1}} j(\alpha) d^n z ,
+\eeqn
+for $\alpha \in \sfA_{[n]}$.
+
+\subsection{Three-dimensional example}
+In this appendix we unpack the model above in the special case of the three-dimensional punctured affine space to come up with a description via generators and relations.
+
 Let $\sfA'$ be the graded polynomial algebra
@@
 \begin{proof}
-First we recall a commutative dg model for punctured affine space defined in \cite{FHK}.
-Let $z_i,z_i^*$ be variables of cohomological degree zero and let $z z^* \define \sum_i z_i z_i^*$.
-Let $A_{[3]}^\bu$ be the commutative graded algebra generated over the localized ring
-\beqn
-\C[z_i,z_i^*] [(z z^*)^{-1}]
-\eeqn
-by degree one generators $\d z_i^*$, $i=1,2,3$ subject to the conditions
-\begin{itemize}
-\item[(i)] Give $z^*_i, \d z^*_i$ weight $+1$.
-An element $\alpha \in A_{[3]}$ is required to have total weight zero.
-\item[(ii)] Let $Eu^* = \sum_i z_i^* \del_{z_i^*}$, then an element $\alpha \in A_{[3]}$ is required to satisfy $\iota_{Eu^*} \alpha = 0$.
-\end{itemize}
-Let $\dbar = \sum_i \d z_i^* \del_{z_i^*}$ be the degree one operator acting on $A_{[3]}$.
-Then $\dbar^2 = 0$ and $\sfA_{[3]}$ is a model for $\R \Gamma(\A^3 - 0, \cO)$ by \cite{FHK}.
-
-This model is isomorphic to $\sfA$ by the isomorphism
+This model is isomorphic to $\sfA_{[n]}$ recollected in the previous section by the isomorphism
 \begin{align*}
@@
 \end{proof}
+
+\subsection{dg model for vector fields}
+
+Next we turn to an explicit model for dg model for vector fields on punctured affine space.
+Algebraic sections of the tangent bundle $\T_{\A^n - \{0\}}$ is a sheaf of Lie algebras on punctured affine space and its derived global sections 
+\beqn
+\R \Gamma(\A^n - \{0\}, \T_{\A^n-\{0\}})
+\eeqn
+therefore carry the structure of a Lie algebra, up to homotopy.
+We use the commutative dg algebra model $\sfA_{[n]}$ for punctured affine space recollected above to derive an explicit model for this as a dg Lie algebra.
+
+The choice of a coordinate determines a trivialization of the tangent bundle on $\A^n - \{0\}$.
+In particular
+\beqn
+\R \Gamma(\A^n - \{0\}, \T_{\A^n-\{0\}}) \simeq \R \Gamma(\A^n - \{0\}, \cO_{\A^n - \{0\}}) \otimes \C^n
+\eeqn
+where $\C^n$ is spanned by the vector fields $\frac{\del}{\del z_i}$, $i=1,\ldots,n$.
+
+\begin{dfn}
+The $n$-\defterm{dimensional Witt algebra} $\lie{witt}(n)$ is the dg Lie algebra whose underlying cochain complex is
+\beqn
+\lie{witt}(n) = \sfA_{[n]} \otimes \C^n = \sfA_{[n]} \otimes \C \left\{\frac{\del}{\del z_i}\right\}_{i=1}^n
+\eeqn
+and whose Lie bracket is
+\begin{multline}
+\left[\alpha_{I,i} (z,z^*) \d z^*_I \frac{\del}{\del z_i}, \beta_{J,j} (z,z^*) \d z^*_J \frac{\del}{\del z_j} \right] \\ = \left(\alpha_{I,i}(z,z^*) \frac{\del}{\del z_i} \beta_{J,j}(z,z^*)\frac{\del}{\del z_j} - (-1)^{|I|} \beta_{J,j}(z,z^*) \frac{\del}{\del z_j}\alpha(z,z^*) \frac{\del}{\del z_i}\right) \d z_I^* \d z_J^* .
+\end{multline}
+\end{dfn}
 
@@
 where $C$ is a Riemann surface.
-Then
-\beqn
-\Omega^{2,\bu}(C \times (\C^2 - \{0\})) \simeq \Omega^{0,\bu}(C) \otimes \Omega^{2,\bu}(\C^2 -\{0\}) \oplus \Omega^{1,\bu}(C) \otimes \Omega^{1,\bu}(\C^2 - \{0\}) .
-\eeqn
+To compactify we replace $\Omega^{0,\bu}(\C^2 - \{0\})$ by
+\beqn
+\Omega^{\bu}(\R) \otimes \left(\C[w_1,w_2] \oplus (w_1 w_2)^{-1}\C[w_1^{-1},w_2^{-1}][-1] \right)
+\eeqn
+Also, let $\cA^{i,\bu}(C \times \R)$ denote $\Omega^{i,\bu}(C) \otimes \Omega^\bu(\R)$ for $i=0,1$.
+
+For the tensor, observe
+\beqn
+\Omega^{2,\bu}(C \times (\C^2 - \{0\})) \simeq \Omega^{0,\bu}(C) \otimes \Omega^{2,\bu}(\C^2 -\{0\}) \oplus \Omega^{1,\bu}(C) \otimes \Omega^{1,\bu}(\C^2 - \{0\}) ,
+\eeqn
+and 
+\beqn
+\Omega^{3,\bu}(C \times (\C^2 - \{0\})) \simeq \Omega^{1,\bu}(C) \otimes \Omega^{2,\bu}(\C^2 - \{0\}) .
+\eeqn
+
+So the complex of fields is
+\beqn
+\begin{tikzcd}
+\ul{-1} & \ul{0} & \ul{1} \\
+\cA^{0,\bu} [w_1,w_2] \d^2 w \ar[r,"\del_C"] & \cA^{1,\bu}[w_1,w_2] \d^2 w & \\
+\cA^{1,\bu}[w_1,w_2] \d w_i \ar[ur,"\del_w"] & & \\
+& (w_1w_2)^{-1}\cA^{0,\bu} [w_1^{-1},w_2^{-1}] \d^2 w \ar[r,"\del_C"] & (w_1w_2)^{-1}\cA^{1,\bu}[w_1^{-1},w_2^{-1}] \d^2 w \\
+& (w_1 w_2)^{-1}\cA^{1,\bu}[w_1^{-1},w_2^{-1}] \d w_i \ar[ur,"\del_w"] & 
+\end{tikzcd}
+\eeqn
+
+This looks to be quasi-isomorphic to
+\beqn
+\begin{tikzcd}
+\ul{-1} & \ul{0} & \ul{1} \\
+\cA^{0,\bu} [w_1,w_2] \d^2 w & & \\
+\cA^{1,\bu} \otimes (\C[w_1,w_2] \slash \C) & & \\
+& (w_1w_2)^{-1}\cA^{0,\bu} [w_1^{-1},w_2^{-1}] \d^2 w & \\
+& \cA^{1,\bu} \otimes \left( (w_1 w_2)^{-1} \C[w_1^{-1},w_2^{-1}] / (\C \cdot (w_1 w_2)^{-1}) \right)  & 
+\end{tikzcd}
+\eeqn
+
+The compactification of the hypermultiplet is
+\beqn
+\begin{tikzcd}
+\ul{-2} & \ul{-1} & \ul{0} & \ul{1} \\
+\cA^{0,\bu}[w_1,w_2] &  (w_1w_2)^{-1}\cA^{0,\bu} [w_1^{-1},w_2^{-1}] \\
+& & \cA^{1,\bu}[w_1,w_2] \d^2 w &  (w_1w_2)^{-1}\cA^{1,\bu} [w_1^{-1},w_2^{-1}] \d^2 w .
+\end{tikzcd}
+\eeqn
+
+It appears if we take $\C^\times$-invariants where $w_i$ has weight one, then the only thing that survives is from the hyper part. 
+Namely
+\beqn
+\begin{tikzcd}
+\ul{-2} & \ul{-1} & \ul{0} & \ul{1} \\
+\cA^{0,\bu} &  & & \\
+& & &  (w_1w_2)^{-1}\cA^{1,\bu} \d^2 w .
+\end{tikzcd}
+\eeqn
+If we regrade, then I think we are looking OK; this is level zero limit of $\lie{gl}(1)$ Chern--Simons theory.
+We should see the level from the shifted Poisson structure somehow.
+
+Something is weird with the spin, I think the correct `twist' replaces the hyper above with 
+\begin{align*}
+\gamma & \in \Omega^{1,\bu}(\C) \otimes \Omega^{0,\bu}(\C^2 - \{0\}) \\
+\beta & \in \Omega^{0,\bu}(C) \otimes \Omega^{2,\bu}(\C^2 - \{0\}) .
+\end{align*}
+Then the compactification looks like
+\beqn
+\begin{tikzcd}
+\ul{-2} & \ul{-1} & \ul{0} & \ul{1} \\
+\cA^{0,\bu}[w_1,w_2] \d^2 w &  (w_1w_2)^{-1}\cA^{0,\bu} [w_1^{-1},w_2^{-1}] \d^2 w \\
+& & \cA^{1,\bu}[w_1,w_2] &  (w_1w_2)^{-1}\cA^{1,\bu} [w_1^{-1},w_2^{-1}]  .
+\end{tikzcd}
+\eeqn
+
+Next, we want to understand what happens when we turn on the $\Omega$-background/superconformal deformation.
 

### 2025-05-20 segalsugawara.tex
major push

@@
 
-\usepackage{macros-master,amsaddr,physics}
+\usepackage{../macros-master,amsaddr,physics}
 \usepackage{mathbbol}
 
-\addbibresource{refs}
-
-\renewcommand{\div}{\del_{\Omega}}
-\renewcommand{\PV}{\mathrm{PV}}
-\renewcommand{\op}{\operatorname}
-
-\newcommand{\sfa}{\mathsf{a}}
-\newcommand{\sfb}{\mathsf{b}}
-\newcommand{\sfc}{\mathsf{c}}
-\newcommand{\bfa}{\mathbf{a}}
-\newcommand{\bfc}{\mathbf{c}}
-\newcommand{\bfk}{\mathbf{k}}
-
-\newcommand{\fields}{\cC}
+\addbibresource{refs.bib}
+
+\newcommand{\fields}{\cE}
 \newcommand{\Vir}{\sV\op{ir}}
@@
 \setcounter{tocdepth}{1}
+
+\renewcommand{\op}{\operatorname}
 
@@
 
-Let $X$ be a complex manifold of dimension $n$.
+Let $X$ b
+e a complex manifold of dimension $n$.
 The sheaf of holomorphic vector fields has the natural structure of a sheaf of Lie algebras with bracket the Lie bracket of vector fields.
@@
 This bracket endows the Dolbeault complex $\Omega^{0,\bu}(X, \T_X)$ with coefficients in the holomorphic tangent bundle with the structure of a dg Lie algebra where the differential is $\dbar$.
+Its global sections is an explicit model for the dg Lie algebra $\R\Gamma(X , \cT_X)$ where $\cT_X$ is the sheaf of holomorphic vector fields on $X$.
 
@@
 Let $\cT_X$ be the local dg Lie algebra whose underlying complex of vector bundles is
-\beqn
-\Omega^{0,\bu}(X, \T_X) .
-\eeqn
+\begin{equation}
+\Omega^{0,\bu}(X, \T_X) = \Gamma_{C^\infty} \left(X , \wedge^\bu \br \T_X \otimes \T_X \right) .
+\end{equation}
 The differential is the $\dbar$-operator associated to the holomorphic bundle $\T_X$.
@@
 
-In particular, the dg Lie algebra $\cT(\C - \{0\})$ is quasi-isomorphic to holomorphic vector fields on $\C^\times$.
-Replacing $\C^\times$ by the formal punctured disk gives the Witt algebra $\Vect(D^\times) = \C((z)) \del_z$ whose unique nontrivial central extension is the Virasoro Lie algebra.
+The dg Lie algebra $\cT(\C - \{0\})$ is quasi-isomorphic to the Lie algebra of holomorphic vector fields on~$\C^\times$.
+Replacing $\C^\times$ by the formal punctured disk gives the Witt algebra $\lie{vect}(D^\times) = \C((z)) \del_z$ whose unique nontrivial central extension is the Virasoro Lie algebra.
 
 For an example of a complex manifold which is not Stein consider $X = \C^n - \{0\}$.
-There is an embedding of dg Lie algebras
-\beqn
+The embedding of dg Lie algebras
+\begin{equation}
 \Vect^{hol}(\C^n - \{0\}) \hookrightarrow \cT(\C^n - \{0\})
-\eeqn
-which is no longer a quasi-isomorphism.
+\end{equation}
+is no longer a quasi-isomorphism.
 This map does define an isomorphism in $H^0$ cohomology, but $\cT(\C^n-\{0\})$ also has cohomology in degree $(n-1)$. 
 In standard coordinates, cochain representatives for this cohomology are given by expressions of the form
-\beqn
+\begin{equation}
 \sum_j \left(\sum_{k_1 \cdots k_n} a^j_{k_1\cdots k_n} L_{\del_{z_1}^{k_1}} \cdots L_{\del_{z_n}^{k_n}} \omega_{BM}\right) \frac{\del}{\del z_j} 
-\eeqn
-Here $a^j_{k_1\cdots k_n}$ are constants and $\omega_{BM} \in \Omega^{0,n-1}(\C^n-\{0\})$ is the Bochner--Martinelli form which is characterized by the formula $\oint_{S^{2n-1}} \omega_{BM} \wedge \d^n z= 1$ with $S^{2n-1}$ the sphere of radius one centered at $0 \in \C^n$.
-
-Here we make the distinction between $\C^n$ and affine space $\A^n$; the latter is the algebraic variety with functions $\C[z_1,\ldots,z_n]$.
-There is an algebraic version of $\cT(\C^n - \{0\})$ with $\C^n - \{0\}$ replaced by punctured $n$-dimensional algebraic affine space $\A^n - \{0\}$.
-Using a dg model for the punctured $n$-space presented in \cite{FHK}, in appendix \ref{appx:A} we construct a dg model for the derived global sections of the tangent bundle over punctured affine space which we will denote by $\lie{witt}(n)$ and refer to as the \defterm{$n$-dimensional Witt algebra}.
+\end{equation}
+Here $a^j_{k_1\cdots k_n}$ are constants and $\omega_{BM} \in \Omega^{0,n-1}(\C^n-\{0\})$ is the Bochner--Martinelli form characterized by the formula $\oint_{S^{2n-1}} \omega_{BM} \wedge \d^n z= 1$ with $S^{2n-1}$ any sphere centered at $0 \in \C^n$.
+
+We make the distinction between the complex manifold $\C^n-\{0\}$, the algebraic variety of punctured affine space $\mathring{\A}^{n}=\A^n - \{0\}$, and the punctured formal disk $\mathring{D}^{n}=D^{n}-\{0\}$.
+A model for the derived algebra of functions for the complex manifold $\C^{n}-\{0\}$ is the Dolbeault complex $\Omega^{0,\bu}(\C^{n}-\{0\})$.
+Using the Jouanolou torsor, an explicit model for the derived algebra of functions on punctured affine space (respectively, formal disk) has been constructed in \cite{FHK} and we will denote it $\sfA_{[n]}$ (respectively, $\sfA_{n}$).
+It is an algebraic (respectively, formal) version of the Dolbeault complex of the complex manifold $\C^{n}-\{0\}$.
+Similarly, there is an algebraic (respectively, formal) version of $\cT(\C^n - \{0\})$ with $\C^n - \{0\}$ replaced by punctured $n$-dimensional algebraic affine space $\mathring{\A}^{n}$ (respectively, the punctured formal disk $\mathring{D}^{n}$).
+In the affine (respectively, formal) case these models are cochain models for the derived global sections of the tangent sheaf $\R \Gamma(\mathring{\A}^{n},\T)$ (respectively, $\R \Gamma(\mathring{D}^{n},\T)$).
+
+Using a dg model for the punctured $n$-space presented in \cite{FHK}, in appendix \ref{appx:A} we construct a dg model for the derived global sections of the tangent bundle over the punctured formal disk which we will denote by $\lie{witt}(n)$ and refer to as the \defterm{$n$-dimensional Witt algebra}.
 Here is a list of important properties of the dg Lie algebra $\lie{witt}(n)$:
 \begin{itemize}
-\item The underlying cochain complex $\lie{witt}(n)$ is concentrated in cohomological degrees $0,\ldots,n-1$.
-\item Its cohomology is concentrated in degrees $0$ and $n-1$.
-There is an inclusion of the Lie algebra of vector fields on $\A^n$ (thought of as a dg Lie algebra concentrated in degree zero):
-\beqn
-\lie{vect}^{alg}(n) = \C[z_1,\ldots,z_n]\{\del_{z_1},\ldots,\del_{z_n}\} \hookrightarrow 
+  \item It is a dg model for $\R \Gamma(\mathring{D}^{n},\T)$.
+        The underlying cochain complex $\lie{witt}(n)$ is concentrated in cohomological degrees $0,\ldots,n-1$. In particular, its cohomology is concentrated in degrees $0$ and $n-1$.
+  \item We have the following local trivializations.
+        Any element of $\xi \in \lie{witt}(n)$ is of the form
+        \begin{equation}\label{}
+          \xi = \sum_{i=1}^{n} \alpha_{i}(z) \frac{\del}{\del z_{i}}
+        \end{equation}
+        where $\alpha_{i}(x) \in \sfA_{n}$.
+\item There is an inclusion of dg Lie algebras from vector fields on the formal disk $D^n$ (thought of as a dg Lie algebra concentrated in degree zero):
+\begin{equation}
+\lie{vect}(n) = \op{Der} \, \C[[z_1,\ldots,z_n]] \hookrightarrow
 \lie{witt}(n)
-\eeqn
+\end{equation}
 which induces an isomorphism in zeroth cohomology.
@@
 
-The Virasoro Lie algebra is the unique nontrivial central extension of the Witt algebra $\lie{witt}(1)$.
+The Virasoro Lie algebra is the unique nontrivial central extension of the ordinary Witt algebra $\lie{witt}(1)$.
 This central extension admits an interpretation in terms of the Lie algebra cohomology of  vector fields $\lie{vect}(1)$ on the $1$-disk via the isomorphisms
-\beqn
+\begin{equation}
 H^3(\lie{vect}(1); \C) \cong H^2(\lie{vect}(1); \Omega^1) \cong H^2(\lie{witt}(1);\C) \cong \C .
-\eeqn
-In the last part of this section we will construct an injective map
-\beqn
+\end{equation}
+This is a version of transgression, and in this example it can be understood explicitly as follows.
+Consider the dg $\lie{vect}(1)$-module $\Omega^{\bu}$ defined by
+\begin{equation}\label{}
+  \cO(D) = \C[[z]] \xto{\del} \C[[z]] \d z = \Omega^{1}(D) [-1]
+\end{equation}
+where the differential is the de Rham differential.
+By the formal Poincar\'{e} lemma, there is a quasi-isomorphism of $\lie{vect}(1)$-modules $\C \xto{\simeq} \Omega^{\bu}$ and a map \brian{finish}
+
+Take a class $[\phi] \in H^{3}(\lie{vect}(1))$.
+
+In the last part of this section we will construct a linear map
+\begin{equation}
 H^{2n+1}(\lie{vect}(n);\C) \to H^2(\lie{witt}(n);\C), 
-\eeqn
+\end{equation}
 thus providing a source of central extensions for the $n$-dimensional Witt algebra.
@@
 
-\subsection{Central extensions from local cohomology}
+\subsection{Local cohomology of vector fields}
 
@@
 We briefly recall the definition of local cohomology from \cite{CG2}.
+For details specific to the local Lie algebra of holomorphic vector fields we refer to \cite{BWgf}.
 
 For $E$ a vector bundle on a manifold $M$, define the space of local functionals to be 
-\beqn
-\oloc(E) \define {\rm Dens}_M \otimes_{D_M} {\rm Lag} (E) .
-\eeqn
+\begin{equation}
+\oloc(E) = {\rm Dens}_M \otimes_{D_M} {\rm Lag} (E) .
+\end{equation}
 Here $\op{Dens}_X$ is the bundle of densities on $M$ and $\op{Lag}(E)$ is the left $D_M$-module of Lagrangians
-\beqn
-\op{Lag} (E) \define \prod_{n > 0} {\rm Hom}_{C^\infty_M} \left(\op{jet} (E) , C^\infty_M\right) .
-\eeqn
+\begin{equation}
+\op{Lag} (E) \define \prod_{n > 0} {\rm Hom}_{C^\infty_M} \left( \Sym^n(J^\infty E) , C^\infty_M\right) .
+\end{equation}
 Concretely, a Lagrangian is a $C^\infty_M$-valued functional which only depends on jets of sections of $E$, and a local functional is a Lagrangian defined up to total derivatives.
+Notice that we throw away the constant coefficient Lagrangian densitites.
 Given a Lagrangian $L = L(\phi)$ we will denote its corresponding local functional by~$\int L(\phi)$.
 
-If $E$ is a complex of vector bundles then $\oloc(E)$ is a sheaf of cochain complexes.
+If $E$ is a complex of vector bundles then $\oloc(E)$ inherits the differential and is a sheaf of cochain complexes.
 If $\cL = \Gamma(M, L)$ is a local Lie algebra then $\oloc(L[1])$ is equipped with the Chevalley--Eilenberg differential, hence giving a local version of Lie algebra cohomology.
-We denote this sheaf of complexes by $C^\bu_{loc}(\cL)$.
+We denote this sheaf of cochain complexes by $C^\bu_{loc}(\cL)$.
 Note that for every open set $U \subset M$ there is an embedding map
-\beqn\label{eqn:localtocompact}
+\begin{equation}\label{eqn:localtocompact}
 C^\bu_{loc}(\cL)(U) \hookrightarrow C^\bu(\cL_c(U)) 
-\eeqn
+\end{equation}
 where the right hand side is the Chevalley--Eilenberg complex computing the Lie algebra cohomology of compactly supported sections of $L$ on $U$.
-
-The local cohomology for $\cL=\cT_X$ the local Lie algebra of holomorphic vector fields on a complex manifold $X$ has been characterized in \cite{BWgf}.
+The map sends $\int \cL|_{U}$ to the honest integral $\int_{U} \cL$.
+Notice that the latter expression is defined by the condition of compact support.
+
+The local cohomology of $\cL=\cT_X$, the local Lie algebra of holomorphic vector fields on a complex manifold $X$, has been characterized in \cite{BWgf}.
 In the theorem below,~$Fr_X$ denotes the principal $U(n)$-bundle of unitary frames on $X$.
 
-\begin{thm}
+\begin{thm}[\cite{BWgf}]
 Let $Y_n$ be the restriction of the universal principal $U(n)$-bundle to the $2n$-skeleton of $BU(n)$.
 Then
-\beqn
+\begin{equation}
 H^\bu_{loc} (\cT(X)) \cong H^\bu(Fr_X \times^{U(n)} Y_n)[2n] .
-\eeqn
+\end{equation}
 
 In particular, when $X = \C^n$ there are isomorphisms
-\beqn
-H^\bu_{loc} (\cT(\C^n)) \cong H^\bu(\lie{vect}(n))[2n] \cong H^\bu(Y_n)[2n] .
-\eeqn
+\begin{equation}
+H^\bu_{loc} (\cT(\C^n)) \cong H^\bu(\lie{vect}(n) ; \C)[2n] \cong H^\bu(Y_n)[2n] ,
+\end{equation}
+where $H^\bu(\lie{vect}(n) ; \C)$ is the Gelfand--Fuks Lie algebra cohomology of $\lie{vect}(n)$ with trivial coefficients.
 \end{thm}
@@
 A simple application of the Serre spectral sequence reveals that in this case 
-\beqn
-H^1_{loc}(\cT(\C^n)) = H^{2n+1}(\lie{vect}(n)) = H^{2n+2} (BU(n)) .
-\eeqn
-So, degree one local cohomology classes for $\cT(\C^n)$ are in one-to-one correspondence with degree $2n+2$ polynomials in the universal Chern classes $c_1,\ldots,c_n$.
+\begin{equation}
+H^1_{loc}(\cT(\C^n)) \simeq H^{2n+1}(\lie{vect}(n)) \simeq H^{2n+2} (BU(n)) .
+\end{equation}
+So, degree one local cohomology classes for $\cT$ are in one-to-one correspondence with degree $2n+2$ polynomials in the universal Chern classes $c_1,\ldots,c_n$.
 
@@
 At this point, we can see how central extensions of the $n$-dimensional Witt algebra appear.
-We have pointed out in \eqref{eqn:localtocompact} how local cohomology classes of a local Lie algebra $\cL$ supported on $U$ determine Lie algebra cohomology classes for the Lie algebra of compactly supported sections $\cL_c(U)$.
+The morphism \eqref{eqn:localtocompact} shows how local cohomology classes of a local Lie algebra $\cL$ supported on $U$ determine Lie algebra cohomology classes for the Lie algebra of compactly supported sections $\cL_c(U)$.
 We showed in appendix \ref{appx:A} that the $n$-dimensional Witt algebra $\lie{witt}(n)$ admits a homomorphism of dg Lie algebras
-\beqn
+\begin{equation}
 j \colon \lie{witt}(n) \hookrightarrow \Omega^{0,\bu} (\C^n - \{0\}, \T) = \cT(\C^n - \{0\}),
-\eeqn
+\end{equation}
 which has the property that in cohomology $H^\bu(j)$ is a dense embedding of topological vector spaces.
@@
 The differential is 
-\beqn
+\begin{equation}
 \d_{dR} \otimes \id + \id \otimes \dbar_{\lie{witt}},
-\eeqn
+\end{equation}
 where the first term is the de Rham operator on $\R$ and the second is the internal differential to the dg Lie algebra $\lie{witt}(n)$.
 The bracket is
-\beqn\label{eqn:tensorbracket}
+\begin{equation}\label{eqn:tensorbracket}
 [\eta \otimes X, \theta \otimes Y] = (\eta \theta) \otimes [X,Y] , \quad \eta,\theta \in \Omega^\bu(\R), \;\; X,Y \in \lie{witt}(n)
-\eeqn
+\end{equation}
 where $[-,-]$ is the Lie bracket in $\lie{witt}(n)$.
-Using $j$ we will construct a map (up to homotopy) of the form
-\beqn
-\til j \colon \Omega^\bu_c (\R) \otimes \lie{witt}(n) \to \cT_c (\C^n - 0)
-\eeqn
-as follows.
+Using $j$ we now construct a map (up to homotopy) of the form
+\begin{equation}\label{eqn:tilj}
+\til j \colon \Omega^\bu_c (\R) \otimes \lie{witt}(n) \to \cT_c (\C^n - 0) .
+\end{equation}
 
@@
 We now construct an $L_\infty$ equivalence 
-\beqn
+\begin{equation}
 \Phi = (\Phi^{(1)}, \Phi^{(2)}) \colon \Omega^\bu(\R) \otimes \lie{witt}(n) \rightsquigarrow \cL_{log} .
-\eeqn
+\end{equation}
 Let $\Phi^{(1)} = \id$ and 
@@
 In particular, the map $\Phi$ defines a quasi-isomorphism of commutative dg algebras
-\beqn
+\begin{equation}
 \Phi^* \colon C^\bu(\cL_{log,c}(\R)) \xto{\simeq} C^\bu(\Omega^{\bu}_c(\R) \otimes \lie{witt}(n))
-\eeqn
+\end{equation}
 which restricts to a quasi-isomorphism
-\beqn
+\begin{equation}
 \Phi^* \colon C_{loc}^\bu(\cL_{log}) \xto{\simeq} C_{loc}^\bu(\Omega^\bu(\R) \otimes \lie{witt}(n)) .
-\eeqn
+\end{equation}
 \end{prop}
@@
 Next we define a homomorphism of dg Lie algebras
-\beqn
+\begin{equation}
 \til j \colon \cL_{log}(\R) \to \cT(\C^n - \{0\})
-\eeqn
+\end{equation}
 by the formulas
@@
 The cochain map
-\beqn
-\til j^* \colon C^\bu (\cT_c(\C^n - 0)) \to C^\bu \left(\cL_c(\R) \right)
-\eeqn
+\begin{equation}
+\til j^* \colon C^\bu (\cT_c(\C^n - 0)) \to C^\bu \left(\cL_{log,c}(\R) \right)
+\end{equation}
 given by restriction along $\til j$ preserves local cochains. 
@@
 Thus, $\til j$ determines a homomorphism
-\beqn
+\begin{equation}
 \til j^* \colon C^\bu_{loc}(\cT(\C^n-0)) \to C^\bu_{loc}\left(\cL_{log}\right)^{\R} .
-\eeqn
+\end{equation}
 \end{lem}
@@
 Then
-\beqn
+\begin{equation}
 H_{loc}^\bu\left(\Omega^\bu_\R \otimes \lie{g}\right)^\R \cong H^{\bu+1}(\lie{g}) .
-\eeqn
+\end{equation}
 \end{lem}
@@
 In \cite[??]{CostelloBook} it is shown that a choice of a flat connection on $E$ produces a quasi- isomorphism 
-\beqn
-\oloc(E)^{\R^n} \simeq \left(\cO(J_0 E) \slash \C\right) \otimes^{\mathbb{L}}_{\R[\del_1,\ldots,\del_n]} |\det|_{\R^n},
-\eeqn
+\begin{equation}
+\oloc(E)^{\R^n} \simeq \left(\cO(J_0 E) \slash \C\right) \otimes^{\mathbf{L}}_{\R[\del_1,\ldots,\del_n]} |\det|_{\R^n} \end{equation}
 where $\del_i$ are the coordinate vector fields and $J_0 E$ denotes the fiber of the $\infty$-jet bundle of $E$ at the origin $0 \in \R^n$.
@@
 Then, this result says that
-\beqn
+\begin{equation}
 C^\bu_{loc}(\cL)^{\R^n} \simeq C^\bu_{red}(J_0 L) \otimes^{\mathbb{L}}_{\R[\del_1,\ldots,\del_n]} |\det|_{\R^n} 
-\eeqn
+\end{equation}
 where $J_0 L$ is the topological Lie algebra obtained by taking the $\infty$-jets of $L$ at $0 \in \R^n$, and is equipped with the bracket obtained by Taylor expanding the bracket on $L$.
@@
 Then, by the formal Poincar\'e lemma
-\beqn
+\begin{equation}
 (J_0 L, \d_{dR}) \simeq \left(\C[[x,\d x]] \otimes \lie{g}, \d_{dR} \otimes \id\right) \simeq \left(\lie{g}, \d = 0\right) .
-\eeqn
+\end{equation}
 This implies the result.
@@
 Combining all of these results, we see that the composition
-\beqn
+\begin{equation}
 C_{loc}^\bu (\cT) \xto{\til j^*} C^\bu_{loc}(\cL_{log})^{\R} \xto{\Phi^*} C^\bu_{loc}(\Omega^\bu_\R \otimes \lie{witt}(n))^{\R} 
-\eeqn
+\end{equation}
 defines, at the level of degree one cohomology, a linear map
-\beqn
+\begin{equation}
 H^{2n+2}(BU(n)) \to H^{2} (\lie{witt}(n)) .
-\eeqn
+\end{equation}
 
 \begin{dfn}
-Every degree $2n+2$ polynomial $\bfc \in H^{2n+2}(BU(n))$ in the universal Chern classes $c_1,\ldots,c_n$ determines a central extension of the dg Lie algebra $\lie{witt}(n)$.
-We denote this central extension
-\beqn
-0 \to \C \to \lie{vir}_{\bfc}(n) \to \lie{witt}(n) \to 0 ,
-\eeqn
-and refer to it as the $n$-dimensional Virasoro Lie algebra of central charge $\bfc$.
+Let $\bc \in H^{2n+2}(BU(n))$ be a degree $2n+2$ polynomial in the universal Chern classes $c_1,\ldots,c_n$.
+Define $\lie{vir}_{\bc}(n)$ to be the central extension of dg Lie algebras
+\begin{equation}
+0 \to \C \to \lie{vir}_{\bc}(n) \to \lie{witt}(n) \to 0  \quad .
+\end{equation}
+We refer to this as the $n$-dimensional Virasoro Lie algebra of \defterm{central charge} $\bc$.
 \end{dfn}
@@
 We can be explicit about the correspondence between universal characteristic classes and central extensions of $\lie{witt}(n)$ for small values of $n$.
-When $n = 1$ we have $\lie{witt}(1) = \C[z^\pm] \del_z$.
-Following \cite{BWgf}, the class $c_1^2 \in H^4(BU(1))$ corresponds to the local cocycle
-\beqn
+The Lie algebra $\lie{witt}(1)$ is the ordinary Witt algebra consisting of expressions $f(z) \del_z$ where $f(z) \in \C((z))$.
+Following \cite{BWgf}, the class $c_1^2 \in H^4(BU(1))$ is proportional to the local cocycle
+\begin{equation}
 \int_{\C} J \mu \del J \mu
-\eeqn
+\end{equation}
 where $\mu = \alpha (z,\zbar) \del_z$ is a section of $\cT$ and $J \mu = \del_z \alpha(z,\zbar)$.
 Following the above restrictions and equivalences, we see that this corresponds to the usual Virasoro cocycle
-\beqn
-(f \del_z, g \del_z) \mapsto \op{Res}_z f'(z) g''(z) \d z , \quad f,g \in \C[z^\pm]
-\eeqn
+\begin{equation}
+(f \del_z, g \del_z) \mapsto \op{Res}_z f'(z) g''(z) \d z , \quad f,g \in \C((z))
+\end{equation}
 Of course, in this case, all Virasoro Lie algebras corresponding to a nonzero central charge are isomorphic.
 
-Next consider $n=2$, so that the possible central charges are linear combinations of $c_1^3, c_1 c_2 \in H^4(BU(2))$.
-For simplicity, consider the class $c_1^3$.
-It is shown in \cite{BWgf} that a local cocycle representative corresponding to this class is a multiple of
-\beqn
+Next consider $n=2$, so that the possible central charges are linear combinations of $c_1^3$ and $c_1 c_2 \in H^4(BU(2))$.
+Consider first the class $c_1^3$.
+It is shown in \cite{BWgf} that a local cocycle representative corresponding to this class is proportional to
+\begin{equation}
 \int_{\C^2} \op{Tr}(J \mu) \del \op{Tr}(J \mu) \del \op{Tr}(J \mu) .
-\eeqn
+\end{equation}
 The corresponding degree two cocycle of $\lie{witt}(2)$ is
-\beqn
+\begin{equation}
 c_1^3 \colon (\mu_0,\mu_1,\mu_2) \mapsto \op{Res}_z \op{Tr}(J \mu_0) \del \op{Tr}(J \mu_1) \del \op{Tr}(J \mu_2)
-\eeqn
+\end{equation}
 where $\mu_i \in \lie{witt}(2)$.
-Here $\op{Res}_z \colon H^1(\sfA_2) \to \C$ is the higher residue as defined in appendix \ref{appx:model}.
+Here $\op{Res}_z \colon \sfA_2 \to \C[-1]$ is the higher residue as defined in appendix \ref{appx:model}, see also \cite{FHK}.
 We observe that sense the residue carries degree one, and that the cocycle above is of polynomial degree three, that $c_1^3$ of $\lie{witt}(2)$ is of total degree two as desired.
-As another example, the $2$-dimensional Virasoro algebra of central charge $c_1\op{ch}_2 = \frac12 (c_1^3 - 2 c_1 c_2)$ is determined by the degree two cocycle
-\beqn
+The other class of two-dimensional Virasoro algebras are of central charge proportional to $c_1\op{ch}_2 = \frac12 (c_1^3 - 2 c_1 c_2)$.
+This central extension is represented by the three-linear cocycle
+\begin{equation}
 c_1 \ch_2 \colon (\mu_0,\mu_1,\mu_2) \mapsto \op{Res}_z \op{Tr}(J \mu_0) \op{Tr}(\del J \mu_1 \del J \mu_2) + \cdots ,
-\eeqn
+\end{equation}
 where the $\cdots$ denote appropriate anti-symmetrization.
@@
 It is shown in \cite{CG1} how the assignment of the graded vector space
-\beqn
+\begin{equation}
 \Sym \, \cE_c(U) = \oplus_{n \geq 0} \Gamma_c(U, \Sym^n E)
-\eeqn
+\end{equation}
 to an open set $U \subset M$ assemble into a factorization algebra on $M$.
@@
 Applying the above construction to $E[-1] = L$ gives rise \cite{CG2} to the factorization algebra which assigns to an open set $U \subset M$ the graded vector space 
-\beqn
+\begin{equation}
 \Sym \, \cL_c (U) [1] .
-\eeqn
+\end{equation}
 For each open set $U$ this graded vector space is equipped with a differential $\d_{CE}$ whose cohomology computes the Lie algebra homology of the dg Lie algebra $\cL_c(U)$.
@@
 Then $\phi$ can be expressed as
-\beqn
+\begin{equation}
 \phi = \phi_1 + \phi_2 + \cdots 
-\eeqn
+\end{equation}
 where $\phi_i$ carries polynomial degree $i$ and internal cohomological degree $k-i$.
@@
 It then defines an $L_\infty$-algebra central extension
-\beqn
+\begin{equation}
 0 \to \C K [k-2] \to  \til{\lie{g}} \to \lie{g} \to 0
-\eeqn
+\end{equation}
 with $\ell$-ary brackets defined by
@@
 The $\ell$-ary bracket is
-\beqn
+\begin{equation}
 [x_1,\ldots,x_\ell]_\ell = K \phi_\ell(x_1,\ldots,x_\ell) .
-\eeqn
+\end{equation}
 \end{itemize}
@@
 For every open set $U \subset M$ there is a cochain map
-\beqn
+\begin{equation}
 C^\bu_{loc}(\cL)(U) \to C^\bu(\cL_c(U))
-\eeqn
+\end{equation}
 So local cocycles define cocycles for the cosheaf of dg Lie algebras $U \mapsto \cL_c(U)$.
 In particular, $\phi$ defines a precosheaf of $L_\infty$ algebras
-\beqn
+\begin{equation}
 0 \to \ul \C[-1] \to \til \cL_c \to \cL_c \to 0 ,
-\eeqn
+\end{equation}
 where $\ul \C[-1]$ is the constant precosheaf which assigns $\C[-1]$ in degree $+1$ to every open set.
 In \cite{CG2} it is shown that the assignment
-\beqn
+\begin{equation}
 U \subset M \mapsto C_\bu(\til \cL_c (U)) 
-\eeqn
+\end{equation}
 defines a factorization algebra on $M$ in $\C[K]$-modules (where, now $K$ has degree zero).
@@
 Fix a complex dimension $n$ and let
-\beqn
-\bfc \in H^{2n+2}(BU(n)) \cong H^1_{loc}(\cT_{\C^n}) .
-\eeqn
+\begin{equation}
+\bc \in H^{2n+2}(BU(n)) \cong H^1_{loc}(\cT_{\C^n}) .
+\end{equation}
 The \defterm{Virasoro factorization algebra} on $\C^n$ is the twisted enveloping factorization algebra of $\cT_{\C^n}$ corresponding to this local cohomology class
-\beqn
-\Vir_{\bfc} \define C_\bu^{\bfc}(\cT_{\C^n,c})|_{K=1} .
-\eeqn
+\begin{equation}
+\Vir_{\bc} \define C_\bu^{\bc}(\cT_{\C^n,c})|_{K=1} .
+\end{equation}
 \end{dfn}
 
-The primary motivation for this terminology is the main result of \cite{BWvir} which exhibits the relationship between the $n=1$ Virasoro factorization algebra and the Virasoro vertex algebra.
-Recall that there is a systematic relationship between (algebro-geometric) factorization algebras on $M = \C$ and vertex algebras \cite{BD}.
-In \cite{CG1}, this relationship is made precise in the form of a functor $\VV$ from a certain category of `tame' holomorphic factorization algebras on $M = \C$ to the category of ($\Z$-graded) vertex algebras.
+Some motivation for this terminology is the result of \cite{BWvir} which exhibits the relationship between the ordinary ($n=1$ dimensional) Virasoro factorization algebra and the Virasoro vertex algebra.
+In \cite{CG1}, it is shown that the cohomology (evaluated on a formal disk) of appropriately structured \textit{holomorphic} factorization algebras on $\Sigma=\C$ are endowed with the structure of a vertex algebra.
+This turns into a functor $\VV$ from a certain category of `tame' holomorphic factorization algebras on $\Sigma = \C$ to the category of $\Z$-graded vertex algebras.
 
@@
 For $c \in \C$ consider the class
-\beqn
-\frac{c}{24} c_1^2 \in H^4(BU(1)) 
-\eeqn
-and the associated Virasoro factorization algebra $\Vir_{c c_1^2/24}$ on $\C$.
-This is a tame holomorphic factorization algebra and its associated vertex algebra $\VV(\Vir_{c c_1^2/24})$ is equivalent to the Virasoro vertex algebra of central charge $c$.
+\begin{equation}
+\frac{c}{12} c_1^2 \in H^4(BU(1))
+\end{equation}
+and the associated Virasoro factorization algebra $\Vir_{c c_1^2/12}$ on $\C$.
+This is a tame holomorphic factorization algebra and its associated vertex algebra $\VV(\Vir_{c c_1^2/12})$ is equivalent to the Virasoro vertex algebra of central charge $c$.
 \end{thm}
 
-We now arrive at the main definition of this section.
-To set it up, we recall some notions.
-
-\begin{dfn}
-A \textit{holomorphic structure} on a factorization algebra $\cF$ on $\C^n$ of central $\bfc \in H^{2n+2}(BU(n))$ is a map of factorization algebras
-\beqn
-\bT \colon \Vir_{\bfc} \to \cF .
-\eeqn
+We now arrive at the main definition of this paper.
+
+\begin{dfn}\label{dfn:hol}
+A \defterm{holomorphic structure} on a factorization algebra $\cF$ on $\C^n$ of central charge $\bc \in H^{2n+2}(BU(n))$ is a map of factorization algebras
+\begin{equation}
+\bT \colon \Vir_{\bc} \to \cF .
+\end{equation}
 \end{dfn}
 
+Largely, the goal of the rest of the paper is to produce examples of holomorphic structures on factorization algebras which are associated to ``free'' quantum field theories which will be introduced in section \ref{s:free}.
+We will also study algebraic consequences of this structure in the form of representations for the higher Virasoro algebra.
+We turn to this now.
+
 \subsection{Relationship to higher Virasoro Lie algebras}
@@
 In this section we show how to produce central extensions of $\lie{witt}(n)$ using factorization algebras.
-Let $\bfc$ be as in definition \ref{dfn:vir} and consider the associated Virasoro factorization algebra on $\C^n$ by $\Vir_{\sfc}$.
+Let $\bc$ be as in definition \ref{dfn:vir} and consider the associated Virasoro factorization algebra on $\C^n$ by $\Vir_{\sfc}$.
 
 \begin{lem}
-There is an $T^n = S^1\times \cdots \times S^1$-action on the factorization algebra $\Vir_{\sfc}$ which covers the $T^n$ action on $\C^n$ rotating each coordinate plane.
+There is an $U(n)$-action on the factorization algebra $\Vir_{\sfc}$ which covers the linear action on $\C^n$.
 \end{lem}
 \begin{proof}
-There's a natural action of $T^n$ on the Dolbeault complex
-\beqn
-\cT = \Omega^{0,\bu}(\C^n, T)
-\eeqn
-induced by pullback of forms.
-Since rotation is holomorphic, this is equivariant for the $\dbar$-operator and is compatible with the Lie bracket of vector fields.
-This implies that there is a $T^n$ action on the untwisted factorization enveloping algebra $\Vir_{0}$.
-
-For the case $\bfc \ne 0$ we need to see that the corresponding local functional is invariant under such rotations.
-If $\sum_i g_i(z) \del_{z_i}$ is a vector field then rotation by $\lambda \in S^1$, the $i$th circle, gives the vector field $\sum_i \lambda_i^{-1} g_i(\lambda_i z) \del_{z_i}$ \brian{A little stuck} 
+Any holomorphic diffeomorphism induces an automorphism of the Dolbeault complex with coefficients in any natural holomorphic vector bundle.
+In particular, there is a $GL(n,\C)$ action on the untwisted factorization enveloping algebra $\Vir_{0}$.
+
+For the case $\bc \ne 0$ we need to see that the corresponding local functional is invariant under such rotations.
+This is by construction: the local functional corresponding to $\mathbf{c}$ originates from an $n$-dimensional universal characteristic class, which is manifestly $U(n)$-invariant.
+%If $\sum_i g_i(z) \del_{z_i}$ is a vector field then rotation by $\lambda \in S^1$, the $i$th circle, gives the vector field $\sum_i \lambda_i^{-1} g_i(\lambda_i z) \del_{z_i}$ \brian{A little stuck}
 \end{proof}
 
-We restrict the factorization algebra $\Vir_{\bfc} |_{\C^n - \{0\}}$ to define a factorization algebra the punctured plane $\C^n - \{0\}$.
+We restrict the factorization algebra $\Vir_{\bc} |_{\C^n - \{0\}}$ to define a factorization algebra the punctured plane $\C^n - \{0\}$.
 Let 
-\beqn
+\begin{equation}
 \rho \colon \C^n - \{0\} \to \R_+
-\eeqn
+\end{equation}
 be the square of the radius $(z_1,\ldots,z_n) \mapsto |z_1|^2 + \cdots + |z_n|^2$, and consider the resulting factorization algebra 
-\beqn
-\rho_* \left(\Vir_{\bfc} |_{\C^n - \{0\}}\right)
-\eeqn
-on $\R_+$ whose value on an open interval $I \subset \R_+$ is the value of $\Vir_{\bfc}$ on the open annular region $\rho^{-1}(I) \subset \C^n$.
-
-For $\bfk = (k_1,\ldots,k_n)\in \Z^n$, denote by $\cF_{\bfc}^{(\bfk)}$ the $\bfk$-eigenspace for this $T^n$ action.
-Define the factorization algebra
-\beqn
-\cF_{\bfc} \define \oplus_{\bfk \in \Z^m} \cF_{\bfc}^{(\bfk)} .
-\eeqn
+\begin{equation}
+\cF_{\bc} \define \rho_* \left(\Vir_{\bc} |_{\C^n - \{0\}}\right)
+\end{equation}
+on $\R_+$ whose value on an open interval $I \subset \R_+$ is the value of $\Vir_{\bc}$ on the open annular region $\rho^{-1}(I) \subset \C^n$.
+
+Let $\cA_{0}$ be one-dimensional enveloping factorization algebra associated to the local Lie algebra $\Omega^{\bu}_{\R} \otimes \lie{witt}(n)$.
+Its underlying associative algebra is the ordinary (or $\mathbb{E}_1$) enveloping algebra $U \lie{witt}(n)$.
+The map $\til j$ from equation \eqref{eqn:tilj} defines an injective map of factorization algebras
+\begin{equation}\label{eqn:injective}
+\til j \colon \cA_{0} \to \cF_{0} .
+\end{equation}
+
+For $k \in \Z$, define the factorization algebra
+\begin{equation}
+\cA_{\bc} \define \bigoplus_{\bk \in \Z^m} \cF_{\bc}^{(k)} ,
+\end{equation}
+where $\cF_{\bc}^{(k)}$ denotes the weight $k$ eiegenspace for the diagonal $S^{1} \subset U(n)$ action.
 
 \begin{prop}
-The factorization algebra $\cF_{\bfc}$ is a locally constant factorization algebra on~$\R_+$. 
-Its associated $\mathbb{E}_1$-algebra is the $\mathbb{E}_1$-enveloping algebra of the dg Lie algebra $\vir_{\bfc}$ given by the central extension
-\beqn
-0 \to \C \to \lie{vir}_{\bfc} (n) \to \lie{witt}(n) \to 0
-\eeqn
-determined by the degree two cocycle which is the image of $\bfc$ 
-\beqn
+The factorization algebra $\cF_{\bc}$ is a locally constant factorization algebra on~$\R_+$. 
+Its associated $\mathbb{E}_1$-algebra is the $\mathbb{E}_1$-enveloping algebra of the dg Lie algebra $\vir_{\bc}$ given by the central extension
+\begin{equation}
+0 \to \C \to \lie{vir}_{\bc} (n) \to \lie{witt}(n) \to 0
+\end{equation}
+determined by the degree two cocycle which is the image of $\bc$ 
+\begin{equation}
 H^1_{loc}(\cT
-\eeqn
+\end{equation}
 \end{prop}
@@
 
-\section{Deligne truncations of de Rham cohomology}
-
-\subsection{Closed forms in complex geometry}
-
-If $X$ is a complex manifold, and $k$ a non-negative integer, let 
-\beqn
-\Omega^{k,\bu}(X) = \Omega^{0,\bu}(X, \wedge^p \T_X)
-\eeqn
-be the graded vector space of $(k,\bu)$ forms on $X$, where the space of $(p,q)$ forms sit in cohomological degree $q$.
-This graded vector space is equipped with the natural $\dbar$ operator turning $\Omega^{p,\bu}(X)$ into a dg $\Omega^{0,\bu}(X)$-module.
-
-For $U \subset X$ any open set, we can also consider the complex of $(p,\bu)$-forms supported on $U$.
-In fact, $U \mapsto \Omega^{p,\bu}(U)$ defines a sheaf of cochain complex which by Dolbeault's theorem is quasi-isomorphic to the sheaf of holomorphic $p$-forms $\Omega^{p,hol}_X$.
-
-The holomorphic de Rham operator is of the form
-\beqn
-\del \colon \Omega^{p,\bu}_X \to \Omega^{p+1,\bu}_X .
-\eeqn
-The total complex
-\beqn
-\left(\Omega^{\bu,\bu}_X , \dbar + \del\right) = \left(\oplus_{p} \Omega^{p,\bu}_X [-p], \dbar + \del \right) 
-\eeqn
-is quasi-isomorphic to the (complexified) smooth de Rham complex $\Omega^\bu_X$ equipped with the smooth de Rham differential.
-
-We are interested in a truncation of the full de Rham complex.
-Define the following sheaf of cochain complexes 
-\beqn
-\Omega^{\geq p, \bu}_X \define \left(\Omega^{p,\bu} \xto{\del} \Omega^{p+1,\bu}[-1] \xto{\del} \cdots \right) 
-\eeqn
-where the $\dbar$ operator is left implicit.
-Explicitly, a section of this sheaf of cohomological degree $k$ is a sum of $(p',q)$ forms where $p' + q = k$ and $p' \geq p$.
-
-\begin{prop}
-The complex of sheaves $\Omega^{\geq p, \bu}_X$ is a free resolution of the sheaf of $\del$-closed, holomorphic $p$-forms on $X$.
-\end{prop}
-
-\begin{dfn}
-Let $X$ be an $(2n+1)$-dimensional complex manifold, define $\cB_X$ to be the sheaf of cochain complexes 
-\beqn
-\fields_X \define \Omega^{\geq n+1, \bu}_X [n] .
-\eeqn
-This is the complex resolving the sheaf of closed $(n+1)$-forms placed in cohomological degree $-n$.
-\end{dfn}
+%\section{Deligne truncations of de Rham cohomology}
 
 \section{Free-field factorization algebras}
-
-In this section we introduce the sort of `free' factorization algebras which we will realize symmetries by the higher dimensional Virasoro algebras that we introduced in the last section.
+\label{s:free}
+
+In this section we introduce the sort of `free' factorization algebras which we will use to realize symmetries by the higher dimensional Virasoro algebras introduced in the last section.
 The contents of this section are only a mild generalization of \cite[\S 8.1]{CG2} which associates a factorization algebra of quantum observables to free quantum field theories.
@@
 cit.} the definition of a free quantum field theory requires non-degeneracy of the two-form on the space of fields; in other words, it pertains to the Batalin--Vilkovisky (BV) quantization of a $(-1)$-shifted symplectic space.
-In this section we weaken non-degeneracy defining the free classical field theoruy; or equivalently, we start with a type of $(-1)$-shifted presymplectic structure.
+In this section we weaken non-degeneracy defining the free classical field theory; or equivalently, we start with a type of $(-1)$-shifted presymplectic structure.
 Because of the strict assumptions we place on the $(-1)$-shifted presymplectic structure, we can associate to it a $\PP_0$-factorization algebra.
@@
 
+In fact, there is a more direct approach to constructing this factorization algebra, which follows very closely the well-known Heisenberg algebra construction
+
 \subsection{Weyl factorization algebras}
@@
 
-Suppose that $V$ is a symplectic vector space with symplectic form $\omega$.
-The Heisenberg Lie algebra is the central extension of $V$ (viewed as an abelian Lie algebra) defined by $\omega$, viewed as a $2$-cocycle.
-The non-degeneracy of $\omega$ is not important for this construction, any $\omega \in \wedge^2 V^*$ defines a central extension of~$V$.
-The Weyl algebra associated to $V$ is the universal enveloping algebra of this central extension where the central parameter is set to the unit.
+Suppose that $V$ is a symplectic vector space with symplectic form $\eta$.
+The Heisenberg Lie algebra is the central extension of $V$, viewed as an abelian Lie algebra, defined by $\eta$, viewed as a $2$-cocycle.
+The non-degeneracy of~$\eta$ is not essential for this construction, any $\eta \in \wedge^2 V^*$ defines the central extension
+%In fact, if $(V,Q)$ is a cochain complex, then any $Q$-closed element
+%\begin{equation}
+%\eta \in \Sym(V^*[-1])
+%\end{equation}
+%of total degree two defines a central extension of dg Lie algebras\footnote{In fact, if we just require that $\eta$ be of total cohomological degree $2$ in this graded symmetric algebra, then when we will find is $L_{\infty}$-central extensions of $V$.}
+\begin{equation}
+0 \to \C \to \lie{heis}(V,\eta) \to V \to 0 .
+\end{equation}
+The (dg) Weyl algebra associated to $V,\eta$ is the universal enveloping algebra of this central extension where the central parameter is set to the unit.
 In this section we review a factorization algebra enhancement of this construction.
 
-Consider a complex of vector bundles $(\cE,Q)$ on a manifold $M$.
-By applying the construction of the enveloping factorization algebra, recalled in \ref{s:enveloping}, to the abelian local Lie algebra $L = E[-1]$ we obtain the factorization algebra
-\beqn
-\Sym(\cE_c) \colon U \subset M \mapsto \Sym(\cE_c(U)) .
-\eeqn
-Now, fix the data of a local functional 
-\beqn
-\omega \in \oloc(E)
-\eeqn
+We will modify/generalize this construction in two ways:
+\begin{itemize}
+  \item[(1)] $V$ is a cochain complex and is equipped with a closed two-form $\eta$ of total degree $+1$.
+  \item[(2)] $V$ is a complex of vector bundles over a (spacetime) manifold $M$. Then, we require this degree $+1$ two-form $\eta$ is ``local'' in a certain sense.
+\end{itemize}
+
+For the first item, we proceed totally analogously as in the usual Heisenberg algebra.
+Suppose $(V,Q)$ is a cochain complex and $\eta$ is a $Q$-closed graded skew symmetric bilinear form on $V$ of total degree $+1$.
+Then the shifted Heisenberg algebra is a dg Lie algebra central extension
+\begin{equation}\label{eqn:shifted}
+0 \to \C[-1] \to \lie{heis}(V,\eta) \to V \to 0 .
+\end{equation}
+
+Consider now a complex of vector bundles $(V,Q)$ on a manifold $M$.
+So, now $V \to M$ is a $\Z$-graded vector bundle with sheaf of sections $\cV = \Gamma(M,V)$ and $Q \colon \cV \to \cV[1]$ is a square-zero differential operator of degree $+1$.
+By applying the construction of the enveloping factorization algebra, recalled in \ref{s:enveloping}, to the abelian local Lie algebra $L = V[-1]$ we obtain the factorization algebra
+\begin{equation}
+\Sym(\cV_c) \colon U \subset M \mapsto \Sym(\cV_c(U)) .
+\end{equation}
+The differential is $Q$ which acts as a graded derivation.
+
+In the context of vector bundles, we need to assume that the functional $\eta$ is local in the sense that it is given by the integral of a Lagrangian density.
+Thus, we fix a local functional
+\begin{equation}
+\eta \in \oloc(V)[1]
+\end{equation}
 of cohomological degree $+1$ which satisfies $Q \omega = 0$.
-In other words, this is a local cocycle for the abelian local Lie algebra $L = E[-1]$ of degree $+1$.
-By applying the twisted factorization enveloping algebra construction to this local cocycle, we obtain the following.
+In other words, this is a local cocycle for the abelian local Lie algebra $L = V[-1]$ of degree $+1$.
+Notice that in this form, $\eta$ is not necessarily quadratic and could have arbitrary polynomial degree.
+Although, for most examples $\eta$ will be quadratic (but not necessarily non-degenerate).
+
+Associated to $\eta$ an operator $\triangle_{\eta}$ acting on $\Sym(\cV_{c})$ is defined.
+It is an example of a Batalin--Vilkovisky (BV) operator, which we can describe explicitly.
+The local functional $\eta$ defines, for each open set $U$, a $(-1)$-shifted central extension of $L_{\infty}$ algebras
+\begin{equation}
+0 \to \C k [-1] \to \cH\lie{eis}_c(U) \to \cV_c(U) \to 0 .
+\end{equation}
+where the nontrivial operations are the differential $Q$ and the higher $\ell$-ary operation
+\begin{equation}
+[f_1,\ldots,f_\ell]_\ell = \int_U \eta_k(f_1,\ldots,f_\ell) k
+\end{equation}
+where $\eta_{\ell}$ is the $\ell$th Taylor component of $\eta$ and $f_{i}\in \cV_c(U)[-1]$.
+Notice that as graded vector spaces
+\begin{equation}
+\Sym\left(\cH\lie{eis}_c (U) [1] \right) = \Sym(\cV_c(U))[K]
+\end{equation}
+where $K$ is a parameter of degree zero.
+The differential $Q + K \triangle_\eta$ acting is the Chevalley--Eilenberg differential for $\cH\lie{eis}_c(U)$, so
+In other words, $\triangle_{\eta}$ is the component of the Chevalley--Eilenberg differential for $\cH\lie{eis}_{c}$ which does not involve $Q$.
+
+This construction is a special case of the twisted enveloping factorization algebra construction.
 
@@
 The assignment
-\beqn
-\cW_{E,\omega} \colon U \subset M \mapsto \left(\Sym(\cE_c(U))[K] \,, \, \,Q + K Q_\omega \right)
-\eeqn
+\begin{equation}
+U \subset M \mapsto \bigg(\Sym(\cV_c(U))[K] \,, \, \,Q + K \triangle_\eta \bigg)
+\end{equation}
 has the structure of a factorization algebra in the category of dg $\C[K]$-modules, where $K$ is a variable of degree zero.
-We refer to this as the \defterm{Weyl factorization algebra} associated to $E,\omega$.
 \end{prop}
 
+Let $\cW_{V,\eta}[K]$ be the factorization algebra on $M$ valued in $\C[K]$-modules described in this proposition.
+
+\begin{dfn}\label{dfn:weyl}
+The \defterm{Weyl factorization algebra} associated to the complex of vector bundles $(V,Q)$ and the local functional $\eta \in \oloc(V)[1]$ of degree one is the $K=1$ specialization $\cW_{V,\eta} \define \cW_{V,\eta}[K]|_{K=1}$.
+\end{dfn}
+
 \begin{eg}
-Let $V$ be an ordinary vector space and $\omega_V \in \wedge^2 V^*$ a symplectic form.
-Consider the complex of vector bundles on the real line
-\beqn
-\Omega^0(\R) \otimes V \xto{\d \otimes \id} \Omega^1 (\R) \otimes V ,
-\eeqn
-where $\Omega^0$ is placed in degree zero.
-Then $\omega = \int_\R \omega_V$ defines a local functional of degree $+1$ on this complex which satisfies~$\d \omega = 0$.
-The Weyl factorization algebra in this case is locally constant on $\R$ and its associated $\EE_1$-algebra is equivalent to the ordinary Weyl associative algebra on the symplectic vector space~$V$.
+Let $V_0$ be an ordinary vector space and $\omega_{V_0} \in \wedge^2 V_0^*$ a symplectic form.
+Consider the complex $\cV$ of vector bundles on the real line
+\begin{equation}
+\Omega^0(\R) [1]\otimes V_0 \xto{\d \otimes \id} \Omega^1 (\R) \otimes V_0 ,
+\end{equation}
+where $\Omega^0\otimes V$ is placed in degree $-1$.
+Then $\omega = \int_\R \omega_{V_0}$ defines a local functional of degree $+1$ on this complex which satisfies~$\d \omega = 0$.
+The Weyl factorization algebra in this case is locally constant on $\R$ and its associated $\EE_1$-algebra is equivalent to the ordinary Weyl associative algebra on the symplectic vector space~$V_0$.
 More generally, if $V$ is an $n$-shifted symplectic vector space then the corresponding local functional on the complex of vector bundles $\Omega^\bu(\R^n) \otimes V$ is also degree $+1$.
@@
 
+\begin{eg}
+  Let $\Sigma$ be a Riemann surface and consider the complex $\cV$ of vector bundles
+  \begin{equation}
+    \Omega^{0,\bu}(\Sigma)[1] = \Omega^{0,0}(\Sigma)[1] \xto{\dbar} \Omega^{0,1}(\Sigma)
+  \end{equation}
+  concentrated in degree $-1$ and zero.
+  A section of $\cV$ is denoted $\alpha$.
+  Define $\eta$ to be the local functional
+  \begin{equation}
+    \eta = \frac12 \int_{\Sigma}\alpha \del \alpha .
+  \end{equation}
+  Clearly $\dbar \eta = 0$.
+  The Weyl factorization algebra associated to $\cV,\eta$ is the factorization algebra underlying the free chiral boson CFT \cite[??]{CG}.
+\end{eg}
+
+Recall that the sheaf of local functionals associated to $V$ can be expressed in terms of polydifferential operators as
+\begin{equation}
+\oloc(V)= \prod_{n \geq 0} \op{PolyDiff}(\cV^{\times n} , \op{Dens}_{M})_{{S_{n}}}
+\end{equation}
+where $\op{Dens}_{M}$ is the bundle of densities on $M$.
+In each of the above examples the functional $\eta$ is quadratic.
+For simplicity, we will assume this from hereon.
+Thus, we can equally view $\eta$ as a graded symmetric section
+\begin{equation}
+\eta \in \Gamma(M, \op{Diff}(\cV, \cV^!))[1]
+\end{equation}
+where $\cV^{!}$ is the sheaf of sections of the Serre dual vector bundle $V^{!} = V^{*} \otimes \op{Dens}_M$.
+
+%Assume that $\eta$ is at least quadratic and consider the factorization algebra $\cW_{V,\eta}$.
+For each open set $U \subset M$, there is an increasing filtration on $\Sym(\cV_c(U))$ by polynomial degree. 
+This induces a filtration on $\cW_{V,\eta}$ as a factorization algebra.
+\begin{prop}
+The associated graded factorization algebra $\op{gr} \cW_{V,\eta}$ assigns to an open set $U \subset M$ the cochain complex
+\begin{equation}
+ \bigg(\Sym(\cV_c(U)) \,, \, \,Q \bigg) .
+\end{equation}
+Notice that this factorization algebra is independent of $\eta$.
+\end{prop}
+
+Notice that this associated graded factorization algebra agrees with the $K=0$ specialization of $\cW_{V,\eta}[K]$.
+The component of the Chevalley--Eilenberg differential $Q_\eta$, which is missing from $\op{gr} \cW_{V,\eta}$,  induces a structure on the associated graded factorization algebra.
+
+\textbf{Note}: From here on we will assume that $\eta$ is purely a quadratic local functional.
+
+Unlike $Q$--the differential induced from the linear differential acting on sections of the complex of vector bundles $V$--the operator $\triangle_\eta$ is not a derivation.
+It induces a bracket on the associated graded factorization algebra.
+To motivate it, we step aside to explain the following general construction in the setting of Lie algebras.
+
+Given an arbitrary dg Lie algebra $(\lie{g},\d_g)$, its Chevalley--Eilenberg complex is $C_\bu(\lie{g}) = \left(\Sym(g[1]), \d_{CE}\right)$ where $\d_{CE}$ is the total Chevalley--Eilenberg differential which is a sum of the linear differential $\d_{\lie{g}}$ plus the Chevalley--Eilenberg differential $\d_{[-,-]}$ associated to the bracket.
+Consider the filtration on $C_\bu(\lie{g})$ by polynomial degree. 
+The associated graded of cochain complex is $\op{gr} C_\bu(\lie{g}) = (\Sym(\lie{g}[1]) , \d_{\lie{g}})$; so, like the Chevalley--Eilenberg complex except the differential is just the linear part.
+Since $\d_{\lie{g}}$ is a derivation, we see that $\op{gr} C_\bu(\lie{g})$ is a commutative dg algebra.
+For $F,G \in \op{gr} C_\bu(\lie{g})$ we define
+\begin{equation}\label{eqn:P0}
+\{F,G\} = \d_{[-,-]} (FG) - \d_{[-,-]} (F) G \pm F \d_{[-,-]} (G) .
+\end{equation}
+For example, if $F = x, G = y \in \lie{g}[1] \subset \op{gr} C_\bu(\lie{g})$ then $\{x,y\} = [x,y]$, the original Lie bracket.
+The formula \eqref{eqn:P0} defines a bracket on $\op{gr} C_\bu(\lie{g})$ of cohomological degree $+1$, satisfies the graded Jacobi identity, is a graded derivation for the commutative product on,  and satisfies the Leibniz rule with respect to $\d_{\lie{g}}$.
+Thus, it endows $\op{gr} C_\bu(\lie{g})$ with the structure of a $\PP_0$-algebra.
+
+We are in a special case of this situation.
+For $\Phi,\Psi$ in $\op{gr} \cW_{V,\eta} (U)$ we define
+\begin{equation}
+\{F, G\} \define Q_{\eta} (F G) - Q_{\eta}(F) G \pm F Q_{\eta}(G) . \footnote{Notice that we could replace $Q_{\eta}$ by the full differential $Q + Q_{\eta}$ in this formula.}
+\end{equation}
+This bracket is of cohomological degree $+1$, satisfies the graded Jacobi identity, is a graded derivation for the commutative product on $\op{gr} \cW_{V,\eta} (U)$, and satisfies the Leibniz rule with respect to $Q$.
+In other words, it endows $\op{gr} \cW_{V,\eta}$ with the structure of a $\PP_0$-factorization algebra \cite[??]{CG2}.
+
+\subsection{Local functionals of a free theory}\label{s:localfree}
+
+Let $(E,Q)$ be a complex of vector bundles and consider its sheaf of local functionals $\oloc(E)$.
+The complex of local one-forms $\Omega^1_{loc}(E)$ is defined similarly.
+
+Concretely
+\begin{equation}
+\Omega^1_{loc}(E) \subset \prod_{n \geq 0} \Hom_{\C} (E^{\otimes n}, E^!)
+\end{equation}
+is the subcomplex of multilinear operators which are differential operators.
+The exterior derivative defines a map
+\begin{equation}
+\d \colon \oloc(V^!) \to \Omega^1_{loc} (V^!) .
+\end{equation}
+
+Suppose now that $E = V^!$ and $\eta \in \oloc(V)$ is a quadratic local functional of degree~$+1$.
+Then $\Omega^1_{loc}(E) = \Omega^1_{loc}(V^!)$. 
+The following lemma is a special case of \cite[theorem ??]{ButsonYoo} but we provide a self-contained proof as it contains formulas that we will use in the proceeding sections.
+
+\begin{lem}
+The functional $\eta$ defines a
+%\begin{equation}
+%\<-,-\>_\eta \colon \Omega^1_{loc} (V^!) \times \Omega^1_{loc}(V^!) \to \oloc(V) [1]  .
+%\end{equation}
+graded Lie bracket
+\begin{equation}
+\{-,-\} \colon \oloc(V^!) \times \oloc(V^!) \to \oloc(V^!)[1]
+\end{equation}
+of cohomological degree $+1$.
+\end{lem}
+\begin{proof}
+Suppose that the local functional $\Phi \in \oloc(V^!)$ is of polynomial degree $k$, meaning we can write it as a finite sum
+\begin{equation}
+\Phi = \sum_i \omega D^\Phi_{i,1} \cdots D^\Phi_{i,k}
+\end{equation}
+where $\omega$ is a section of $\op{Dens}_M$ and $D_{i,j}$ are differential operators $\cV^! \to C^\infty_M$.
+This local functional defines the linear map
+\begin{equation}
+\int \Phi \colon \cV_c^!(M)^{\otimes k} \to \C
+\end{equation}
+defined by
+\begin{equation}
+\alpha_1 \otimes \cdots \otimes \alpha_k \mapsto \sum_i \int_M \omega  (D_{i,1}^\Phi \alpha_1) \cdots (D_{i,k}^\Phi \alpha_k) .
+\end{equation}
+
+The differential $\d \Phi$ is of the form
+\begin{align*}
+\d \Phi & \colon \cV^!_c(M)^{\otimes (k-1)} \to \cV_c(M)  \\ & \alpha_1 \otimes \cdots \otimes \alpha_{k-1} \mapsto \sum_i \omega (D_{i,1}^\Phi \alpha_1) \cdots (D_{i,k-1}^\Phi \alpha_{k-1}) D_{i,k}(-) + \cdots
+\end{align*}
+where the $\cdots$ denotes graded symmetrization.
+The differential $\d \Phi (\alpha_1 \otimes \cdots \otimes \alpha_{k-1})$ is \textit{a priori} a distributional section of $\cV_c$, but upon integrating by parts we see that it is, in fact, a smooth section.
+
+Now, suppose $\Psi$ is of polynomial degree $\ell$.
+We have the composition
+\begin{equation}
+\cV_{c}^!(M)^{\otimes (k+\ell-2)} \xto{\d \Phi \otimes \d \Psi} \cV_c(M)^{\otimes 2} \xto{\eta} \Gamma_c(M,\op{Dens}_M)
+\end{equation}
+that we denote by $\eta\<\d \Phi, \d \Psi\>$.
+%Since polydifferential operators preserve the condition of being compactly supported, we see that $\eta\<\d \Phi, \d \Psi\>$ is compactly supported.
+Define
+\begin{equation}
+\int_M \{\Phi, \Psi\} \define \int_M \eta\<\d \Phi, \d \Psi\> \colon \cV_c^!(M)^{\otimes (k+\ell-2)} \to \C .
+\end{equation}
+This is clearly a polydifferential operator, so we see that this construction defines a local functional $\{\Phi,\Psi\} \in \oloc(V^!)$.
+\end{proof}
+
+%We consider the Serre dual $V^!$ as a complex of vector bundles.
+%As we've utilized, integration over $U \subset M$ defines an inclusion of cochain complexes
+%\begin{equation}
+%\oloc(V^!) \hookrightarrow \Sym(\cV_c(U)) .
+%\end{equation}
+%We will denote the image of a local functional $\Phi$ under this embedding by $\int_U \Phi$.
+%
+%\begin{lem}
+%Suppose that $\Phi, \Psi$ are local functionals on $V^!$, which we may view as elements in $\Sym(\cV_c(U))$ for any open set $U \subset M$.
+%Then there exists a unique local functional $\Xi$ such that $\int_U \Xi = \{\int_U \Phi, \int_U \Psi\}$.
+%\end{lem}
+
+This lemma defines a bracket on local functionals which is of cohomological degree~$+1$.
+Together with the differential $Q$ this bracket thus endows $\oloc(V^!)[-1]$ with the structure of a dg Lie algebra.
+
 \subsection{Quantization in the BV formalism}
@@
 In this section we show that the Weyl factorization algebra is also the result of a sort of quantization in the context of the Batalin--Vilkovisky (BV) formalism.
-In the case that $\omega \in \oloc(E)$ arises from a bundle morphism
-\beqn\label{eqn:nondeg}
-\omega \colon E \otimes E \to \op{Dens}_M
-\eeqn
-which is fiberwise non-degenerate then the data $(E,\omega,Q)$ defines a free BV theory in the sense of \cite[definition 4.2.0.2]{CG2}.
-In this case, the associated factorization algebra of quantum observables is quasi-isomorphic to the Weyl factorization algebra \cite[Proposition 8.1.3.1]{CG2}.
-In this section, we introduce a generalization of the notion of a free BV theory whose BV quantization is captured by the Weyl factorization algebras of the previous section.
-
-First, we recall some notation.
-The $!$-dual (or Serre dual) of a vector bundle $E$ is the bundle $E^!
+
+The following is a special case of the construction in the previous subsection.
+Suppose $(\cE,Q, \omega)$ is a free BV theory in the sense of \cite[definition 4.2.0.2]{CG2}.
+Here, $(\cE,\omega)$ is an elliptic complex of vector bundles and
+\begin{equation}\label{eqn:nondeg}
+\omega \colon E \otimes E \to \op{Dens}_M [-1]
+\end{equation}
+is a bundle map that is fiberwise non-degenerate.
+
+Recall that the $!$-dual (or Serre dual) of a vector bundle $E$ is the bundle $E^!
 = E^* \otimes \op{Dens}_M$ where $E^*$ is the ordinary dual vector bundle and $\op{Dens}_M$ is the density bundle on $M$ (an orientation is an isomorphism $\op{Dens}_M \cong \wedge^n \T_M^*$).
-The linear dual of $\cE = \Gamma(M,E)$ is $\br \cE^!_c = \br \Gamma_c(M, E^!)$ where $\br \Gamma_c$ denotes compactly supported distributional sections.
-There is hence a natural map of cosheaves
-\beqn
-\cE^!_c = \Gamma_c(M,E^!) \hookrightarrow \cE^\vee ,
-\eeqn
-which includes the smooth (non-distributional) sections.
-If $E$ is an elliptic complex of vector bundles then the above map is a quasi-isomorphism.
-In particular, one has the following.
-
-\begin{prop}[see theorem 5.4.0.1 of \cite{CG}]
-Let $(E,Q)$ be an elliptic complex of vector bundles.
-Then the inclusion
-\beqn
-\left(\Sym(\cE_c), Q\right) \hookrightarrow \left(\cO(\cE^!) , Q\right)
-\eeqn
-is an equivalence of factorization algebras.
-If $\omega \in \oloc(E)$ is non-degenerate of the form \eqref{eqn:nondeg} then this is an equivalence of $\PP_0$-factorization algebras.
+
+The section $\omega$ defines a graded bundle isomorphism $E^! \simeq E[1]$.
+In particular, there is a sequence of graded bundle isomorphisms
+\begin{align*}
+E^* \otimes E^* \otimes \op{Dens}_M [-1] & \simeq E^!
+\otimes E^!
+\otimes \op{Dens}_M^{-1} [-1] \\ & \simeq_{\omega} E \otimes E \otimes \op{Dens}_M^{-1} [-1] \\ & \simeq (E^!)^* \otimes (E^!)^* \otimes \op{Dens}_M [1]
+\end{align*}
+We gather that at the level of compactly supported sections there is an embedding
+\begin{equation}
+i \colon \Gamma_c (M, E^* \otimes E^* \otimes \op{Dens}_M) \hookrightarrow \oloc(E^!) .
+\end{equation}
+The image of $\omega$ is thus a $Q$-closed local functional $i(\omega) \in \oloc(E^!)$ for the vector bundle~$E^!$.
+
+So, if we set $V = E^!$ and $\eta = i(\omega)$, the construction of the Weyl factorization algebra of the previous section yields the factorization algebra $\cW_{E^!, i(\omega)}$.
+This is the factorization algebra of observables of the free BV theory $(E,Q,\omega)$ as in \cite{CG2}.
+
+It is in this sense that $\cW_{V,\eta}$ is a generalization of ordinary BV quantization of the BV theory whose ``fields'' are sections of the graded vector bundle $E = V^!$.
+Generally, there is no non-degeneracy requirement on the local functional $\eta \in \oloc(V)$.
+
+%First, we recall some notation.
+%
+%The linear dual of $\cE = \Gamma(M,E)$ is $\br \cE^!_c = \br \Gamma_c(M, E^!)$ where $\br \Gamma_c$ denotes compactly supported distributional sections.
+%There is hence a natural map of cosheaves
+%\begin{equation}
+%\cE^!_c = \Gamma_c(M,E^!) \hookrightarrow \cE^\vee ,
+%\end{equation}
+%which includes the smooth (non-distributional) sections.
+%If $E$ is an elliptic complex of vector bundles then the above map is a quasi-isomorphism.
+%In particular, one has the following.
+%
+%\begin{prop}[see theorem 5.4.0.1 of \cite{CG}]
+%Let $(E,Q)$ be an elliptic complex of vector bundles.
+%Then the inclusion
+%\begin{equation}
+%\left(\Sym(\cE_c), Q\right) \hookrightarrow \left(\cO(\cE^!) , Q\right)
+%\end{equation}
+%is an equivalence of factorization algebras.
+%If $\omega \in \oloc(E)$ is non-degenerate of the form \eqref{eqn:nondeg} then this is an equivalence of $\PP_0$-factorization algebras.
+%\end{prop}
+%
+%The following paragraph is a review of ideas that appear in \cite{PavelPoisson}.
+%Let $(P,\d)$ be a cochain complex. Consider the following commutative dg algebra
+%\begin{equation}
+%\op{Pol}(P,-1) \define \Sym(P^*) \otimes \Sym(P) .
+%\end{equation}
+%We consider two additional gradings on this algebra.
+%The first is by polynomial degree where $P^*$ carries weight $+1$.
+%The second endows $P$ with weight $+1$, we refer to this as the weight grading.
+%The (shifted) Schouten bracket $[-,-]_{Sch}$ endows this with the structure of a graded (unshifted) Lie algebra. 
+%It is defined on this usual way on vector fields $\Sym(P^*) \otimes P \subset \op{Pol}(P,-1)$ and extended to the full algebra by the condition that it is a graded derivation with respect to multiplication.
+%A $(-1)$-shifted Poisson structure on $P$ is an element
+%\begin{equation}
+%\pi \in \op{Pol}(P,-1) [1]
+%\end{equation}
+%of cohomological degree $+1$, concentrated in weights $\geq 2$, which satisfies the Maurer--Cartan equation
+%\begin{equation}
+%\d \pi + \frac12 [\pi,\pi]_{Sch} = 0 .
+%\end{equation}
+%Such an element can be decomposed $\pi = \pi_2 + \pi_3 + \cdots$ where $\pi_k$ has weight $k$ with respect to the weight grading.
+%Contraction with $\pi$ endows the commutative dg algebra $\cO(P)$ with a sequence of brackets $\{-,-\}, \{-,-\}_3, \ldots$ endowing it with the structure of a \textit{homotopy $\PP_0$ algebra} \cite{??}.
+%In this paper we only consider $(-1)$-shifted Poisson structures with weight $2$, hence $\cO(P)$ is an ordinary, or strict, $\PP_0$-algebra with bracket we denote by $\{-,-\}$.
+%In physics, this is the BV anti-bracket.
+%
+%Given such a $\pi$ we construct an operator $\triangle_\pi$ acting on $\cO(P)$ defined as follows.
+%Let 
+%\begin{equation}
+%\triangle_{\pi_k} \colon \Sym^k(P^*) \to \C 
+%\end{equation}
+%be contraction with $\pi_k$; extend this to ... \brian{finish}
+%
+%
+%
+%\begin{prop}
+%Let $(P,\d)$ be a cochain complex and suppose that $\pi$ is a constant coefficient $(-1)$-shifted Poisson structure on $P$.
+%Then $\triangle_\pi \circ \triangle_\pi = 0$.
+%\brian{BD quantization??}
+%\end{prop}
+%
+%\begin{dfn}\label{dfn:free}
+%A \defterm{free BV theory of Poisson type} on a manifold $M$ is an elliptic complex of vector bundles $(\cE,Q)$ on $M$ together with a local, constant coefficient, $(-1)$-shifted local Poisson tensor
+%\begin{equation}
+%\pi \in ??
+%\end{equation}
+%which satisfies $Q \pi = 0$.
+%\end{dfn}
+%
+%Now we return to the relationship to Weyl factorization algebras.
+%A $\PP_0$-structure $\pi$ as in definition \eqref{dfn:free} 
+%The factorization algebra of classical observables of a free BV theory of Poisson type is simply $\cO(\cE) = \Sym\left(\cE^\vee\right)$.
+%
+
+\section{Examples of holomorphic free field factorization algebras}
+\subsection{The higher $\beta\gamma$ system}
+
+If $X$ is a complex manifold, and $p$ a non-negative integer, let
+\begin{equation}
+\Omega^{p,\bu}(X) = \Gamma_{C^\infty}\left(X, \Sym(\br \T^*_X [-1]) \otimes \wedge^p \T^*_X\right)
+\end{equation}
+be the space of smooth sections of the graded vector bundle of $(p,\bu)$ forms on $X$, where $(p,q)$ forms sit in cohomological degree $q$.
+This complex of bundles is equipped with the natural $\dbar$ operator turning $\Omega^{p,\bu}(X)$ into a dg $\Omega^{0,\bu}(X)$-module.
+Similarly, $\Omega_{c}^{p,\bu}(X)$ is the subcomplex of compactly supported forms on $X$.
+The complex of sheaves $U \mapsto \Omega^{p,\bu}(U)$ is a free resolution for the sheaf of holomorphic $p$-forms $\Omega^{p,hol}_{X}$.
+
+We move on to our first example of this section.
+Suppose that $X$ is a complex manifold of dimension $n$.
+Define $\cV = \Gamma(X,V)$ to be the complex of vector bundles
+\begin{equation}\label{eqn:bg}
+\Omega^{0,\bu}_{X} [1] \oplus \Omega^{n,\bu}_{X} [n],
+\end{equation}
+whose sections we will denote by $(\beta,\gamma)$.
+The local functional $\eta$ is defined by
+\begin{equation}\label{eqn:etabg}
+\eta = \int \beta \wedge \gamma .
+\end{equation}
+
+The $\beta-\gamma$ \defterm{factorization algebra} on $X$ is the Weyl factorization algebra associated to this data, see definition \ref{dfn:weyl}.
+We denote it by $\beta\gamma \define \cW_{V,\eta}$.
+
+More generally, given any super vector bundle $Z \to X$, one can consider the $\beta-\gamma$ system valued (or twisted by) $Z$.
+In this case $\cV$ is the complex of bundles
+\begin{equation}\label{eqn:bgZ}
+\Omega^{0,\bu}_{X}(Z) [1] \oplus \Omega^{n,\bu}_{X}(Z^{*}) [n].
+\end{equation}
+where $Z^{*}$ is the dual bundle.
+
+In super string theory, the plain $\beta-\gamma$ system on a Riemann surface $X = \Sigma$ plays a role in BRST quantization.
+In fact, the cohomology of the factorization algebra $\beta\gamma$ on~$\Sigma=\C$ recovers the usual $\beta-\gamma$ vertex algebra \cite{CG1}.
+
+When $n=2$, the $\beta-\gamma$ system is the factorization algebra of observables of the holomorphic twist of the $\cN=1$ supersymmetric quantum field theory of a free chiral multiplet in four (real) dimensions \cite{CosYangian,ESW}.
+When $n=3$ and $Z = \Pi K^{1/2}_{X}[1]$ (this is a choice of a spin structure on the threefold $X$), the $\beta-\gamma$ system is equivalent to the holomorphic twist of the $\cN=(1,0)$ supersymmetric theory of a free hypermultiplet in six (real) dimensions \cite{ESW,SWtensor}.
+
+There are relationships among $\beta-\gamma$ systems of different dimensions.
+For example, the plain $(n+m)$-dimensional $\beta-\gamma$ system can be defined on the manifold $X \times \PP^{m}$.
+Its compactification along $\pi \colon X \times \PP^{m} \to X$ is simply the $n$-dimensional $\beta-\gamma$ system on $X$.
+That is, there is an equivalence of factorization algebras
+\begin{equation}\label{eqn:bgcompact}
+\pi_{*} \beta\gamma[X \times \PP^{m}] \simeq \beta \gamma[X] .
+\end{equation}
+Here, $\beta\gamma[Y]$ denotes the $\beta-\gamma$ factorization algebra on the complex manifold $Y$.
+
+\subsection{The higher Kac--Moody factorization algebra for $\lie{gl}(1)$}
+
+Let $X$ be a complex manifold of dimension $n$.
+Consider the shifted Dolbealt complex
+\begin{equation}\label{eqn:gl1}
+\cV = \Omega^{0,\bu}(X)[1] .
+\end{equation}
+On this complex of bundles, there is the following $(n+1)$-linear local functional
+\begin{equation}\label{eqn:km}
+\eta = \frac{1}{(n+1)!} \int \alpha \del \alpha \cdots \del \alpha .
+\end{equation}
+Though it is not quadratic (like our previous examples), it is nevertheless of total cohomological degree $+1$ and defines a factorization algebra via the construction of definition \ref{dfn:weyl}.
+We denote it by $\cU = \cW_{V,\eta}$ and refer to it as the (higher-dimensional) \defterm{$\lie{gl}(1)$ Kac-Moody factorization algebra}.
+(Notice that in this example we do not claim to construct a bracket on local functionals on $E = V^{!}$ as in the setting of section \ref{s:localfree}.)
+
+More generally, $\cU$ is an example of a higher-dimensional Kac--Moody factorization algebra as defined in \cite{GWkm}.
+For any Lie algebra $\lie{g}$, we can define the enveloping factorization algebra (see section \ref{s:enveloping}) associated to the local Lie algebra $\lie{g} \otimes \Omega^{0,\bu}(X)$.
+(This is not an example of a ``Weyl factorization algebra'' unless $\lie{g}$ is itself abelian.)
+Moreover, this can be centrally extended by a cocycle of the form $\eta$ which is defined, more generally, with the additional data of an invariant polynomial for $\lie{g}$ of degree $n+1$.
+In the case $\lie{g} = \lie{gl}(1)$ then this is no extra data at all and we recover the factorization algebra $\cU$.
+More generally, if $\theta$ is such a degree $(n+1)$ polynomial on a Lie algebra $\lie{g}$, the cocycle is
+\begin{equation}\label{eqn:km2}
+\eta_\theta = \frac{1}{(n+1)!} \int \theta(\alpha \del \alpha \cdots \del \alpha) .
+\end{equation}
+This cocycle first appeared in the work of \cite{FHK} where they used it to construct central extensions of the higher dimensional current algebra $\R\Gamma(\mathring{D}^{n},\cO) \otimes \lie{g}$.
+
+%In \cite{GWkm} we find a relationship between $\cU$ and the $\beta\gamma$, introduced in the previous section.
+
+%It is straightforward to observe the following relationship among the $\lie{gl}(1)$ Kac--Moody factorization algebras of different dimension.
+%For instance, if $\pi \colon X \times \P^{m} \to X$ is the pushforward, then
+%\begin{equation}\label{eqn:kmcompact}
+%\pi_{*}\cU[X \times \PP^{m}] \simeq \cU[X] .
+%\end{equation}
+
+\subsection{The higher-dimensional free chiral boson}
+
+The previous two examples exist in any complex dimension.
+This class of examples only exists in odd complex dimensions.
+Let $X$ be a $(2n+1)$-dimensional complex manifold.
+Consider the holomorphic de Rham operator
+\begin{equation}
+\del \colon \Omega^{p,\bu}_X \to \Omega^{p+1,\bu}_X
+\end{equation}
+acting on Dolbeault forms.
+The total complex of sheaves
+\begin{equation}
+\left(\Omega^{\bu,\bu}_X , \dbar + \del\right) = \bigg(\oplus_{p,q} \Gamma_{C^\infty}\left(X, \wedge^q \br T^*_X \otimes \wedge^p \T^*_X\right) [-p-q] \; , \; \dbar + \del \bigg) 
+\end{equation}
+is the (complexified) smooth de Rham complex $\Omega^\bu_X$ equipped with the smooth de Rham differential $\d_{dR} = \dbar + \del$.
+
+We are interested in a truncation of the full de Rham complex.
+Consider the following complex of vector bundles
+\begin{equation}
+\Omega^{\geq p, \bu}_X \define \left(\Omega^{p,\bu} \xto{\del} \Omega^{p+1,\bu}[-1] \xto{\del} \cdots \right) 
+\end{equation}
+where the $\dbar$ operator is left implicit.
+Explicitly, a section of this sheaf of cohomological degree $k$ is a sum of $(p',q)$ forms where $p' + q = k$ and $p' \geq p$.
+
+For $X$ a smooth complex manifold, it is well-known that the complex of sheaves $\Omega^{\geq p, \bu}_X$ is a free resolution of the sheaf of $\del$-closed, holomorphic $p$-forms on $X$:
+\begin{equation}
+\Omega^{k,hol,cl}_X = \cK\op{er} (\del) \subset \Omega^{k,hol}_X .
+\end{equation}
+
+Define $(E,Q)$ to be the complex of vector bundles
+\begin{equation}
+\Omega^{\geq n+1, \bu}_X [n] .
+\end{equation}
+The differential $Q$ is the component the smooth de Rham operator $\dbar + \del$.
+In other words, this is a subcomplex of the full de Rham complex.
+This is the complex resolving the sheaf of closed and holomorphic $(n+1)$-forms placed in cohomological degree $-n$.
+Thus, in this complex of bundles forms of type $(p,q)$ live in cohomological degree~$p+q-2n-1$.
+
+We will denote the Serre dual by $V = E^!$, which inherits the structure of a complex of vector bundles.
+Explicitly, the sheaf of sections of the Serre dual is
+\begin{equation}\label{eqn:bosonV}
+  \Omega^{\leq n, \bu}_X [2n+1] = \left(\Omega^{0,\bu} [2n+1] \xto{\del} \Omega^{1,\bu}[2n] \xto{\del} \cdots \Omega^{n,\bu} [n+1]\right) .
+\end{equation}
+So, in $V$, forms of type $(p,q)$ also live in cohomological degree $p+q-2n-1$ and the differential $Q$ is the components of the smooth de Rham operator $\dbar + \del$.
+We use $\alpha$ to denote a section of $\cV$.
+
+\begin{lem}
+The local functional $\eta \in \oloc(V)$ defined by
+\begin{equation}\label{eqn:bosoneta}
+\eta = \frac12 \int \alpha \del \alpha 
+\end{equation}
+is of cohomological degree one and satisfies $Q \eta = 0$.
+\end{lem}
+\begin{proof}
+$\dbar \eta = 0$ is obvious and $\del \eta = 0$ follows from $\del^2 = 0$.
+\end{proof}
+
+Define the (higher-dimensional) \defterm{chiral boson factorization algebra} $\cB$ on the $(2n+1)$-dimensional complex manifold $X$ to be the Weyl factorization algebra associated to this data, $\cB = \cW_{V,\eta}$.
+
+Take $n=0$, so $X=\Sigma$ is a Riemann surface.
+Then $\cE = \Omega^{1,\bu}_\Sigma$ and $\cV = \Omega^{0,\bu}_\Sigma [1]$.
+The factorization algebra $\cB$ describes the (perturbative) chiral boson conformal field theory.
+Indeed, in \cite[??]{CG1} it is shown that on $\Sigma = \C$ this factorization algebra produces the chiral boson vertex algebra consisting of a single field $\sfb$ of conformal weight one and OPE
+\begin{equation}
+\sfb(z) \sfb(w) \simeq \frac{1}{(z-w)^2} .
+\end{equation}
+In fact, we already covered this example.
+It is identical to the $\lie{gl}(1)$ Kac--Moody factorization algebra on a Riemann surface.
+This is a low-dimensional isomorphism, generally the chiral boson factorization algebra and (higher) $\lie{gl}(1)$
+Kac--Moody factorization algebras are different.
+
+There is the following relationship amoung the chiral boson factorization algebras of varying dimensions.
+First, we can consider the chiral boson factorization algebra on $X \times \PP^{2n}$ where $X$ is a complex manifold of dimension $2n+1$.
+Its pushforward, or compactification, along $\PP^{2n}$ returns the ordinary chiral boson factorization algebra on~$C$.
+
+\begin{prop}
+  Let $C$ be a Riemann surface.
+  If $\pi \colon C \times \PP^{2n} \to C$ is projection, then there is an equivalence of factorization algebras
+\begin{equation}\label{eqn:bosoncompact}
+\pi_{*} \cB[C \times \PP^{2n}] \simeq \cB[C] \otimes \cT
+\end{equation}
+where $\cT$ is a locally constant factorization algebra on $X$.
 \end{prop}
-
-The following paragraph is a review of ideas that appear in \cite{PavelPoisson}.
-Let $(P,\d)$ be a cochain complex. Consider the following commutative dg algebra
-\beqn
-\op{Pol}(P,-1) \define \Sym(P^*) \otimes \Sym(P) .
-\eeqn
-We consider two additional gradings on this algebra.
-The first is by polynomial degree where $P^*$ carries weight $+1$.
-The second endows $P$ with weight $+1$, we refer to this as the weight grading.
-The (shifted) Schouten bracket $[-,-]_{Sch}$ endows this with the structure of a graded (unshifted) Lie algebra. 
-It is defined on this usual way on vector fields $\Sym(P^*) \otimes P \subset \op{Pol}(P,-1)$ and extended to the full algebra by the condition that it is a graded derivation with respect to multiplication.
-A $(-1)$-shifted Poisson structure on $P$ is an element
-\beqn
-\pi \in \op{Pol}(P,-1) [1]
-\eeqn
-of cohomological degree $+1$, concentrated in weights $\geq 2$, which satisfies the Maurer--Cartan equation
-\beqn
-\d \pi + \frac12 [\pi,\pi]_{Sch} = 0 .
-\eeqn
-Such an element can be decomposed $\pi = \pi_2 + \pi_3 + \cdots$ where $\pi_k$ has weight $k$ with respect to the weight grading.
-Contraction with $\pi$ endows the commutative dg algebra $\cO(P)$ with a sequence of brackets $\{-,-\}, \{-,-\}_3, \ldots$ endowing it with the structure of a \textit{homotopy $\PP_0$ algebra} \cite{??}.
-In this paper we only consider $(-1)$-shifted Poisson structures with weight $2$, hence $\cO(P)$ is an ordinary, or strict, $\PP_0$-algebra with bracket we denote by $\{-,-\}$.
-In physics, this is the BV anti-bracket.
-
-Given such a $\pi$ we construct an operator $\triangle_\pi$ acting on $\cO(P)$ defined as follows.
-Let 
-\beqn
-\triangle_{\pi_k} \colon \Sym^k(P^*) \to \C 
-\eeqn
-be contraction with $\pi_k$; extend this to ... \brian{finish}
+\begin{proof}
+  The value of the factorization algebra $\pi_{*} \cB[X \times \PP^{2m}]$ on an open set $U \subset X$ is the graded symmetric algebra on
+  \begin{equation}\label{}
+\Omega_{c}^{\leq n+m, \bu}(U \times \PP^{m})[2n+2m+1] \simeq \Omega^{\leq n,\bu}_{c}(U) [2n+1] .
+  \end{equation}
+\end{proof}
+
+%Let $X$ be a $(2n+1)$-dimensional complex manifold and consider the complex of vector bundle $\cA = \cA_X$ from definition \ref{dfn:??}.
+%As a graded vector bundle recall that $\cA = \Omega^{\leq n, \bu} [n+1]$.
+%
+%Define the following pairing on the complex of vector bundles $\cA_{X,c}$:
+%\begin{equation}
+%\omega(\beta, \gamma) = \int_X \beta \del \gamma .
+%\end{equation}
+%One can immediately check that $\omega$ carries degree $+1$ as required for the construction of the Weyl factorization algebra.
+%Importantly, for each open $U \subset X$ the pairing $\omega$ defines the operator $\triangle$ acting on 
+%\begin{equation}
+%\Sym \left(\cA_c(U) [n+1] \right)
+%\end{equation}
+%by the following rules:
+%\begin{itemize}
+%\item If $\Phi \in \Sym^{\leq 1}$ then $\triangle \Phi = 0$.
+%\item If $\Phi = \beta \gamma \in \Sym^2$ then define
+%\begin{equation}
+%\triangle (\beta \gamma) = \omega|_{U} (\beta, \gamma) = \int_U \beta \del \gamma .
+%\end{equation}
+%\item \brian{FINISH}.
+%\end{itemize}
+%
+%\begin{dfn}
+%Let $X$ be a complex manifold of dimension $2n+1$.
+%The \defterm{free boson factorization algebra} on $X$ is
+%\begin{equation}
+%\cF \define \left(\Sym \left(\Omega^{\leq n,\bu}_{X,c} [n+1] \right) \; , \; Q + \triangle \right) ,
+%\end{equation}
+%where $\triangle$ is defined as in items (1)-(3) above.
+%In the notation of section \ref{ss:weyl}, $\cF = \cW_{\cA,\omega}$.
+%\end{dfn}
+%
+%Finally, we frame this factorization algebra as a quantization of a free BV theory.
+%First, let
+%\begin{equation}
+%\delta_\Delta \in \br\Omega^{2n+1,2n+1}(X \times X)
+%\end{equation}
+%be the $\delta$-distribution along the diagonal $X \hookrightarrow X \times X$.
+%This is a distributional form of Hodge type $(2n+1,2n+1)$ on $X \times X$.
+%Applying the holomorphic de Rham operator along one of the directions yields a distribution
+%\begin{equation}\label{eqn:fullbcov}
+%(\del \otimes \id) \delta_{\Delta} \in \br\Omega^{2n+2,2n+1}(X \times X) .
+%\end{equation}
+%This is the full BCOV propagator as introduced in \cite{CLbcov1,CLbcov2}.
+%We are only interested in a particular component of this distributional section.
+%There is a K\"unneth decomposition
+%\begin{equation}
+%\br\Omega^{2n+2,2n+1}(X \times X) = \bigoplus_{k=1}^{2n+1} C^k ,
+%\end{equation}
+%where $C^k = \oplus_{q+q'=2n+1} \br \Omega^{k,q}(X) \hotimes \br \Omega^{2n+2-k,q'}(X)$.
+%We let
+%\begin{equation}\label{eqn:poisson1}
+%\pi \in C^{n+1} = \bigoplus_{q+q'=2n+1} \br \Omega^{n+1,q}(X) \hotimes \br \Omega^{n+1,q'}(X) 
+%\end{equation}
+%be the projection of \eqref{eqn:fullbcov} to the component $C^{n+1}$.
+%
+%\begin{lem}
+%This $\pi$ determines a section
+%\begin{equation}
+%\pi \in \br \fields_X \hotimes \br \fields_X [-1]
+%\end{equation}
+%which satisfies $\d_{\fields} \pi = 0$.
+%Thus $\pi$ endows $\fields$ with the structure of a free BV theory of Poisson type.
+%\end{lem}
+%
+%\begin{prop}
+%Let $X$ be a complex manifold of dimension $2n+1$.
+%The free boson factorization algebra $\cF$ is the BV quantization of the free BV theory of Poisson type whose fields are
+%\begin{equation}
+%\fields = \Omega^{\geq n+1, \bu}_X [n]
+%\end{equation}
+%and whose $(-1)$-shifted local Poisson structure is $\pi$ as in \eqref{eqn:poisson1}.
+%More precisely, there is an equivalence of factorization algebras
+%\begin{equation}
+%\cF \xto{\simeq} \Obs^q (\fields)|_{\hbar = 1} .
+%\end{equation}
+% \end{prop}
+
+The chiral boson factorization algebras appear in string theory and supersymmetry.
+Suppose that $X$ is a complex manifold of dimension three.
+The chiral boson factorization algebra $\cB[X]$ is equivalent to the factorization algebra of observables in the holomorphic twist of the six-dimensional $\cN=(1,0)$ supersymmetric ``tensor multilpet'' theory \cite{SWtensor}.
+Concretely, the field $\beta^{2,1} + \beta^{3,0} \in \cE^{0}$ represents the components of the field strength of the infamous chiral two-form \cite{WittenM5} which survive the holomorphic twist.
+
+Suppose that $X$ is a complex manifold of dimension five.
+The factorization algebra $\cB[X]$ represents the factorization algebra underlying the (field strength) of the Ramond--Ramond four-form in the holomorphic twist of type IIB supergravity.
+Note that to understand this within supergravity, the manifold $X$ must be equipped with a Calabi--Yau structure \cite{CLsugra}.
+Nevertheless, the factorization algebra $\cB[X]$ is defined independently of such a structure.
+
+The following relationship links a few of the free-field holomorphic factorization algebras we have discussed.
 
 \begin{prop}
-Let $(P,\d)$ be a cochain complex and suppose that $\pi$ is a constant coefficient $(-1)$-shifted Poisson structure on $P$.
-Then $\triangle_\pi \circ \triangle_\pi = 0$.
-\brian{BD quantization??}
+  Let $X$ be a complex threefold and consider the chiral boson factorization algebra on $X \times \PP^{2}$.
+  Then, there is an equivalence of factorization algebras
+  \begin{equation}\label{eqn:20}
+    \pi_{*} \cB[X \times \PP^{2}] \simeq \cB[X] \otimes \beta\gamma[X] \otimes \cT
+  \end{equation}
+  where $\cT$ is a locally constant factorization algebra on $X$ and $\pi \colon X \times \PP^{2}\to X$ is projection.
+  Furthemore, this factorization algebra is equivalent to the observables underlying the holomorphic twist of the (abelian) $\cN=(2,0)$ superconformal theory on $X$.
 \end{prop}
 
-\begin{dfn}\label{dfn:free}
-A \defterm{free BV theory of Poisson type} on a manifold $M$ is an elliptic complex of vector bundles $(\cE,Q)$ on $M$ together with a local, constant coefficient, $(-1)$-shifted local Poisson tensor
-\beqn
-\pi \in ??
-\eeqn
-which satisfies $Q \pi = 0$.
-\end{dfn}
-
-Now we return to the relationship to Weyl factorization algebras.
-A $\PP_0$-structure $\pi$ as in definition \eqref{dfn:free} 
-The factorization algebra of classical observables of a free BV theory of Poisson type is simply $\cO(\cE) = \Sym\left(\cE^\vee\right)$.
-
-\subsection{The higher-dimensional free chiral boson}
-
-Let $X$ be a $(2n+1)$-dimensional complex manifold and consider the complex of vector bundle $\cA = \cA_X$ from definition \ref{dfn:??}.
-As a graded vector bundle recall that $\cA = \Omega^{\leq n, \bu} [n+1]$.
-
-Define the following pairing on the complex of vector bundles $\cA_{X,c}$:
-\beqn
-\omega(\beta, \gamma) = \int_X \beta \del \gamma .
-\eeqn
-One can immediately check that $\omega$ carries degree $+1$ as required for the construction of the Weyl factorization algebra.
-Importantly, for each open $U \subset X$ the pairing $\omega$ defines the operator $\triangle$ acting on 
-\beqn
-\Sym \left(\cA_c(U) [n+1] \right)
-\eeqn
-by the following rules:
-\begin{itemize}
-\item If $\Phi \in \Sym^{\leq 1}$ then $\triangle \Phi = 0$.
-\item If $\Phi = \beta \gamma \in \Sym^2$ then define
-\beqn
-\triangle (\beta \gamma) = \omega|_{U} (\beta, \gamma) = \int_U \beta \del \gamma .
-\eeqn
-\item \brian{FINISH}.
-\end{itemize}
-
-\begin{dfn}
-Let $X$ be a complex manifold of dimension $2n+1$.
-The \defterm{free boson factorization algebra} on $X$ is
-\beqn
-\cF \define \left(\Sym \left(\Omega^{\leq n,\bu}_{X,c} [n+1] \right) \; , \; Q + \triangle \right) ,
-\eeqn
-where $\triangle$ is defined as in items (1)-(3) above.
-In the notation of section \ref{ss:weyl}, $\cF = \cW_{\cA,\omega}$.
-\end{dfn}
-
-Finally, we frame this factorization algebra as a quantization of a free BV theory.
-First, let
-\beqn
-\delta_\Delta \in \br\Omega^{2n+1,2n+1}(X \times X)
-\eeqn
-be the $\delta$-distribution along the diagonal $X \hookrightarrow X \times X$.
-This is a distributional form of Hodge type $(2n+1,2n+1)$ on $X \times X$.
-Applying the holomorphic de Rham operator along one of the directions yields a distribution
-\beqn\label{eqn:fullbcov}
-(\del \otimes \id) \delta_{\Delta} \in \br\Omega^{2n+2,2n+1}(X \times X) .
-\eeqn
-This is the full BCOV propagator as introduced in \cite{CLbcov1,CLbcov2}.
-We are only interested in a particular component of this distributional section.
-There is a K\"unneth decomposition
-\beqn
-\br\Omega^{2n+2,2n+1}(X \times X) = \bigoplus_{k=1}^{2n+1} C^k ,
-\eeqn
-where $C^k = \oplus_{q+q'=2n+1} \br \Omega^{k,q}(X) \hotimes \br \Omega^{2n+2-k,q'}(X)$.
-We let
-\beqn\label{eqn:poisson1}
-\pi \in C^{n+1} = \bigoplus_{q+q'=2n+1} \br \Omega^{n+1,q}(X) \hotimes \br \Omega^{n+1,q'}(X) 
-\eeqn
-be the projection of \eqref{eqn:fullbcov} to the component $C^{n+1}$.
-
-\begin{lem}
-This $\pi$ determines a section
-\beqn
-\pi \in \br \fields_X \hotimes \br \fields_X [-1]
-\eeqn
-which satisfies $\d_{\fields} \pi = 0$.
-Thus $\pi$ endows $\fields$ with the structure of a free BV theory of Poisson type.
-\end{lem}
-
+In general, we also have the following relationship to higher form Chern--Simons theory.
+
+\begin{prop}[\cite{GRWcs}]
+Let $X$ be a complex manifold of complex dimension $2n+1$.
+Consider $(2n+1)$-form Chern--Simons theory on the $(4n+3)$-dimensional product manifold with boundary $X \times \R_+$ equipped with the ``chiral'' boundary condition along $X \times \{0\}$ as defined in \cite{GRWcs}.
+The boundary factorization algebra of quantum observables is equivalent to the chiral boson factorization algebra $\cB$ on $X$.
+\end{prop}
+
+\section{Segal--Sugawara construction}
+
+In quantum field theory, it is often natural to study not a single theory but a family of theories over a derived stack $\cX$.
+In the case that the derived stack is $\cX = BG$, with $G$ a group, this amounts to prescribing a $G$-symmetry on the quantum field theory.
+As an example, consider the $\beta-\gamma$ system on a complex manifold $X$ of dimension $n$ as a family over the
+derived stack $\cX = \op{Bun}_{GL(r)}(X)$ of vector bundles on $X$ of rank $r$.
+The fiber over a vector bundle~$Z$ of rank $r$ is the $\beta-\gamma$ system twisted by $Z$, see equation \eqref{eqn:bgZ} for a description of the fields of this theory.
+
+As a more elaborate example, also involving the $\beta-\gamma$ system, we consider $\cX$ to be the derived moduli stack of complex manifolds of dimension $n$.
+Fixing a tensor bundle $\cZ$ (that is, a vector bundle over the universal complex $n$-manifold) we obtain a family over $\cX$ whose fiber over a complex manifold $X$ is the $\beta-\gamma$ system on $X$ twisted by the tensor bundle $\cZ$.
+For example, if $\cZ = \cT$ is the universal tangent bundle, then the theory over $X$ is the $\beta-\gamma$ system on $X$ twisted by $Z = \T_{X}$.
+
+Working with families of theories over \textit{formal} derived stacks, we can be more explicit.
+A symmetry for a formal derived stack described by a dg Lie algebra $\cL$ simply amounts to an infinitesimal $\cL$-symmetry which, in field theory, we assume is prescribed in terms of local currents.
+We recall precise definitions below.
+For a quantum field theory with a $\cL$-symmetry, the work \cite{fact2} formulates a version of Noether's theorem in terms of factorization algebras.
+The result says that for a theory with a $\cL$ action, and factorization algebra of observables $\Obs$, there is a map
+of factorization algebras
+\begin{equation}\label{eqn:noether1}
+C_{\bu}^{\theta}(\cL_{c}) \to \Obs
+\end{equation}
+where, we recall from section \ref{s:enveloping} that $C_{\bu}^{\theta}(\cL_{c})$ is the $\theta$-twisted enveloping factorization algebra of $\cL$.
+The twist~$\theta$ can be understood as the t'Hooft anomaly associated to the symmetry and is explicitly an obstruction to solve the so called (equivariant) master equation in the BV formalism.
+
+Now, let $X$ be a complex manifold.
+The dg Lie algebra $\cL= \cT(X) = \Omega^{0,\bu}(X, \T_{X})$ describes the formal moduli problem of deformations of complex structure.
+In other words, it is the formal neighborhood of $X$ inside of the moduli of all complex manifolds.
+A $\cT$-symmetry amounts to prescribing a holomorphic version of the stress tensor in ordinary quantum field theory.
+In complex dimension one, this is precisely the chiral half of a conformal structure on a theory.
+The anomaly $\theta$ accounts for, at the level of the moduli space, the Beilinson--Schechtman line bundle over the moduli
+space of Riemann surfaces \cite{BS}.
+In this setting, we will find a presentation for this line bundle as a local cocycle for the local Lie algebra $\cT$.
+
+As a conequence of the factorization algebra enhancement of Noether's theorem of \cite{fact2}, we obtain the following linking back to our main definition of a \textit{holomorphic structure}.
 \begin{prop}
-Let $X$ be a complex manifold of dimension $2n+1$.
-The free boson factorization algebra $\cF$ is the BV quantization of the free BV theory of Poisson type whose fields are
-\beqn
-\fields = \Omega^{\geq n+1, \bu}_X [n]
-\eeqn
-and whose $(-1)$-shifted local Poisson structure is $\pi$ as in \eqref{eqn:poisson1}.
-More precisely, there is an equivalence of factorization algebras
-\beqn
-\cF \xto{\simeq} \Obs^q (\fields)|_{\hbar = 1} .
-\eeqn
+  A $\cT_{X}$-symmetry on a theory whose underlying factorization algebra of quantum observables is $\Obs$ defines a holomorphic structure on $\Obs$, see definition \ref{dfn:hol}.
+  The central charge $\bc$ is determined by the obstruction for this $\cT_{X}$ symmetry to solve the equivariant master equation.
 \end{prop}
 
-\begin{prop}[\cite{GRWcs}]
-This free theory of Poisson type is a boundary theory for $(4n+3)$-dimensional abelian $(2n+1)$-form Chern--Simons theory on the product manifold $X \times \R_+$.
-The boundary factorization algebra of quantum observables is equivalent to $\cF$.
+The primary goal of this section is to present examples of holomorphic structures on free theories in various dimensions.
+
+\subsection{Equivariant master equation}
+
+We discuss the precise notion of a family of theories over the formal derived stack $B \cL$, where $\cL$ is a local dg
+Lie algebra---this is, equivalently, the notion of a (local) $\cL$-symmetry.
+
+Let's start with an approach to symmetry in shifted Poisson geometry.
+Suppose that $V$ is a graded vector space and $\eta \in \wedge^2 V^*$.
+Dually, we can think of $\eta$ as a Poisson bivector for the vector space $E = V^*$.
+The bivector $\eta$ induces a Poisson bracket on $\Sym (V) = \cO(E)$.
+A strict Hamiltonian action of a Lie algebra $\lie{g}$ on $E$ is a map of Lie algebras $\mu \colon \lie{g} \to \cO(E)$.
+By Koszul duality between Lie and commutative algebras, see for example \cite{LurieDAGX}, we can view such a linear map $\mu$ as an element of the dg Lie algebra
+$C^\bu(\lie{g}) \otimes \cO(E)$ of cohomological degree one satisfying the Mauer--Cartan equation.
+More generally, $L_\infty$ maps $\lie{g} \rightsquigarrow \cO(E)$ are \textit{defined} to be the Maurer--Cartan elements in
+the dg Lie algebra $C^\bu(\lie{g}) \otimes \cO(E)$.
+
+Now, suppose that $\lie{g}$ is a dg Lie algebra and $(E,Q)$ is a cochain complex equipped with a $Q$-closed bivector
+$\eta \in \wedge^2 E$ of cohomological degree zero.
+The Chevalley--Eilenberg complex $C^\bu(\lie{g})$ is a commutative dg algebra and so the Poisson bracket endows $C^\bu(\lie{g}) \otimes \cO(E)$ with the structure of a dg Lie algebra; the differential is the sum of $\d_{CE}$ and $Q$.
+A (weak) \textit{Hamiltonian action} is, more generally, a Maurer--Cartan element of the dg Lie algebra $C^\bu(\lie{g}) \otimes \cO(E)$.
+That is, an element of degree one
+\begin{equation}
+\mu \in \left[C^\bu(\lie{g}) \otimes \cO(E)\right]^1
+\end{equation}
+such that
+\begin{equation}
+\d_{CE} \mu + Q \mu + \frac12 \{\mu,\mu\} = 0 .
+\end{equation}
+This generalizes the notion of \textit{strict} Hamiltonian action to allow for $L_\infty$ maps $\mu \colon \lie{g}
+\rightsquigarrow \cO(E)$.
+
+Now, we move to our setting where $\eta$ carries cohomological degree $+1$.
+Let $(E,Q)$ and $\lie{g}$ be the same as above. 
+This time, $\eta$ equips $\cO(E)[-1]$ with the
+structure of a dg Lie algebra (notice the shift by one).
+By definition, a $\lie{g}$-symmetry on the $0$-dimensional free quantm field theory defined by $(E,Q,\eta)$ is a
+Maurer--Cartan element in the dg Lie algebra $C^\bu(\lie{g}) \otimes \cO(E)[-1]$.
+Note that the underlying graded Lie algebra underlying this dg Lie algebra is $\cO(\lie{g}[1] \oplus E)$.
+
+The work of \cite{fact2} formulates the general notion of symmetry in perturbative quantum field theory.
+This amounts, in part, to replacing $(E,Q)$ with a complex of vector bundles, whose sections are the space of fields of the theory, and $\lie{g}$ with a local Lie algebra,
+which we denote by $\cL = \Gamma (L)$.
+%Now, we replace $V$ by a complex of vector bundles.
+We will assume for simplicity that $\eta$ is of the form
+\begin{equation}\label{eqn:etaD}
+\eta(\phi) = \frac12 \int \phi D \phi
+\end{equation}
+where $D \colon V \to V^![-1]$ is an elliptic differential operator of cohomological degree $-1$.
+Let $E = V^!$ be the $!$-dual bundle.
+Then, we have seen that the bracket defined using $\eta$ endows the complex of local functionals $\oloc(E)[-1]$ with
+the structure of a dg Lie algebra (after shifting to account for the degree of $\eta$).
+This bracket extends to a bracket on $\oloc(L[1] \oplus E)[-1]$. 
+Combined with the total differential $\d_{CE} + Q$, where $\d_{CE}$ is the Chevalley--Eilenberg differential associated
+to $\cL$, we obtain the structure of a dg Lie algebra that we denote 
+\begin{equation}\label{eq:def}
+    \op{Def}(L,E) \define \big(\oloc(L[1] \oplus E)[-1] , d_{CE} + Q, \{-,-\}_\eta \big)
+\end{equation}
+By definition, a \defterm{local Hamiltonian action} of $\cL$ on the free theory $(E,Q,\eta)$ is a Maurer--Cartan element
+$J \in \op{Def}(L,E)^1$ which is non-constant in the fields (sections of $E$).
+
+\begin{thm}\ref{thm:freenoether}
+Suppose that $(V,Q)$ is an elliptic complex of vector bundles on $M$ and that $\eta \in \oloc(V)$ is a local functional of the form \eqref{eqn:etaD}.
+Suppose that $J^{cl}$ is a local Hamiltonian action of a local Lie algebra $\cL$ on $E = V^!$.
+Then, there is a local cohomology class
+\begin{equation}
+\Theta \in H^1_{loc}(\cL)
+\end{equation}
+together with a map of factorization algebras
+\begin{equation}
+J \colon \mathbf{U}_{\Theta} \cL \to \cW_{V,\eta}
+\end{equation}
+such that $\op{gr} J = J^{cl}$.
+\end{thm}
+
+In the case that $\cL = \cT_X$ is the local Lie algebra of holomorphic vector fields on a complex manifold $X$, then we
+will denote the local current $J$ by the symbol $\sfT$ to emphasize its role as the "holomorphic stress tensor" of the
+theory.
+
+%Suppose that $P$ is a $(-1)$-shifted Poisson dg vector space.
+%Then we have seen that the (BV) bracket endows $\cO(P)[-1]$ with the structure of a dg Lie algebra (generally this is just an $L_\infty$ algebra if the Poisson structure $\pi$ has components of weight $\geq 3$).
+%A strict Hamiltonian action of a dg Lie algebra $\lie{g}$ on $P$ is the data of a map of dg Lie algebra
+%\begin{equation}\label{eqn:moment}
+%T \colon \lie{g} \to \cO(P)[-1]\footnote{Alternatively, this can be thought of as arising from a shifted version of the moment map $P \to \lie{g}^*[-1]$, where the $(-1)$-shifted Poisson structure on $\lie{g}^*[-1]$ is, like the Kostant--Kirillov Poisson structure, determined by the Lie bracket of $\lie{g}$.}.
+%\end{equation}
+%The (BV) bracket is a map of dg Lie algebras $\{-,-\} \colon \cO(P)[-1] \to \op{Vect}(P)$; hence a Hamiltonian action defines, in particular, an infinitesimal $\lie{g}$-action on $P$.
+%
+%Hamiltonian actions of the above type can be classified as follows.
+%Recall that the Chevalley--Eilenberg cochain complex $C^\bu(\lie{g})$ is a commutative dg algebra whose cohomology is the Lie algebra cohomology of $\lie{g}$ (with trivial coefficients).
+%Consider the dg Lie algebra
+%\begin{equation}\label{eqn:babycme}
+%C^\bu(\lie{g}) \otimes \cO(P)[-1] 
+%\end{equation}
+%where the bracket uses the product on the Chevalley--Eilenberg complex and the bracket on $\cO(P)$.
+%Hamiltonian actions \eqref{eqn:moment} define Maurer--Cartan elements in this dg Lie algebra.
+%More generally, we define a \defterm{Hamiltonian action} of $\lie{g}$ on the $(-1)$-shifted Poisson space $P$ to be a Maurer--Cartan element in this dg Lie algebra.
+%Directly in terms of the Lie algebra $\lie{g}$ these correspond to $L_\infty$ morphisms from $\lie{g}$ to $\cO(P)[-1]$.
+%Strict Hamiltonian actions are those which are linear in $\lie{g}$.
+%The Maurer--Cartan element equation for \eqref{eqn:babycme} is
+%\begin{equation}
+%\d_{CE} J + \d_{P} J + \frac12 \{J,J\}  = 0
+%\end{equation}
+%where $\d_{CE}$ is the Chevalley--Eilenberg differential for $\lie{g}$, $\d_P$ is the internal differential to $P$, and $\{-,-\}$ is the $(-1)$-shifted Poisson bracket on $\cO(P)$.\footnote{If $\pi$ has components of higher weight then \eqref{eqn:babycme} is only an $L_\infty$ algebra and the MC equation will also involve the higher brackets.}
+
+\subsection{The $\beta-\gamma$ system}
+
+Fix a complex dimension $n$ and suppose that $W$ is a natural holomorphic vector bundle functor on complex
+$n$-manifolds \cite{MK}.
+This is a functor from the category of all $n$-dimensional complex manifolds with morphisms given by local holomorphic
+diffeomorphisms to the category of vector bundles.
+Examples include the trivial bundle, the (co)tangent bundle, tensor bundles, and quotients of such.
+
+Fix a complex manifold $X$ and let $W_X$ denote the corresponding holomorphic vector bundle on $X$.
+The naturality assumption implies that the space of sections $\Gamma(W)$ is a module for the Lie algebra of holomorphic vector
+fields; the action is by Lie derivative.
+This furthermore extends to an action of the dg Lie algebra $\Omega^{0,\bu}(X,\T_X)$ on the cochain complex
+$\Omega^{0,\bu}(X,W_X)$ which we denote 
+\begin{equation}\label{}
+  (\mu, \gamma) \mapsto L_\mu \gamma 
+\end{equation}
+where $\mu \in \Omega^{0,\bu}(X,\T_X)$ and $\gamma \in \Omega^{0,\bu}(X,W_X)$.
+
+The free theory we consider is the $\beta-\gamma$ system on $X$ with values in the natural bundle $W_X$.
+This means that $\gamma \in \Omega^{0,\bu}(X,W_X)$ and $\beta \in \Omega^{0,\bu}(X,W_X^!)[n-1]$.
+Notice that the (free) classical action $\int_X \beta \dbar \gamma$ is manifestly invariant under the action of
+holomorphic vector fields.
+
+There is a local Hamiltonian which encodes this symmetry.
+For $\mu \in \cT_X$ define the local functional 
+\begin{equation}\label{}
+  \sfT(\mu) = \int_X \beta L_X \gamma .
+\end{equation}
+
+\begin{prop}
+  The local functional $\sfT \in \oloc(\cT[1] \oplus E)$ satisfies the Maurer--Cartan equation and hence defines a
+  local Hamiltonian symmetry of holomorphic vector fields on the $\beta-\gamma$ system on $X$ with values in the
+  natural bundle $W_X$.
 \end{prop}
 
-\section{Segal--Sugawara construction}
+\begin{proof}
+We need to check the equation
+\begin{equation}\label{eqn:mcbg}
+  \d_{CE} \sfT + \dbar \sfT + \frac12 \{\sfT, \sfT\} = 0 .
+\end{equation}
+It is clear that $\dbar \sfT = 0$.
+The Chevalley--Eilenberg differential applied to $\sfT$ gives the local functional, which is quadratic in vector fields: 
+\begin{equation}\label{}
+  (\d_{CE} \sT)(\mu,\mu') = -\sfT([\mu,\mu'])= - \int_X \beta L_{[\mu,\mu']} \gamma . 
+\end{equation}
+On the other hand, we have 
+\begin{equation}\label{}
+  \frac12 \{\sfT,\sfT\} (\mu,\mu') = \{\sfT(\mu),\sfT(\mu')\} = \int \beta (L_\mu L_{\mu'} - (-1)^{|\mu'|} L_{\mu'} L_\mu)
+\gamma = \sfT([\mu,\mu']).
+\end{equation}
+\end{proof}
+
+We now turn to quantization.
+By \ref{thm:freenoether}, we know that there exists a higher central charge $\bc \in H^{2n+2}(BU(n))$ for $\cT$ together with a homomorphism of
+factorization algebras 
+\begin{equation}\label{}
+  \cV\op{ir}_{\bc} \to \beta\gamma(W)   
+\end{equation}
+
+\subsection{The chiral boson}
 
 \begin{thm}
-Let $X$ be a complex manifold of dimension $2n+1$ and let
-\beqn
+Let $X$ be a complex manifold of dimension $2n+1$ and consider the higher dimensional chiral boson factorization algebra $\cB$ on $X$.
+The current $\frac12 \int \alpha \iota_X \alpha$ extends to a map of factorization algebras
+\begin{equation}
+\cV\op{ir}_{\mathbf{c}} \to \cB 
+\end{equation}
+where
+\begin{equation}
 \mathbf{c} \define \sum^{n}_{k = 0} (-1)^k \op{Td} \cdot \op{ch}(\wedge^k T)|_{4n+4} \in H^{4n+4}(BU(2n+1)) .
-\eeqn
-Then the current $\int \alpha \iota_X \alpha$ extends to a map of factorization algebras on $X$:
-\beqn
-\cV\op{ir}_{\mathbf{c}} \to \cB .
-\eeqn
+\end{equation}
 \end{thm}
-
-\subsection{Equivariant master equations}
-
-Suppose that $P$ is a $(-1)$-shifted Poisson dg vector space.
-Then we have seen that the (BV) bracket endows $\cO(P)[-1]$ with the structure of a dg Lie algebra (generally this is just an $L_\infty$ algebra if the Poisson structure $\pi$ has components of weight $\geq 3$).
-A strict Hamiltonian action of a dg Lie algebra $\lie{g}$ on $P$ is the data of a map of dg Lie algebra
-\beqn\label{eqn:moment}
-T \colon \lie{g} \to \cO(P)[-1]\footnote{Alternatively, this can be thought of as arising from a shifted version of the moment map $P \to \lie{g}^*[-1]$, where the $(-1)$-shifted Poisson structure on $\lie{g}^*[-1]$ is, like the Kostant--Kirillov Poisson structure, determined by the Lie bracket of $\lie{g}$.}.
-\eeqn
-The (BV) bracket is a map of dg Lie algebras $\{-,-\} \colon \cO(P)[-1] \to \op{Vect}(P)$; hence a Hamiltonian action defines, in particular, an infinitesimal $\lie{g}$-action on $P$.
-
-Hamiltonian actions of the above type can be classified as follows.
-Recall that the Chevalley--Eilenberg cochain complex $C^\bu(\lie{g})$ is a commutative dg algebra whose cohomology is the Lie algebra cohomology of $\lie{g}$ (with trivial coefficients).
-Consider the dg Lie algebra
-\beqn\label{eqn:babycme}
-C^\bu(\lie{g}) \otimes \cO(P)[-1] 
-\eeqn
-where the bracket uses the product on the Chevalley--Eilenberg complex and the bracket on $\cO(P)$.
-Hamiltonian actions \eqref{eqn:moment} define Maurer--Cartan elements in this dg Lie algebra.
-More generally, we define a \defterm{Hamiltonian action} of $\lie{g}$ on the $(-1)$-shifted Poisson space $P$ to be a Maurer--Cartan element in this dg Lie algebra.
-Directly in terms of the Lie algebra $\lie{g}$ these correspond to $L_\infty$ morphisms from $\lie{g}$ to $\cO(P)[-1]$.
-Strict Hamiltonian actions are those which are linear in $\lie{g}$.
-The Maurer--Cartan element equation for \eqref{eqn:babycme} is
-\beqn
-\d_{CE} J + \d_{P} J + \frac12 \{J,J\}  = 0
-\eeqn
-where $\d_{CE}$ is the Chevalley--Eilenberg differential for $\lie{g}$, $\d_P$ is the internal differential to $P$, and $\{-,-\}$ is the $(-1)$-shifted Poisson bracket on $\cO(P)$.\footnote{If $\pi$ has components of higher weight then \eqref{eqn:babycme} is only an $L_\infty$ algebra and the MC equation will also involve the higher brackets.}
-
-\subsection{Stress tensor}
 In this section, we fix a complex manifold $X$ of dimension $2n+1$ on which all objects are defined.
 For $\mu \in \cT$ define the local functional
-\beqn
+\begin{equation}
 T(\mu) \in \oloc(\fields)
-\eeqn
+\end{equation}
 by the formula
-\beqn
+\begin{equation}
 T(\mu) = \sum_{k \geq 1} f(k) \int \alpha \iota_\mu^k \alpha .
-\eeqn
+\end{equation}
 
@@
 The functional
-\beqn
+\begin{equation}
 T \in \op{Act}(\cT,\fields)^1 
-\eeqn
+\end{equation}
 satisfies the classical master equation
-\beqn
+\begin{equation}
 \d_{\cT} T + \del T + \frac12 \{T,T\} = 0 .
-\eeqn
+\end{equation}
 \end{lem}
@@
 First we compute
-\beqn
+\begin{equation}
 \d_{\cT} T = - \sum_{k \geq 1} k f(k) \int \alpha \iota_{[\mu,\mu]} \iota^{k-1}_\mu \alpha 
-\eeqn
+\end{equation}
 and
-\beqn
+\begin{equation}
 \del T = \sum_{k \geq 1} \int \alpha \iota_\mu^k \del \alpha .
-\eeqn
+\end{equation}
 
 Next, we compute
-\beqn
+\begin{equation}
 \{\int \alpha \iota_{\mu} \alpha, \int \alpha \iota_{\mu'} \alpha\} = \int \del 
-\eeqn
+\end{equation}
 \end{proof}
@@
 The most general stress tensor is
-\beqn
+\begin{equation}
 T_a(X) = \int \alpha \iota_X \alpha + \hbar a \int \alpha (J X)  
-\eeqn
+\end{equation}
 
@@
 The most general stress tensor is
-\beqn
-T_{\bfa} (X) = \int \alpha \iota_X \alpha + a_1 \int \alpha \op{Tr}(J X \del J X) + a_2 \int \alpha \op{Tr}(J X) \op{Tr}(\del J X) .
-\eeqn
+\begin{equation}
+T_{\ba} (X) = \int \alpha \iota_X \alpha + a_1 \int \alpha \op{Tr}(J X \del J X) + a_2 \int \alpha \op{Tr}(J X) \op{Tr}(\del J X) .
+\end{equation}
 
 \subsection{Coupling in type IIB string theory}
+
+\section{Higher vertex algebras}
+
+\subsection{The higher Heisenberg algebra}
+
+We will use the explicit commutative dg algebra model $\sfA$ for $\R \Gamma(\mathring{D}^{2n+1}, \cO)$ where $\mathring{D}^{2n+1}$ is the punctured formal $(2n+1)$-disk which was introduces in \cite{FHK} and recalled in appendix \ref{appx:model}.
+Denote the differential on this dg model by $\dbar$.
+In appendix \ref{appx:model} we have also introduced dg $\sfA$-modules $\sfA^{(p)}$ for $\R \Gamma(\mathring{D}^{2n+1}, \Omega^{p})$ where $\Omega^{p}$ is the sheaf of $p$-forms on the formal disk.
+We set $\sfA = \sfA^{(0)}$.
+Let $\del \colon \sfA^{(p)} \to \sfA^{(p+1)}$ be the formal holomorphic de Rham operator.
+
+The formal $S^{4n+1}$-residue is a cochain map
+\begin{equation}\label{eqn:residue}
+  \oint \colon \sfA^{(2n+1)} \to \C[-2n+2] .
+\end{equation}
+
+Consider the following abelian dg Lie algebra
+\begin{equation}\label{eqn:f}
+\mathsf{f} \define \sfA[2n] \xto{\del} \sfA^{(1)} [2n-1] \to \cdots \to \sfA^{(n)}[n]
+\end{equation}
+concentrated in degrees $-2n$ up to $1$.
+Notice that this is the totalization of a double complex; we have left the $\dbar$-degree and operator intrinsic to this expression.
+
+The higher Heisenberg dg Lie algebra $\mathsf{h}$ is the dg Lie algebra central extension
+\begin{equation}\label{eqn:higherheis}
+0 \to \C \to \mathsf{h} \to \mathsf{f} \to 0
+\end{equation}
+determined by the degree two cocycle
+\begin{equation}\label{eqn:cocycleheis}
+\oint \alpha \del \beta
+\end{equation}
+where $\alpha, \beta \in \mathsf{f}$.
+Notice that this expression is only nonzero on the holomorphic $n$-form components of $\alpha$ and $\beta$.
+
+We focus on the case $n=3$ from now on in this section.
+
+Note that in this case, $\mathsf{h}$ is concetrated in degrees $-2$ up to $1$.
+In fact, since $\mathsf{h}$ is formal, we might as well replace it with its cohomology $\lie{h}' \define H^{\bu}(\mathsf{h})$.
+This cohomology is concentrated in degrees $-2,-1,0,1$.
+In degree $-2$ the cohomology is one-dimensional given by the constant functions on the formal disk and this summand appears trivially in all Lie brackets.
+We will mostly consider the graded Lie subalgebra $\lie{h} \subset \lie{h}'$ which agrees with $\lie{h}'$ in degrees $-1,0,1$.
+In degree $-1$ we have
+\begin{equation}\label{eqn:deg-1}
+\lie{h}^{-1} = \Omega^{1} (D^{3}) \slash \del \cO(D^{3})
+\end{equation}
+The degree zero part of $\lie{h}$ is one-dimensional $\lie{h}^{0} = \C K$, spanned by the central element $K$.
+The degree one part is, by formal Serre duality, given by
+\begin{equation}\label{eqn:formalserre}
+  \lie{h}^{1} = H^{2}(\mathring{D}^{3}, \Omega^{1} \slash \del \cO) \simeq \left(\Omega^{2,cl}(D^{3})\right)^{\vee}
+\end{equation}
+where $\Omega^{2,cl}(D^{3})$ is the space of closed two-forms on the formal three-disk.
+
+%In fact, we can simplify this model slightly.
+%Let $\Omega^{1} \slash \d \cO$ denote the sheaf of one-forms modulo the sheaf of exact one-forms.
+%We can then consider the Joaunalou model $\sfA^{(0 \to 1)}$ for $\R \Gamma (\mathring{D}^{3}, \Omega^{1} \slash \d \cO)$.
+%It has the following explicit form.
+%
+%Recall that in degree zero $\sfA^{0} = \sfA^{(0),0}$ is the localized algebra $\C[[z]][z^{*}][(z z^{*})^{-1}]$.
+%Similarly, from the $\cO = \C[[z]]$-module $\Omega^{1} \slash \d \cO$ we can localize to get the $\sfA^{0}$-module $\Omega^{1} \slash \d \cO [z^{*}][(z z^{*})^{-1}]$ which we denote by $\sfA^{(0 \to 1),0}$.
+%
+%For $0 \leq m \leq 2$ we identify $\sfA^{(0 \to 1),m}$ with the vector space formed by expressions
+%\begin{equation}\label{eqn:forms}
+%\alpha = \sum_{1 \leq i_{1} \leq \cdots \leq i_{m} \leq 3} \alpha_{i_{1}\cdots i_{m}}(z, z^{*}) \d z_{i_{1}}^{*} \cdots \d z_{i_{m}}^{*}
+%\end{equation}
+%where $\alpha_{i_{1}\cdots i_{m}} \in \sfA^{(0 \to 1),0}$ and
+%\begin{itemize}
+  %\item[(i)] $\alpha$ is homogenous in the starred variables $z_{i}^{*}, \d z_{i}^{*}$ of total degree zero.
+  %\item[(ii)] The contraction of $\alpha$ with the Euler vector field $Eu^{*} = \sum_{i} z_{i}^{*} \frac{\del}{\del z_{i}^{*}}$ vanishes, $i_{Eu^{*}} \alpha = 0$.
+%\end{itemize}
+%The differential on $\sfA_{m}$ is simply the $\dbar$ operator $\dbar = \sum_{i} \d z_{i}^{*} \frac{\del}{\del z_{i}^{*}}$.
+%
+%This dg $\sfA$-module $\sfA^{(0 \to 1)}$ is concentrated in degrees $0,1,2$ (just like $\sfA$).
+%In particular, $\lie{f} = \sfA^{(0\to 1)}[1]$ can be considered as an abelian dg Lie algebra concentrated in degrees $-1,0,1$.
+%The same formula as above defines the one-dimensional central extension $\lie{h}$ of $\lie{f}$.
+%
+%Let $\lie{h}_{-} = H^{1}(\lie{f}_{-}^{1}) [-1] = H^{2}(\sfA^{(0 \to 1)})[-1]$ which is a vector space concentrated in degree $+1$.
+%
+%\begin{lem}
+  %There is an isomorphism $\lie{h}_{-} \simeq \left(\Omega^{2,cl}(D^{3})\right)^{\vee}[-1]$.
+%\end{lem}
+%
+%Let $\lie{h}_{+} = \ker (\lie{h} \to \lie{h}_{-})$ where the map is simply the identity in degree $+1$.
+%Note that $\lie{h}_{+}$ is concentrated in degrees $-1$ and $0$.
+%There is, of course, a splitting of cochain complexes $\lie{h}= \lie{h}_{-} \oplus \lie{h}_{+}$, but this splitting does not respect the Lie bracket.
+%In fact, $\lie{h}_{+}$ is a sub dg Lie algebra.
+%
+%\brian{below is the version where I take cohomology}
+
+Define the abelian subalgebras $\lie{h}_{+} = \lie{h}^{-1} \oplus \C K$ and $\lie{h}_{-} = \lie{h}^{1}$ so that
+\begin{equation}\label{}
+  \lie{h} = \lie{h}_{+} \oplus \lie{h}_{-} \simeq \left(\frac{\Omega^{1}(D^{3})}{\del \cO(D^{3})} [1] \oplus \C K\right) \oplus \left(\Omega^{2,cl}(D^{3})\right)^{\vee} [-1] .
+\end{equation}
+
+\subsection{The vacuum module}
+
+Let $\C_{K=1}$ denote the one-dimensional $\lie{h}_{+}$-module (concentrated in degree zero) defined by the rules:
+\begin{itemize}
+  \item $K \in \lie{h}_{+}^{0}$ acts by the identity.
+  \item By degree reasons, $\lie{h}_{+}^{-1} = \Omega^{1} \slash \del \cO$ necessarily acts trivially on $\C_{K = 1}$.
+\end{itemize}
+
+Define the dg $\lie{h}$-module
+\begin{equation}\label{eqn:module}
+  \pi \define U(\lie{h}) \otimes_{U(\lie{h}_{+})} \C_{K=1}
+\end{equation}
+
+By construction, we see that there is an isomorphism of graded vector spaces
+\begin{equation}\label{eqn:isomorphism?}
+\pi \simeq \C[\lie{h}_{-}] \simeq \op{Sym} \left( \Omega^{2,cl}(D^{3})^{\vee}[-1] \right) .
+\end{equation}
+In other words, as a vector space $\pi$ is the free graded commutative algebra on the vector space $H^{2}\sfA^{(0 \to 1),2}[-1] \simeq (\Omega^{2,cl}(D))^{\vee}[-1]$ (concentrated in degree one).
+
+We can describe the $\lie{h}$-module structure explicitly.
+In degree $-1$ we have $\lie{h}^{-1} = \Omega^{1}(D)\slash \del \cO(D^{3})$.
+Recall that we have used the canonical isomorphism
+\begin{equation}\label{eqn:serre}
+\Omega^{2,cl}(D^{3})^{\vee} \simeq H^{2}(\mathring{D}^{3}, \Omega^{1} \slash \del \cO) .
+\end{equation}
+granted by the higher residue pairing.
+Given a class $[\alpha] \in \Omega^{1}(D)\slash \del \cO$, and a linear generator $\beta \in \Omega^{2,cl}(D^{3})^{\vee} \simeq H^{2}(D, \Omega^{1} \slash \del \cO)$ we define
+\begin{equation}\label{eqn:alphaaction}
+\alpha \cdot \beta = \oint \alpha \del \beta \in \C .
+\end{equation}
+We then extend this, as a graded derivation on $\pi$ of cohomological degree $-1$, to a linear map that we denote
+\begin{equation}\label{eqn:derivation}
+  \frac{\del}{\del \alpha} \colon \pi \to \pi [-1], \quad \alpha \in \lie{h}^{-1} = \frac{\Omega^{1}(D^{3})}{\del \cO(D^{3})} .
+\end{equation}
+
+In degree zero, the central element $K \in \lie{h}_{+}$ acts on $\pi$ by the identity.
+
+Finally, in degree $-1$ we have $\lie{h}^{1}= \lie{h}_{-} = \left(\Omega^{2,cl}(D^{3})\right)^{\vee}$.
+Such elements act simply by multiplication (this is sensible since $\lie{h}_{-}$ is concentrated in degree $+1$ just like the generators of $\pi$).
+Thus, we obtain linear maps
+\begin{equation}\label{eqn:created}
+  \alpha \cdot \colon \pi \to \pi [1] , \quad \alpha \in \lie{h}^{1} = \left(\Omega^{2,cl}(D^{3})\right)^{\vee} .
+\end{equation}
+
+\subsection{Explicit generators}
+
+We provide explicit generators and relations for the algebras and modules of the previous section.
+
+For $k_{1},k_{2},k_{3} \geq 0$, and $i=1,2,3$, let
+\begin{equation}\label{eqn:positive}
+  b_{i}[\bm] = b_{i}[m_{1},m_{2},m_{3}] \in \lie{h}_{+} = \Omega^{1}(D^{3})/ \del \cO(D^{3})
+\end{equation}
+be the equivalence class of the one-form $z_{1}^{m_{1}} z_{2}^{m_{2}}z_{3}^{m_{3}} \d z_{i}$ on the formal disk.
+By definition, $b_{i}[\bm]$ is of cohomological degree $-1$.
+Similarly, let
+\begin{equation}\label{eqn:negative}
+  b_{i}[-\bm-1] = b_{i}[-m_{1}-1,-m_{2}-1,-m_{3}-1] \in \lie{h}_{-} = \Omega^{2,cl}(D^{3})^{\vee}
+\end{equation}
+be the element linearly dual to the closed two-form $\del(z_{1}^{m_{1}} z_{2}^{m_{2}}z_{3}^{m_{3}} \d z_{i})$ on the formal disk.
+The elements $b_{i}[-\bm-1]$ are of cohomological degree $+1$.
+Thus, $\{b_{i}[\bm], K\}$ where $i=1,2,3$ and $\bm \geq 0$ (in the sense that $m_{j} \geq 0$ for $j=1,2,3$).
+
+The Lie bracket for $\lie{h}$, in terms of this basis, is
+\begin{align*}
+  \left[b_{i}[\bm], b_{j}[-\bn-1]\right] & = \sum_{k=1}^{3} \eps_{ijk} n_{k} \delta_{\bm+e_{k}, \bn} K \\
+  \left[b_{i}[\bm], b_{j}[\bn]\right] & = 0 \\
+  \left[b_{i}[-\bm-1], b_{j}[-\bn-1]\right] & = 0 .
+\end{align*}
+In this expression, $e_{j}$ stands for the length three multi-index with $1$ in entry $j$ and $0$'s elsewhere and $\delta_{\bk, \bl} = \delta_{k_{1},l_{1}}\delta_{k_{2},l_{2}} \delta_{k_{3},l_{3}}$.
+
+As a vector space, the module $\pi$ is the graded polynomial algebra on the cohomological degree one generators $b_{i}[-\bm-1]$ for $i=1,2,3$ and $\bm \geq 0$.
+For example, in cohomological degree zero $\pi^{0} = \C$, spanned by the unit.
+In degree one, we have $\pi^{1}=\lie{h}_{-}$ spanned by $\{b_{i}[-\bm-1]\}$.
+In degree two, $\pi^{2}$ is spanned by antisymmetric expressions of the form
+\begin{equation}\label{eqn:deg2}
+b_{i}[-\bm-1,\bn-1] b_{j}[-\br-1,\bs-1]
+\end{equation}
+subject to the relations
+\begin{equation}\label{}
+b_{i}[-\bm-1,\bn-1] b_{j}[-\br-1,\bs-1] = b_{j}[-\br-1,\bs-1] b_{i}[-\bm-1,\bn-1]  .
+\end{equation}
+
+The $\lie{h}$-module structure on $\pi$ is as follows.
+For $\bn \geq 0$ the elements $b_{j}[-\bn-1]$ act on $\pi$ by left multiplication.
+These are the ``creation'' operators.
+The element $K$ acts by the identity.
+For $\bn > 0$ (meaning $n_{j} \geq 0$ and $n_{1}+n_{2}+n_{3} > 0$) the elements $b_{j}[\bn]$ acts by the derivation\begin{equation}\label{eqn:derivationexplicit}
+  \frac{\del}{\del b_{j}[-\bn]}.
+\end{equation}
+These are the ``annihilation'' operators.
+Finally, $b_{j}[0,0,0]$ acts by zero for $j=1,2,3$.
+
+%In conformal triweight $(0,0,0)$ we have just the unit $1 \in \C$.
+%In conformal triweight $e_{j}$ we have $b_{j}[-1,-1,-1]$, $j=1,2,3$.
+%In conformal triweight
+
+\subsection{Segal-Sugwara, locally}
+
+Consider the following vectors
+\begin{equation}\label{}
+\omega_{i} = \sum_{j<k} \eps_{ijk} b_{j}[-1] b_{k}[-1] , \quad i=1,2,3
+\end{equation}
+where $b_{j}[-1] = b_{j}[-1,-1,-1]$.
+
+\subsection{Higher vertex algebra structure}
 
@@
 Let $\sfA_{[n]}^\bu$ be the commutative graded algebra generated over the localized ring
-\beqn
+\begin{equation}
 \C[z_i,z_i^*] [(z z^*)^{-1}]
-\eeqn
+\end{equation}
 by degree one generators $\d z_i^*$, $i=1,\ldots,n$ subject to the conditions
@@
 In degree zero the cohomology is simply globally defined algebraic functions on punctured affine space, which by Hartog's theorem is
-\beqn
+\begin{equation}
 H^0(\sfA_{[n]}) = \C[z_1,\ldots,z_n] .
-\eeqn
+\end{equation}
 Next, define
-\beqn
+\begin{equation}
 \omega_{BM} = \# \sum_{i=1}^n (-1)^{i+1} \frac{z_i^* \d z_1^* \cdots \Hat{\d z_i^*} \cdots \d z_n^* }{(z z^*)^n}
-\eeqn
+\end{equation}
 be the Bochner--Martenilli kernel.
@@
 Then a presentation for the degree $(n-1)$ cohomology is 
-\beqn
+\begin{equation}
 H^{n-1}(\sfA_{[n]}) \cong \C[\del_{z_1},\ldots,\del_{z_n}] \omega_{BM} .
-\eeqn
+\end{equation}
 
 In the main text, we find it convenient to introduce the notation
-\beqn
+\begin{equation}
 \lambda_i \define \frac{\zbar_i}{(zz^*)} .
-\eeqn
+\end{equation}
 When $n=1$ this is simpy $\lambda = \frac{1}{z}$.
@@
 There is an embedding of commutative dg algebras \cite{FHK}:
-\beqn
+\begin{equation}
 j \colon \sfA \hookrightarrow \Omega^{0,\bu}(\C^n - \{0\})
-\eeqn
+\end{equation}
 which sends $z_i \mapsto z_i$, $z_i^* \mapsto \zbar_i$, $\d z^*_i \mapsto \d \zbar_i$, which clearly interchanges the algebraic $\dbar$-operator with the usual one.
@@
 Let 
-\beqn
+\begin{equation}
 \op{Res} \left(- \d^n z\right) \colon \sfA \to \C[-n+1]
-\eeqn
+\end{equation}
 be defined by the projection onto the component of $\omega_{BM} \in \sfA_{[n]}$, which is of degree $n-1$.
 As observed in \cite{FHK}, one has compatibility with usual integration over any $(2n-1)$-sphere centered at the origin as
-\beqn
+\begin{equation}
 \Res_z(\alpha \d^n z) = \oint_{S^{2n-1}} j(\alpha) d^n z ,
-\eeqn
+\end{equation}
 for $\alpha \in \sfA_{[n]}$.
@@
 Let $\sfA'$ be the graded polynomial algebra
-\beqn
+\begin{equation}
 \C[z_i, \lambda_j, \mu_k]
-\eeqn
+\end{equation}
 where $i,j,k=1,2,3$ and the cohomological degrees of the generators are:
-\beqn
+\begin{equation}
 \op{deg}(z_i) = \op{deg}(\lambda_j) = 0, \quad \op{deg}(\mu_i) = 1 .
-\eeqn
+\end{equation}
 Define the degree $2$ element
-\beqn
+\begin{equation}
 \omega \define \sum_{ijk} \eps_{ijk} z_i \mu_j \mu_k = z_1 \mu_2 \mu_3 - z_2 \mu_1 \mu_3 + z_3 \mu_1 \mu_2 .
-\eeqn
+\end{equation}
 Define the differential $\d$ on $\sfA'$ on generators as follows
@@
 %In the graded algebra $\sfA$ one has the relations $\mu_1 \mu_2 \mu_3 = 0$ and 
-%\beqn
+%\begin{equation}
 %\sum_{ijk} \eps_{ijk} \mu_i \mu_j z_k = \omega .
-%\eeqn
+%\end{equation}
 %\end{lem}
@@
 %Similarly, using (3) we have 
-%\beqn
+%\begin{equation}
 %\sum_{ijk} \mu_i \mu_j z_k = \sum_k \lambda_k z_k \omega = \omega .
-%\eeqn
+%\end{equation}
 %\end{proof}
@@
 %Indeed from the above lemma we see
-%\beqn
+%\begin{equation}
 %\omega^2 = \left(\sum_{ijk} \eps_{ijk} \mu_i \mu_j z_k \right)^2 = 0
-%\eeqn
+%\end{equation}
 %and
-%\beqn
+%\begin{equation}
 %\mu_i \omega = 0.
-%\eeqn
+%\end{equation}
 
@@
 Algebraic sections of the tangent bundle $\T_{\A^n - \{0\}}$ is a sheaf of Lie algebras on punctured affine space and its derived global sections 
-\beqn
+\begin{equation}
 \R \Gamma(\A^n - \{0\}, \T_{\A^n-\{0\}})
-\eeqn
+\end{equation}
 therefore carry the structure of a Lie algebra, up to homotopy.
@@
 In particular
-\beqn
+\begin{equation}
 \R \Gamma(\A^n - \{0\}, \T_{\A^n-\{0\}}) \simeq \R \Gamma(\A^n - \{0\}, \cO_{\A^n - \{0\}}) \otimes \C^n
-\eeqn
+\end{equation}
 where $\C^n$ is spanned by the vector fields $\frac{\del}{\del z_i}$, $i=1,\ldots,n$.
@@
 The $n$-\defterm{dimensional Witt algebra} $\lie{witt}(n)$ is the dg Lie algebra whose underlying cochain complex is
-\beqn
+\begin{equation}
 \lie{witt}(n) = \sfA_{[n]} \otimes \C^n = \sfA_{[n]} \otimes \C \left\{\frac{\del}{\del z_i}\right\}_{i=1}^n
-\eeqn
+\end{equation}
 and whose Lie bracket is
@@
 Let $\alpha \in \Omega^{1,\bu}(\C)$ be a spin $1$ field and consider the non-local action
-\beqn
+\begin{equation}
 \int_\C \alpha \dbar \del^{-1} \alpha .
-\eeqn
+\end{equation}
 
@@
 Let $\psi^\pm(z)$ be the fields of the free fermion system with OPE
-\beqn
+\begin{equation}
 \psi^+(z) \psi^-(w) \simeq \frac{1}{z-w} .
-\eeqn
+\end{equation}
 These fields generate a simple vertex algebra that we denote by $F$.
@@
 There is a family of stress tensors
-\beqn
+\begin{equation}
 T^\lambda (z) = (1-\lambda) \colon \del \psi^+(z) \psi^- (z) \colon  + \lambda \colon \del \psi^- (z)\psi^+(z) \colon ,
-\eeqn
+\end{equation}
 which have central charge
-\beqn
+\begin{equation}
 c_\lambda = - 2 (6 \lambda^2 - 6 \lambda + 1) .
-\eeqn
+\end{equation}
 
@@
 Define the field
-\beqn
+\begin{equation}
 \alpha(z) \define \colon \psi^+(z) \psi^-(z) \colon 
-\eeqn
+\end{equation}
 This is a free boson field of level $1$ and $\psi^\pm(z)$ has charge $\pm 1$ with respect to $\alpha(z)$.
 This endows $F$ with the structure of a representation for the Heisenberg, or oscillator, algebra
-\beqn
+\begin{equation}
 0 \to \C K \to \Hat{\lie{s}} \to \C((t)) \to 0
-\eeqn
+\end{equation}
 where $\alpha_j = t^j$ and the commutation relations are $[\alpha_i, \alpha_j] = i \delta_{i,-j}$.
 Moreover, the stress tensor can be written in terms of this field as
-\beqn
+\begin{equation}
 T_\lambda(z) = \frac12 \colon \alpha(z)^2 \colon + \left(\frac12 - \lambda\right) \del \alpha (z) .
-\eeqn
+\end{equation}
 
@@
 For $m > 0$ define the state
-\beqn
+\begin{equation}
 |m\> \define \psi^+_{(-m)} \cdots \psi_{(-2)}^+ \psi_{(-1)}^+ |0\> 
-\eeqn 
+\end{equation}
 and for $m < 0$ define the state
-\beqn
+\begin{equation}
 |m\> \define \psi^-_{(m)} \cdots \psi_{(-2)}^- \psi_{(-1)}^- |0\>  .
-\eeqn 
+\end{equation}
 Then $|m\> \in F^{(m)}$.
@@
 The weight $\mu$ Verma module is
-\beqn
+\begin{equation}
 \til V (\vec{\mu}) = U(\Hat{\lie{h}}) \otimes_{U(\lie{h}[[t]] \oplus \C K)} \C_{\mu, 1}
-\eeqn
+\end{equation}
 where $\C_{\vec{\mu},1}$ is the one-dimensional module where $t^0$ acts by the vector $\vec{\mu}$ and $K$ acts by $1$.
 As a vector space
-\beqn
+\begin{equation}
 \til V (\vec{\mu}) \simeq S \left(\lie{h}^{<0}\right)
-\eeqn
+\end{equation}
 where $\lie{h}^{<0} = \oplus_{j < 0} \lie{h} \otimes t^j$.
@@
 Let 
-\beqn
+\begin{equation}
 V_Q \define S \otimes \C[Q] .
-\eeqn
+\end{equation}
 
@@
 We consider the local Lie algebra
-\beqn
+\begin{equation}
 \Omega^\bu(S) \hotimes \Omega^{0,\bu}(\Sigma, \T_{\Sigma}) 
-\eeqn
+\end{equation}
 controlling deformations of the THF.
@@
 where the classical action is 
-\beqn
+\begin{equation}
 \int_{S \times \Sigma} \sfb (\d + \dbar) \sfc + \frac12 \int_{S \times \Sigma} \sfb [\sfc,\sfc] .
-\eeqn
+\end{equation}
 The central charge should introduce a coupling like
-\beqn
+\begin{equation}
 \int_{S \times \C} J \sfc \del J \sfc .
-\eeqn
+\end{equation}
 
@@
 The complex of local operators is equivalent to
-\beqn
+\begin{equation}
 C^\bu(\lie{vect}(1) \oplus F_{-2}[-1]) \simeq C^\bu(\lie{vect}(1) ; S^\bu \left(F^\vee_{-2}\right))
-\eeqn
+\end{equation}
 where $F_{-2} = \Gamma(D, K^{\otimes 2})$.
@@
 Since $\sfb$ is spin $2$ the cohomology of this is the same as the cohomology of just the $\sfc$'s:
-\beqn
+\begin{equation}
 H^\bu(\lie{vect}(1)) = \C \oplus \C[-3] .
-\eeqn
+\end{equation}
 This is hopeful, it's the same as the cohomology of local operators in Chern--Simons theory for $\lie{sl}(2)$.
@@
 Consider compactification of the free tensor multiplet along
-\beqn
+\begin{equation}
 C \times (\C^2 - \{0\})
-\eeqn 
+\end{equation}
 where $C$ is a Riemann surface.
 To compactify we replace $\Omega^{0,\bu}(\C^2 - \{0\})$ by
-\beqn
+\begin{equation}
 \Omega^{\bu}(\R) \otimes \left(\C[w_1,w_2] \oplus (w_1 w_2)^{-1}\C[w_1^{-1},w_2^{-1}][-1] \right)
-\eeqn
+\end{equation}
 Also, let $\cA^{i,\bu}(C \times \R)$ denote $\Omega^{i,\bu}(C) \otimes \Omega^\bu(\R)$ for $i=0,1$.
@@
 For the tensor, observe
-\beqn
+\begin{equation}
 \Omega^{2,\bu}(C \times (\C^2 - \{0\})) \simeq \Omega^{0,\bu}(C) \otimes \Omega^{2,\bu}(\C^2 -\{0\}) \oplus \Omega^{1,\bu}(C) \otimes \Omega^{1,\bu}(\C^2 - \{0\}) ,
-\eeqn
+\end{equation}
 and 
-\beqn
+\begin{equation}
 \Omega^{3,\bu}(C \times (\C^2 - \{0\})) \simeq \Omega^{1,\bu}(C) \otimes \Omega^{2,\bu}(\C^2 - \{0\}) .
-\eeqn
+\end{equation}
 
 So the complex of fields is
-\beqn
+\begin{equation}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\eeqn
+\end{equation}
 
 This looks to be quasi-isomorphic to
-\beqn
+\begin{equation}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\eeqn
+\end{equation}
 
 The compactification of the hypermultiplet is
-\beqn
+\begin{equation}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\eeqn
+\end{equation}
 
@@
 Namely
-\beqn
+\begin{equation}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\eeqn
+\end{equation}
 If we regrade, then I think we are looking OK; this is level zero limit of $\lie{gl}(1)$ Chern--Simons theory.
@@
 Then the compactification looks like
-\beqn
+\begin{equation}
 \begin{tikzcd}
@@
 
+\cite{ButsonYoo}
+
+\printbibliography
+
 \end{document}
@@
 Let 
-\beqn
+\begin{equation}
 \sfR = \C[z_i,\lamba_j,\mu_k]_{i=1,2,3} / (1-z_i \lambda_i, 

### 2025-11-18 ac/lmp_revise/response.tex
lmp

\documentclass[11pt]{amsart}

\usepackage{../macros,amsaddr,physics}
\numberwithin{equation}{section}

\setcounter{tocdepth}{1}

%\linespread{1.2} %for editing
%\usepackage{mathpazo}

\begin{document}

\title{Response to referee report}

\maketitle

I thank the referee for their detailed reading of my manuscript and for the interesting and very helpful questions and
comments. 
Below, I have responded to each of these questions and comments.

\begin{itemize}
  \item I have added a remark after the definition of $\cL$-background to point to the familiar notion of "background
    fields".
    I have also added a paragraph in the introduction which more explicitly relates this work to the untwisted
    superconformal setting.
  \item We only consider theories which admit quantizations that are exact (or truncate) at one-loop in perturbation
    theory.
    For this reason, all of our anomalies necessarily occur at one-loop.
    I do not know of any theories which admit a one-loop symmetry of holomorphic vector fields but are  obstructed to
    having a higher-loop symmetry.
    It is an interesting question.
    I think to construct such an example one needs to consider more exotic theories that do not admit a strict action
    of holomorphic vector fields, but rather a homotopical one.
  \item There is no problem extending the results to non-rational $\lambda$ on flat space (which is all we consider
    here). But, we lose the geometric interpretation in this case. 
    I have added a paragraph at the end of section 3.2 detailing this.
  \item Proposition 5.2 proves that if we choose the bundle where the holomorphic quarks live correctly, then the
    theory has a quantum background for all holomorphic vector fields.
    Since holomorphic symplectic vector fields are automatically divergence-free, we see that symplectic vector fields
    will be a quantum symmetry for \textit{any} choice of $\lambda$ (hence for any choice of line bundle to twist the
    holomorphic quarks by).
    At the present time, I am unaware how to see the superconformal window at the level of the holomorphic twist.
    What I can prove is that the twist of any superconformal theory has a quantum background for all holomorphic
    vector fields.
    On the other hand, this is not a necessary condition; there are many supersymmetric theories (like QCD) which are
    non-conformal yet whose holomorphic twists admit a symmetry by holomorphic vector fields.
    I think what needs to be uncovered is how the process of RG flow intertwines with twisting.
    This would be a big breakthrough towards a holomorphic understanding of Seiberg duality.
 \item As indicated in the last bullet point, I know of many theories which are not conformal yet twist to a theory
   which admits a holomorphic vector field symmetry. 
  My conjectural interpretation is that $a^{hol}, c^{hol}$, and hence $a,c$, for these theories should be the ones
  associated to the superconformal theory that the original theory flows to (if such a flow exists).
  I am happy to put this in the draft if the referee thinks it is illuminating.
\item For the last typo suggestion, I believe that in equation (4.7) the space that $\beta$ lives is correct. 
  The factor of the canonical bundle is absorbed into the coefficients of the Dolbeault complex.
  \end{itemize}
\end{document}

### 2025-11-18 ac/lmp_revise/ac_revised.tex
lmp

\documentclass[11pt]{amsart}

\usepackage{macros,amsaddr,physics}
\numberwithin{equation}{section}

\addbibresource{refs_new.bib}

\renewcommand{\div}{\del_{\Omega}}
\renewcommand{\PV}{\mathrm{PV}}
\renewcommand{\op}{\operatorname}

\setcounter{tocdepth}{1}

%\linespread{1.2} %for editing
%\usepackage{mathpazo}

\begin{document}

\title{A complex geometric perspective on the $a,c$ anomalies}
\author{Brian R. Williams}
\thanks{Boston University, Department of Mathematics and Statistics}
\email{bwill22@bu.edu}

\maketitle

In four-dimensional conformal field theory, the numbers $a$ and $c$ are defined as coefficients of particular terms in the operator product expansion (OPE) of the energy-momentum tensor.
They can be understood as conformal anomalies appearing in the trace of the energy-momentum tensor in a background gravitational field as in
\[
\<T_\mu^\mu\> = -\frac{a}{16 \pi^2} \left(\text{Euler}\right)  + \frac{c}{16 \pi^2} \left(\text{Weyl}\right)^2 
\]
where $(\text{Weyl})^2$ is the square of the Weyl curvature and $(\text{Euler})$ is the Euler density.
Generally, conformal (or Weyl) anomalies exist in any even dimension; a complete classification has appeared in \cite{Duff,Deser:1993yx}.
The quantities $a,c$ are informative invariants of a four-dimensional conformal field theory.
For example, reminiscent of Zamolodchikov's $c$-theorem in two-dimensions \cite{Zamolodchikov} is the famous ``$a$-theorem'' in four-dimensions proposed in \cite{Cardy:1988cwa} and proved in \cite{Komargodski:2011vj}.
This states that the function $a$ is monotonic along (unitary) $RG$ flow implying, in particular, that the IR value of $a$ is strictly less than its UV value.

The numbers $a,c$ are also well-defined for superconformal field theories in four dimensions, but turn out to be much simpler to characterize.
This is because the superconformal symmetry necessarily mixes spacetime symmetry with supersymmetry and hence $a,c$ admit descriptions in terms of supersymmetric invariants of the theory.
Concretely, as we will review below, the $a,c$ anomalies can be understood in terms of anomalies to $R$-symmetry.

The $R$-symmetry is also used to twist a supersymmetric theory \cite{WittenTwist,CostelloHol,ESW}.
Typically, a supersymmetric theory is defined on some geometric class of spin manifolds.
The $R$-symmetry allows one to re-label fields of a theory so as to make sense of the theory in other geometric contexts.
So, for a topological twist, one can use $R$-symmetry to define the theory on an arbitrary smooth manifold.
For a holomorphic twist \cite{CostelloHol}, one can use $R$-symmetry to define the theory on complex manifolds.
$R$-symmetry is not the only thing needed to twist a supersymmetric theory; additionally, one must choose the data of a square-zero supercharge.
Fields and operators in the twisted theory can be described in terms of the cohomology with respect to the chosen supercharge.
The twisting process, hence, often provides a significant simplification of the original supersymmetric model.
The holomorphic twist is especially relevant for this paper since we consider four-dimensional supersymmetric theories which do not, generally, admit topological twists.

In this paper, we give an interpretation of the $a,c$ anomalies in terms of complex geometric invariants of the \textit{holomorphic twist} of a four-dimensional supersymmetric quantum field theory.
The symmetry by holomorphic vector fields is generally obtained as an enhancement of
the holomorphic
twist of the symmetries of a superconformal field theory \cite{SWsuco,HRSWconf,BGWW}.
For example, the holomorphic twist of a four-dimensional superconformal field theory will always have a symmetry by (a
central extension of) the Lie algebra of holomorphic vector fields on $\C^2 \setminus \{0\}$ \cite{SWsuco,BGWW}.
As a more exotic example, the holomorphic twist of the six-dimensional superconformal algebra is enhanced to the
infinite-dimensional exceptional Lie superalgebra $E(3|6)$, which contains as part of its bosonic subalgebra the Lie
algebra of holomorphic vector fields on $\C^3$.

In the way that our work pertains to supersymmetric quantum field theory, our main result is that $a,c$ can be
understood, in the holomorphic twist, in terms of anomalies for the symmetry of holomorphic vector fields.
Since twisting mixes $R$-symmetry with spacetime symmetry, we find that while this interpretation is not extremely surprising, it does provide a satisfying complex geometric perspective for the coefficients which is also computationally effective via the Riemann--Roch theorem.

As a consequence of the holomorphic formulation of the $a,c$ anomalies one obtains a classification of complex two-dimensional analogs of the Virasoro algebra in conformal field theory.
The higher dimensional affine Kac--Moody Lie algebra was proposed by Faonte, Hennion, and Kapranov in \cite{FHK} and was connected to symmetries of holomorphic quantum field theory in \cite{GWkm}.
The key point is that it is absolutely necessary, in higher dimensions, to work in a derived setting.
Indeed, the $n$-dimensional Kac--Moody algebras are all obtained as central extensions of the dg Lie algebra of derived sections of the structure sheaf on the punctured $n$-disk with values in an ordinary Lie algebra $\lie{g}$.
Similarly, one can contemplate central extensions of the the dg Lie algebra of derived sections of the tangent sheaf of the punctured $n$-disk.
In complex dimension two, $a,c$ label all possible central extensions of $\Gamma(\Hat{D}^2 - 0, \T)$.
For an approach to characterizing central extensions of the derived tangent sheaf which uses factorization homology we refer to \cite{HKgf}.
While we don't pursue any algebraic structures in this paper, we refer to recent work of Bomans and Wu \cite{Bomans:2023mkd} for a characterization of the two-dimensional Virasoro algebra from the point of view of the holomorphic twist of four-dimensional supersymmetery.
We will return to the relationship between the $a,c$ anomalies and the higher dimensional Virasoro algebra from the point of view of factorization algebras in future work.

The key technical aspect of this paper is a formulation of the supersymmetric theory, its twist, and symmetries within the Batalin--Vilkovisky (BV) formalism.
The universal symmetry of holomorphic field theory is introduced in section \ref{s:vf}.
In section \ref{s:bv}, we provide a background of anomalies in the BV formalism, specifically in the context of symmetries which largely follows Costello and Gwilliam's treatment \cite{CG2}. 
We turn to holomorphic theories in section \ref{s:hol}, and interpret the anomaly to quantizing holomorphic diffeomorphism symmetry as the Chern class of a line bundle over the universal complex manifold; thus affording the Riemann--Roch theorem as an effective method of computation.
In section \ref{s:rsymmetry} we turn to twists of supersymmetric theories and prove the precise relationship between anomalies to holomorphic diffeomorphism with $a,c$.
Finally, in section \ref{s:qcd} we elaborate on an example involving the twist of supersymmetric quantum chromodynamics (QCD).

\subsection*{Acknowledgements}

I thank Kevin Costello and Owen Gwilliam for their development of the quantum Noether theorem within the Batalin--Vilkovisky formalism as presented in their book \cite{CG2} which we rely heavily on throughout this paper.
I also am grateful to Ingmar Saberi for his collaboration on twists of four-dimensional $\cN=1$ superconformal theories which was the catalyst for this paper.
I thank Jingxiang Wu for feedback on a draft of this paper. 
Finally, I thank Boston University and the Center for Advanced Studies (CAS) at the Ludwig Maximilian University (LMU) in Munich, Germany for hospitality during the preparation of this work.
The only source of funding is salary from Boston University.
The author states that there is no conflict of interest.

\ul{Data availability statement}: The findings of this research were supported, in part, by references included in the
bibliography and cited throughout the work. The author has checked that all cited works (including this manuscript) are
available through either the \texttt{arXiv} database or standard, well-known, peer-reviewed academic journals.
\tableofcontents

\newpage

\section{A local model for holomorphic vector fields}
\label{s:vf}

Let $X$ be a complex manifold.
The $\dbar$-operator associated to a holomorphic vector bundle $V$ defines its Dolbeault complex $\Omega^{0,\bu}(X , V)$.
In degree $q$, the space $\Omega^{0,q}(X, V)$ denotes the space of smooth sections of the vector bundle $\Wedge^q \br \T_X^* \otimes V$ and the $\dbar$-operator extends to a differential $\dbar \colon \Omega^{0,q}(X,V) \to \Omega^{0,q+1}(X,V)$, $\dbar^2 = 0$.
%For any $U \subset X$, the complex $\Omega^{0,\bu}(U,V)$ is defined; in this way the Dolbeault complex is naturally a sheaf of cochain complexes.
%In fact, $\Omega^{0,\bu}(X,V)$ is an elliptic complex, see appendix \ref{a:local}.
By Dolbeault's theorem, the complex provides a resolution for the sheaf of holomorphic sections of the bundle $V$.

A holomorphic vector field is a holomorphic section of the holomorphic tangent bundle $\T_X$.
The sheaf of holomorphic vector fields has the natural structure of a sheaf of Lie algebras with bracket the Lie bracket of vector fields.
Since this bracket involves only holomorphic differential operators, it extends to a bracket on the Dolbeault complex of $\T_X$.
In local holomorphic coordinates the Lie bracket is
\begin{equation}
[f_{I,i} (z,\zbar) \d \zbar_I \del_{z_i} , g_{J,j} (z,\zbar) \d \zbar_J \del_{z_j}] = f_{I,i} \del_{z_i} g_{J,j} \d \zbar_I \wedge \d \zbar_J \del_{z_j} - g_{J,j} \del_{z_j} f_{I,i} \d \zbar_J \wedge \d \zbar_I \del_{z_i}.
\end{equation}
This bracket endows $\Omega^{0,\bu}(X, \T_X)$ with the structure of a dg Lie algebra where the differential is $\dbar$.
This leads to the following definition; for a recollection of terminology on local complexes and local Lie algebras we refer to \cite{CG1}.

\begin{dfn}
Let $\cT_X$ be the local dg Lie algebra whose underlying complex of vector bundles is
\begin{equation}
\Omega^{0,\bu}(X, \T_X) .
\end{equation}
The differential is the $\dbar$-operator associated to the holomorphic bundle $\T_X$.
The bracket is the Lie bracket of holomorphic vector fields extended to the Dolbeault complex as described above.

When $X = \C^n$ we will abusively refer to this local dg Lie algebra simply as $\cT$.
\end{dfn}

By Dolbeault's theorem, for $U \subset X$ a Stein open set there is a quasi-isomorphism $\cT_X(U) \simeq \op{Vect}^{hol}(U)$, the Lie algebra of holomorphic vector fields on $U$.

There is also the following relationship between $\cT$ and formal vector fields, which will be used subsequently.
Let \(E \to M\) denote a $\Z$-graded vector bundle on \(M\).
We consider the pro vector bundle of $\infty$-jets which we will denote by $j^\infty E$, see \cite{Anderson} or \cite[\S 5.6]{CostelloBook} for instance.
The sheaf of smooth sections of this pro vector bundle carries the natural structure of a $D_M$-module.
If $\cL = \Gamma(L)$ is a local $L_\infty$ algebra then $j^\infty L$ is a bundle of $L_\infty$ algebras.

\begin{lem}
The map
\begin{equation}
j_0^\infty \colon \cT(\C^n) \to \lie{vect}(n) [[\zbar, \d \zbar]] 
\end{equation}
induces a quasi-isomorphism of dg Lie algebras $j_0^\infty \cT (\C^n) \simeq \lie{vect}(n)$.
\end{lem}

\section{Anomalies and descent}
\label{s:bv}

In this section we rely on the quantum Batalin--Vilkovisky formalism as developed in the series of books \cite{CG1,CG2}.

\subsection{Anomalies as local functionals}
\label{sec:anomalies1}

Let $E$ be a vector bundle on a smooth manifold $M$.
The $C^\infty_M$-module of \defterm{local functionals} on $M$ is
\begin{equation}
\oloc(E) \define {\rm Dens}_M \otimes_{D_M} \prod_{n > 0} {\rm Hom}_{C^\infty_M} \left(\op{jet} (E) , C^\infty_M\right) ,
\end{equation}
where $D_M$ is the algebra of differential operators and $\op{jet}(E)$ is the $\infty$-jet bundle of~$E$.
Concretely, if $M$ is equipped with a volume form, a section of $\oloc(E)$ is a linear combination of objects of the form
\[
(\phi_1,\ldots,\phi_n) \mapsto \left[ (D_{1} \phi_1 \cdots  D_{n} \phi_n)  \; \dvol_M\right]
\]
where $\phi_i$ denote sections of $E$, where $D_i$ are differential operators $\sE \to C^\infty(M)$, and where $[-]$ means equivalence classes up to total derivative.

Suppose that $(\cE,\omega, S)$ is a classical BV theory on a smooth manifold $M$.
This means, in particular:
\begin{itemize}
\item $\cE = \Gamma(M,E)$ is sections of a $\Z$-graded vector bundle $E \to M$.
\item $\omega \colon E \otimes E \to \op{Dens}_M [-1]$ is a density valued, non-degenerate, pairing of degree~$-1$.
\item $S \in \oloc(\cE)$ is a local functional of cohomological degree zero.
\end{itemize}

The BV anti-bracket induced from $\omega$ equips the complex $\oloc(\cE)[-1]$ with the structure of a graded Lie algebra.
The \textit{classical master equation} is the condition that $S$ be a Maurer--Cartan element $\{S,S\} = 0$.
Equivalently, we can decompose $\{S,-\} = Q + \{I,-\}$ where $S(\Phi) = \omega(\phi,Q\phi) + I(\phi)$.
Then the classical master equation is $Q I + \frac12 \{I,I\} = 0$.
When this equation holds, the operator $\{S,-\}$ is square-zero and endows
\begin{equation}
\left(\oloc(\cE), \{S,-\}\right) ,
\end{equation}
with the structure of a dg Lie algebra.

Our goal in the remainder of the section is recall the various versions of symmetry that a theory in the BV formalism can exhibit.
To that end, suppose that $\lie{g}$ is an arbitrary dg Lie algebra.
Then we can define its Chevalley--Eilenberg complex $C^\bu(\lie{g})$ which is a commutative dg algebra.
Furthermore, we can tensor with a shift of local functionals
\begin{equation}
C^\bu(\lie{g}) \otimes \oloc(\cE)[-1]
\end{equation}
to obtain a dg Lie algebra.
The subcomplex 
\begin{equation}\label{eqn:red1}
C^\bu_{red}(\lie{g}) \otimes \oloc(\cE)[-1]
\end{equation}
is a sub dg Lie algebra.
To write this in a slightly more symmetric way, we recall that $S$ equips $\cE[-1]$ with the structure of a local $L_\infty$ algebra such that $\{S,-\}$ is precisely the Chevalley--Eilenberg differential.
Thus we can write this sub dg Lie algebra as
\begin{equation}\label{eqn:red}
C^\bu_{red}(\lie{g}) \otimes \cloc^\bu(\cE[-1])[-1] .
\end{equation}

Let $\cL$ be a local dg Lie algebra (our main example is the local dg Lie algebra $\cT_X$ from the previous section).
The Chevalley--Eilenberg differential equips the $C^\infty_M$-module of local functionals $\oloc(\cL[1])$ on the shift of $\cL$ with the structure of a cochain complex which we denote $\cloc^\bu(\cL)$
There is a cochain embedding
\begin{equation}
\cloc^\bu(\cL)(M) \subset C_{red}^\bu(\cL(M)) 
\end{equation}
from local cochains (by our conventions, local cochains are always reduced) to ordinary Chevalley--Eilenberg cochains of the dg Lie algebra of global sections $\cL(M)$.

Furthermore, the Lie bracket in \eqref{eqn:red} restricts to a Lie bracket on the subcomplex
\begin{equation}
\cloc^\bu(\cL \oplus \cE[-1])[-1] \subset C^\bu_{red}(\lie{g}) \otimes \cloc^\bu(\cE[-1])[-1] ,
\end{equation}
thus equipping the left hand side with the structure of a dg Lie algebra.

The embedding of local dg Lie algebras $\cE[-1] \to \cL \oplus \cE[-1]$ induces a map of dg Lie algebras
\begin{equation}
\cloc^\bu(\cL \oplus \cE[-1])[-1] \to \cloc^\bu(\cE[-1]) [-1] = \oloc(\cE)[-1] .
\end{equation}
Let $\op{InnerAct}(\cL,\cE)$ denote the kernel of this map.
The map of local dg Lie algebras $\cL \oplus \cE[-1] \to \cL$ induces an inclusion of dg Lie algebras
\begin{equation}
\cloc^\bu(\cL) \to \cloc^\bu(\cL \oplus \cE[-1])[-1] .
\end{equation}
This map factors through the dg Lie algebra $\op{InnerAct}(\cL,\cE) \subset \cloc^\bu(\cL \oplus \cE[-1])[-1]$.
We let 
\begin{equation}
\op{Act}(\cL,\cE) \define \op{InnerAct}(\cL,\cE) \slash \cloc^\bu(\cL) 
\end{equation}
be the quotient dg Lie algebra.

As cochain complexes there are isomorphisms
\begin{align*}
\op{Act}(\cL,\cE) & \simeq \cloc^\bu(\cL \oplus \cE[-1])[-1] \slash \left(\cloc^\bu(\cL)[-1] \oplus \cloc^\bu(\cE[-1])[-1] \right) \\
\op{InnerAct}(\cL,\cE) & \simeq \cloc^\bu(\cL \oplus \cE[-1])[-1] \slash \cloc^\bu(\cE[-1])[-1] .
\end{align*}
Thus, an element of $\op{Act}(\cL,\cE)$ is a local functional on the complex $\cL[1] \oplus \cE$ which does not depend solely on $\cL[1]$ or $\cE$.
Likewise, an element of $\op{InnerAct}(\cL,\cE)$ is a local functional which does not depend solely on $\cE$.

\begin{dfn}
Let $(\cE,\omega, S)$ be a classical BV theory and $\cL$ a local Lie algebra.
A \defterm{classical $\cL$-background} is a Maurer--Cartan element
\begin{equation}
S^{\cL} \in \text{Act}(\cL,\cE)^1 .
\end{equation}
Unwrapping the definitions above, this means that $\cS^{\cL}$ is a local functional on $\cL[1] \oplus \cE$ of cohomological degree zero which satisfies the equation
\begin{equation}\label{eqn:equivariantmaster}
\d_{\cL} S^{\cL} + \{S, S^{\cL}\} + \frac12 \{S^{\cL},S^{\cL}\} = 0 ,
\end{equation}
where $\d_{\cL}$ is the Chevalley--Eilenberg differential for $\cL$.
\end{dfn}

  The notion of a classical $\cL$-background in the BV formalism is motivated by the notion of "background" or
  "non-propagating" fields in physics.
  Here, the ordinary background fields are given as total degree one sections of $\cL$.
  For example, if $\cL$ describes the background coupling of a perturbative gauge field, then we would take 
  \begin{equation}\label{}
    \cL = \Omega^{\leq 1}(M, \lie{g})
  \end{equation}
  where the bracket is obtained from the Lie bracket on $\lie{g}$.
  The degree one elements are precisely $\lie{g}$-valued one-forms, so deformations of the connection.
  The degree zero elements are the infinitesimal symmetries of the background.

The equation \eqref{eqn:equivariantmaster} is referred to in \cite{CG2} as the $\cL$-\textit{equivariant classical master equation.}

In \cite{CostelloBook} the problem of perturbative quantization of classical theories within the BV formalism is put within an obstruction-deformation theoretic framework.
There are two main steps to construct a quantization.
The first is to construct a renormalized, or effective action, $\{I[L]\}$ which is a family of action functionals depending on a scale parameter $L$ whose $L \to 0$ limit agrees with the classical interaction $I$ (among other conditions).
Additionally, this effective family is required to satisfy the \textit{quantum master equation}
\begin{equation}\label{eqn:qme}
(Q + \hbar \triangle_L) e^{I[L]/\hbar}  = 0 ,
\end{equation}
where $\triangle_L$ is the effective BV Laplacian.

Starting with a classical BV theory $(\cE,\omega,S = S_{kin} + I)$, the problem of quantization order by order in $\hbar$ is controlled by the dg Lie algebra $\oloc(\cE)[-1]$.
While there are possibly many inequivalent ways to quantize a theory, even at one-loop, there is a scheme-dependent obstruction to the one-loop quantization of a classical BV theory which is measured by a degree $+1$ cohomology class
\begin{equation}
\Theta_{1-loop} \in H^1_{loc}(\cE) = H^2 \left(\oloc(\cE)[-1], \{S,-\}\right) ,
\end{equation}
obtained as the $L \to 0$ limit of the quantum master equation (in other words, it is the failure for an effective action to solve the master equation).
Similarly, if a quantization exists and is fixed to order $\hbar^{n-1}$ there is an obstruction $\Theta_{n-loop}\in H^1_{loc}(\cE)$ to extending this to a quantization to order $\hbar^n$.

Now we turn to the question of the equivariant quantization; more specifically, the quantization of $\cL$-backgrounds as defined above.
Here is the summary of the definition, we refer to \cite[Definition 13.2.2.1]{CG2} for the full definition.

\begin{dfn}
Suppose $\{I[L]\}$ is an effective family of interactions describing a quantum field theory (satisfies, amongst other conditions, the ordinary quantum master equation \eqref{eqn:qme}).
A \defterm{quantum $\cL$-background} is a family of effective actions
\begin{equation}
I^{\cL}[L] \in \cO(\cL[1] \oplus \cE) \slash \cO(\cL[1]) [[\hbar]]
\end{equation}
which agrees with $I[L]$ modulo functionals of $\cL[1]$ and
satisfies the following equivariant master equation
\begin{equation}
\d_\cL I^{\cL}[L] + Q I^{\cL}[L] + \frac12 \{I^{\cL}[L],I^{\cL}[L]\}_L + \hbar \triangle_L I^{\cL}[L] = 0 
\end{equation}
in $\cO(\cL[1] \oplus \cE) \slash \cO(\cL[1]) [[\hbar]]$.

Likewise, an \defterm{inner} quantum $\cL$-background is an effective family in a bigger class of functionals 
\begin{equation}
I^{\cL}[L] \in \cO(\cL[1] \oplus \cE) [[\hbar]]
\end{equation}
satisfying the same quantum master equation.
\end{dfn}

In the equivariant context the dg Lie algebras $\op{Act}(\cL,\cE)$ and $\op{InnerAct}(\cL,\cE)$ control different equivariant quantization situations, analogously to how the dg Lie algebra $\oloc(\cE)[-1]$ controls the non-equivariant situation.
For simplicity, we consider the problem of quantization to one-loop.
Throughout, we assume that a fixed quantization of the classical BV theory $(\cE,\omega,Q)$ is fixed at one-loop (in particular the one-loop obstruction $\Theta_{1-loop}$ vanishes).
The complex which controls quantizations of a classical $\cL$-background while leaving this quantization of the BV theory fixed is precisely~$\op{Act}(\cL,\cE)$.

\begin{prop}
Let $S^{\cL} \in \op{Act}(\cL,\cE)$ be a classical $\cL$-background and suppose $S_{1-loop} = S + \hbar S^{(1)}$ is a one-loop quantization of a classical BV theory $(\cE,\omega, S)$.
The obstruction to lifting this to a one-loop $\cL$-background is an element
\begin{equation}
\Theta^{\cL,\cE} \in H^2 \left(\op{Act}(\cL,\cE) \right) ,
\end{equation}
which, in this situation, lifts to an element
\begin{equation}
\Theta^{\cL,\cE} \in H^1_{loc}\left(\cL \ltimes \cE[-1] \; | \; \cL\right) .
\end{equation}

Similarly, the obstruction to lifting this to a one-loop inner $\cL$-background is an element
\begin{equation}
\Theta^{\cL} \in H^2 \left(\op{InnerAct}(\cL,\cE) \right) 
\end{equation}
which, in this situation, lifts to an element 
\begin{equation}
\Theta^{\cL} \in H_{loc}^1 (\cL) = H^2 \left(\cloc^\bu(\cL)[-1] \right) .
\end{equation}
\end{prop}

\subsection{Central charges}

The local cohomology classes of cohomological degree one deserve a special name which takes the form of the following terminological definition.

\begin{dfn}
The \defterm{space of central charges} for a local Lie algebra $\cL$ is the vector space 
\begin{equation}
H_{loc}^1 (\cL) .
\end{equation}
In particular, an obstruction to a quantum inner $\cL$-background determines a central charge for $\cL$.
\end{dfn}

The motivation for this definition is the following.
Suppose that our local Lie algebra $\cL = \Gamma(L)$ is defined on $\R^d$.
Typically, a \textit{current} is a $(d-1)$-form valued in Lagrangian densities.
More generally, for $\cL$ a local Lie algebra, we obtain the space of currents valued in $\cL_c$ by evaluating on the codimension one sphere $S^{d-1}$.
Here $\cL_c = \Gamma_c(L)$ is the cosheaf of compactly supported sections of the underlying vector bundle $L$.
Some care must be taken in this definition, since strictly it only makes sense to evaluate $\cL$ on open subsets; thus one should consider the value of $\cL$ on open sets which are infinitesimal neighborhoods of the $(d-1)$-sphere.
In nice situations, which we will turn to momentarily, the value of $\cL$ on a neighborhood of the form $(-\epsilon,\epsilon) \times S^{d-1}$ can be written as
\begin{equation}\label{eqn:splitting}
\Omega^\bu_c (- \epsilon, \epsilon) \otimes \lie{g}_{S^{d-1}}
\end{equation}
where $\lie{g}_{S^{d-1}}$ is some dg Lie (or more generally $L_\infty$) algebra.
We call $\lie{g}_{S^{d-1}}$ the Lie algebra of $S^{d-1}$-currents associated to $\cL$.

Now suppose that $\phi \in C^{1}_{loc}(\cL)$ is a local cocycle of cohomological degree $+1$.
Assume its value on $(-\epsilon,\epsilon) \times S^{d-1}$ can be expressed as $\int_{-\epsilon}^{\epsilon} \boxtimes \psi$ where
\begin{itemize}
\item $\int_{-\epsilon}^{\epsilon} \colon \Omega^\bu_c (- \epsilon, \epsilon) \to \C[-1]$ is the (degree one) integration map along the interval, and
\item $\psi$ is a degree two cocycle for the Lie algebra $\lie{g}_{S^{d-1}}$.
Automatically, $\psi$ is of cohomological degree two since integration along the interval is of cohomological degree one.
\end{itemize}
In this situation, $\psi$ determines a central extension 
\begin{equation}
0 \to \C \to \Hat{\lie{g}}_{S^{d-1}} \to \lie{g}_{S^{d-1}} \to 0 ,
\end{equation}
and we interpret $\Hat{\lie{g}}_{S^{d-1}}$ as the Lie algebra of centrally extended currents associated to $\cL$ and $\phi$.

We consider an example, studied in \cite{GWkm}.
Let $\lie{g}$ be an ordinary Lie algebra and consider the following local Lie algebra defined on $\C^n = \R^{2n}$
\begin{equation}
\cL = \lie{g} \otimes \Omega^{0,\bu}(\C^n) .
\end{equation}
Take the neighborhood $\C^n - 0 = \R \times S^{2n-1}$ of the sphere.
In this situation, there is a dense embedding of $\lie{g}$-valued derived algebraic sections of the structure sheaf into the spherical currents
\begin{equation}
\lie{g} \otimes \R \Gamma(D^n - 0, \cO) \hookrightarrow \lie{g}_{S^{2n-1}} .
\end{equation}
Any invariant and symmetric homogenous polynomial $\theta \in \Sym^{n+1}(\lie{g})^{G}$ determines a local cocycle for $\lie{g} \otimes \Omega^{0,\bu}(\C^n)$ defined by
\begin{equation}
\phi(\alpha_0,\ldots,\alpha_n) = \int_{\C^n} \theta ( \alpha_0 \del \alpha_1\cdots \del \alpha_n ) .
\end{equation}
The corresponding cocycle $\psi$ is precisely the higher dimensional Kac--Moody cocycle \cite{FHK}:
\begin{equation}
\psi(f_0,\ldots,f_n) = \oint_{S^{2n-1}} \theta ( \alpha_0 \del \alpha_1\cdots \del \alpha_n ) 
\end{equation}
where $f_0,\ldots,f_n \in \lie{g} \otimes \R \Gamma(D^n - 0, \cO)\subset \lie{g}_{S^{2n-1}}$.
Thus, every choice of ``level'' $\theta$ defines a central extension of the spherical currents.
In \cite{GWkm} we prove that such $\theta$ label all such central charges for this local Lie algebra which are $GL(n)$ and translation invariant.

Similarly, one could start with the local Lie algebra $\cT$ resolving holomorphic vector fields on $\C^n$.
We will explain a characterization of central charges in this case in the next section.
We will not, however, return to the resulting higher dimensional Virasoro algebras such central charges determine.
We refer to \cite{Bomans:2023mkd} for results in the complex two-dimensional setting.

\subsection{Diffeomorphism anomalies and Gelfand--Fuks cohomology}

We turn our attention to the holomorphic version of diffeomorphism, or gravitational, anomalies.
As recollected, the underlying local Lie algebra describing infinitesimal holomorphic diffeomorphisms is $\cT$, which resolves the Lie algebra of holomorphic vector fields.

The following result characterizes, in any dimension, the local anomalies to holomorphic reparametrization invariance.

\begin{thm}
\cite{BWgf}
\label{thm:bwgf}
On flat space $X = \C^n$ there is a quasi-isomorphism
\begin{equation}
\cloc^\bu \left(\cT ( \C^n ) \right) \simeq C^\bu_{red}(\lie{vect}(n)) [2n] .
\end{equation}
The space of central charges (on flat space) for $\cT$ is
\begin{equation}
H_{loc}^1 (\cL (\C^n)) \simeq H^{2n+1}(\lie{vect}(n)) .
\end{equation}
\end{thm}

Consider the one-dimensional case $n=1$.
Then the space of central charges for holomorphic vector fields is $H^3(\lie{vect}_1)$, which is one-dimensional.
By transgression this space is naturally isomorphic to the cohomology of the holomorphic Witt algebra $\lie{witt} = \C((z)) \del_z$, which is the Lie algebra of vector fields on the punctured formal disk.
The unique (up to scale) central charge for the local Lie algebra $\cT(\C)$ corresponds to the usual central charge in conformal field theory.
As a local cocycle for $\cT (\C)$, a local representative for this central charge is
\begin{equation}
\phi(\mu, \mu') = \int_\C J \mu \wedge \del (J \mu') .
\end{equation}
Of course, in coordinates $\mu = f(z,\zbar) \del_z$, where $f(z,\zbar)$ is a Dolbeault form of type $(0,\bu)$, this recovers the familiar expression for the Virasoro cocycle.

In the notation of the previous section, the space of spherical currents in this example receives a dense embedding of the Lie algebra of algebraic vector fields on the punctured disk $\C[z,z^{-1}] \del_z \hookrightarrow \lie{g}_{S^1}$.
The corresponding cocycle for $\C[z,z^{-1}]\del_z$, denoted $\psi$ above, is the standard Virasoro cocycle.

We comment that the result above can be generalized.
In \cite{BWgf} it is shown that for \textit{any} complex manifold $X$ of complex dimension $n$ that there is an isomorphism
\begin{equation}
H_{loc}^\bu(\cT(X)) \simeq H^\bu_{dR}(X) \otimes H^\bu (\lie{vect}(n)) [2n] .
\end{equation}
When $X = \C^n$ we recover the result as stated above.

\subsection{The holomorphic $a,c$ anomalies}

In the last section we have seen how the space of central charges for the local Lie algebra of holomorphic vector fields can be expressed in terms of the Gelfand--Fuks cohomology of formal vector fields.
In this section we recall an elegant description of this cohomology, following \cite{Fuks} and match with explicit representatives of the corresponding local cocycles in complex dimension two.

Let $\op{Gr}(n,k)$ be the complex Grassmannian of $n$-planes in $\C^k$. 
Denote by $\op{Gr}(n,\infty)$ the colimit of the natural sequence of topological spaces
\begin{equation}
\{\star\} \to {\rm Gr}(n, n+1) \to \op{Gr}(n,n+2) \to \cdots . 
\end{equation} 
It is a standard fact that ${\rm Gr}(n, \infty)$ is a model for the classifying space $BGL(n)$ of rank $n$ vector bundles.
%Let $EU(n) \to BU(n)$ be the universal principal $U(n)$-bundle. 
From the colimit description, this results in the skeletal filtration of the classifying space:
\begin{equation}
{\rm sk}_{k} BGL(n) = {\rm Gr}(n,k) .
\end{equation} 
Let $X_n$ denote the restriction of the universal bundle $EGL(n)$ over the $2n$-skeleton:
\begin{equation}
\begin{tikzcd}
X_n \ar[r] \ar[d] & E GL(n) \ar[d] \\
{\rm sk}_{2n} B GL(n) \ar[r] & B GL(n) .
\end{tikzcd}
\end{equation}

%\begin{rmk}
%Though not the way the Gelfand and Fuks originally proved the result, one can use the computation of the cohomology of $\W_d$ with coefficients in $\hOmega^k_d$ together with the spectral sequence (\ref{ss1}) to prove this description of $H^*(\W_d)$. 
%Indeed, the spectral sequence (\ref{ss1}) is isomorphic, up to regradings, to the Serre spectral sequence for the principal $\U(d)$-bundle $X_d \to {\rm sk}_{2d} B \U(d)$. 
%In other words, the formal de Rham differential on $\hOmega^*_d$ is exactly the $E_2$ differential for the Serre spectral sequence. 
%\end{rmk}

\begin{thm}[\cite{Fuks} Theorem 2.2.4] 
\label{thm:fuks}
There is an isomorphism of graded commutative algebras
\begin{equation}
H^\bu(\lie{vect}(n)) \cong H^\bu_{dR} (X_n) .
\end{equation}
The commutative product is the trivial one.
\end{thm}

Note that when $n = 1$ we have ${\rm sk}_2 B U(1) = \PP^1 \subset \PP^\infty = B U(1)$. 
Moreover, the restriction of the universal bundle is the Hopf fibration $U(1) \to S^3 \to \PP^1$ so that $X_1 \simeq S^3$.

It will be useful to say a few words about the proof of this theorem, as we will need a more general version to discuss mixed anomalies shortly.

For a Lie algebra $\lie{g}$ with a subalgebra $\lie{h} \subset \lie{g}$ the relative Lie algebra cohomology is defined to be the cohomology of the subcomplex 
\begin{equation}
C^\bu(\lie{g} \; | \; \lie{h}) \subset C^\bu(\lie{g})
\end{equation}
which consists of $\lie{h}$-invariant cochains $\phi \in C^\bu(\lie{g})$ satisfying $\iota_X \phi = 0$.
Here $\iota_X \colon C^\bu(\lie{g}) \to C^{\bu-1} (\lie{g})$ is the contraction with an element $X \in \lie{h}$.
The Hochschild--Serre spectral sequence for a subalgebra $\lie{h} \subset \lie{g}$ is a spectral sequence whose $E_2$ page is given in terms of relative Lie algebra cohomology
\begin{equation}
E_2 \simeq H^\bu(\lie{g}, \lie{h}) \otimes H^\bu(\lie{h}),
\end{equation}
and converges to the absolute Lie algebra cohomology $H^\bu(\lie{g})$.

In the current context we are interested in the absolute cohomology of $\lie{vect}(n)$.
The key idea is that the Hochschild--Serre spectral sequence for the subalgebra $\lie{gl}_n \subset \lie{vect}(n)$ consisting of linear vector fields can be interpreted geometrically in terms of classifying spaces.
One can identify the relative Lie algebra cohomology $H^\bu(\lie{vect}(n) \; | \; \lie{gl}_n)$ with the cohomology of the $2n$-skeleton $\op{sk}_{2n} BGL(n)$.
This identification can be extended to an isomorphism of spectral sequences between the Serre spectral sequence computing the cohomology of $X_n$, as a $GL(n)$ space over the $2n$-skeleton, and the Hochschild--Serre spectral sequence for the subalgebra $\lie{gl}_n \subset \lie{vect}(n)$ converging to the absolute cohomology of $\lie{vect}(n)$.

An immediate application of the Serre spectral sequence shows that first nontrivial cohomology above degree zero of $X_n$ is in degree $2n+1$ and we have
\begin{equation}
H^{2n+1}(\lie{vect}(n)) \simeq H^{2n+1}(X_n) \simeq H^{2n+2}(BGL(n)) .
\end{equation}
In other words, the degree $2n+1$ cohomology of formal vector fields is isomorphic to degree $2n+2$ polynomials built from universal characteristic classes of rank $n$ vector bundles.

In the previous section we have argued that the space of holomorphic diffeomorphism anomalies in $n$-dimensions, the space of central charges for $\cT$, is precisely this first non-trivial cohomology group of $X_n$.
When $n=1$ we have that $X_1 \simeq S^3$ hence the space of central charges for holomorphic vector fields in complex dimension one is one-dimensional, as expected (all being multiples of the universal characteristic class is $c_1^2 \in H^4 (BGL_1)$).
When $n = 2$ we see that the space of central charges is two-dimensional
\begin{equation}
H^1_{loc}(\cT(\C^2)) \simeq H^{5} (\lie{vect}_2) \simeq H^6(BGL(2)) = \C \cdot c_1^3 \oplus \C \cdot c_1 c_2
\end{equation}
spanned by the universal characteristic classes $c_1^3$ and $c_1 c_2$.

It will be convenient for our purposes to relabel this cohomology in terms of the degree six components of the universal Chern character:
\begin{equation}
\ch_1^3 = c_1^3, \quad \ch_1 \ch_2 = \frac12 \left(c_1^3 - 2 c_1 c_2\right) .
\end{equation} 
Any holomorphic diffeomorphism anomaly represented by a class $\Theta \in H^5(\lie{vect}(n))$ can be written as a linear combination of these universal classes
\begin{equation}
\label{eqn:achol}
\Theta = a^{hol} \cdot \ch_1 \ch_2 + c^{hol} \cdot \ch_1^3 .
\end{equation}
We will see momentarily how the coefficients $a^{hol},c^{hol}$ are related to the standard $a,c$ anomalies in four-dimensional conformal geometry.

We state explicit local models for the central charges $\ch_1 \ch_2, \ch_1^3$.

\begin{prop}\label{prop:holac}
The following are explicit degree one local cocycle representatives for the classes $\ch_1 \ch_2$ and $\ch_1^3$:
\begin{equation}
\Theta_{a^{hol}} = \frac{1}{12} \int_{\C^2} \op{tr} ( J \mu ) \op{tr}(\del J \mu \del J \mu) ,
\end{equation}
and
\begin{equation}
\Theta_{c^{hol}} = \frac{1}{6} \int_{\C^2} \op{tr}(J \mu) \op{tr}(\del J \mu) \op{tr}(\del J \mu) 
\end{equation}
respectively.
\end{prop}
\begin{proof}
The arguments that follow are elaborated in \cite{BWgf}.

There are two main steps.
The first is to identify explicit representatives in the cohomology of formal vector fields.
The second is in passing from Gelfand--Fuks classes in $H^5(\lie{vect}(2))$ to local cohomology classes in $H^1_{loc}(\cT(\C^2))$.
Both steps follow the general principle of descent.

The first step is accomplished by considering the double complex associated to the Lie algebra cohomology of $\lie{vect}(2)$ with coefficients in the formal de Rham complex~$\Omega^\bu(\Hat{D}^2)$.
Since the de Rham complex is quasi-isomorphic to $\C$ in degree zero, the resulting spectral sequence converges to $H^\bu(\lie{vect}(2))$.
The first page of the spectral sequence is generated, as an bigraded algebra, by generators $a_1,a_2$ of bidegree $(0,1),(0,3)$ respectively and by generators $(\tau_1,\tau_2)$ of bidegree $(1,1)$, $(2,2)$ respectively.
These generators are subject to the relations $\tau_1^3 = \tau_1 \tau_2 = \tau_2^2 = 0$.
In degree five, the following two classes remain at the $E_\infty$ page: $a_1 \tau_1^2, a_1 \tau_2$ which are represented by the totally skew symmetric tri-linear functionals on $\lie{vect}(2)$ with values in $\Omega^2(\Hat{D}^2)$:
\begin{align*}
a_1 \tau_1^2 \colon (X_0,X_1,X_2) & \mapsto \op{tr}(J X_0) \op{tr} (\d J X_1 \wedge \op{tr} (\d J X_2) + \cdots\\
a_1 \tau_2 \colon (X_0,X_1,X_2) & \mapsto \op{tr}(J X_0) \op{tr} (\d J X_1 \wedge \d J X_2) + \cdots .
\end{align*}
The $\cdots$ denote appropriate skew-symmetrization.

The passage from Gelfand--Fuks classes to local cohomology classes uses descent for the $\dbar$-operator.
If $\phi$ is one of the representatives above, we can extend it to a functional on $\cT = \Omega^{0,\bu}(\C^2, \T)$ with values in densities on $\C^2$ and can then take the local class.
The resulting local functional is of total degree $+1$ since the functionals are cubic and must have anti-holomorphic Dolbeault degree which sums to two.
\end{proof}

\subsection{Mixed anomalies}

In this section we generalize the discussion of holomorphic diffeomorphism anomalies on $\C^n$ to anomalies for a local Lie algebra built from both infinitesimal holomorphic diffeomorphisms and infinitesimal holomorphic gauge symmetries.
For gauge symmetries of the trivial holomorphic $G$-bundle, the local Lie algebra is the semi-direct product local Lie algebra
\begin{equation}
\cT_X \ltimes \lie{g} \otimes \Omega^{0,\bu}_X .
\end{equation}
Where the local Lie algebra $\cT_X$ resolving holomorphic vector fields acts by Lie derivative on the Dolbeault complex for the trivial bundle.

Our goal is to describe, just as we did in the case of $\cT_X$, the space of anomalies for the existence of quantum backgrounds with respect to this local Lie algebra.
Following the discussion of section \ref{sec:anomalies1} the space of such anomalies is the degree one local cohomology
\begin{equation}
H^1_{loc} (\cT_X \ltimes \lie{g} \otimes \Omega^{0,\bu}_X ).
\end{equation}
We will use the characterization, in particular, to describe diffeomorphism anomalies for holomorphic gauge theory in \ref{sec:mixed2}.
In analogy with the case that the group $G$ is trivial, we have the following result, which can be proved by similar methods as in theorem \ref{thm:bwgf}.

\begin{thm}
On flat space $X = \C^n$ there is a quasi-isomorphism
\begin{equation}
\cloc^\bu \left(\cT ( \C^n ) \ltimes \lie{g} \otimes \Omega^{0,\bu}(\C^n) \right) \simeq C^\bu_{red}(\lie{vect}(n) \ltimes \lie{g} \otimes \cO_n) [2n] .
\end{equation}
In particular, the space of mixed anomalies can be identified with the following Lie algebra cohomology
\begin{equation}
H_{loc}^1 \simeq H^{2n+1}(\lie{vect}(n) \ltimes \lie{g} \otimes \cO_n) .
\end{equation}
\end{thm}

Like in the case of pure holomorphic diffeomorphism anomalies, we will identify the space of mixed anomalies with certain characteristic classes.
This will be facilitated by the following result.

\begin{thm}[\cite{Khoroshkin}]
Let $G$ be a compact Lie group and $\lie{g}$ its complexified Lie algebra.
There is a graded ring isomorphism
\begin{equation}
H^\bu(\lie{vect}(n) \ltimes \lie{g} \otimes \cO_n \; | \; \lie{gl}_n \oplus \lie{g}) \simeq H^{\bu \leq 2n} \left(B GL(n) \times BG\right) ,
\end{equation}
where the right hand side is the cohomology of the $2n$-skeleton of the product of classifying spaces.
\end{thm}

In this theorem appears the relative Lie algebra cohomology.
In our context we are considering the relative cohomology with respect to the subalgebra
\begin{equation}\label{eqn:subalg}
\lie{gl}_n \oplus \lie{g} \subset \lie{vect}(n) \ltimes \lie{g} \otimes \cO_n 
\end{equation}
consisting of linear vector fields and constant $\lie{g}$-valued functions.
Using Khoroshkin's result we can proceed similarly as in the case $\lie{g}=0$ (see theorem \ref{thm:fuks} and the discussion following) to identify the absolute Lie algebra cohomology in terms of classifying spaces.
Indeed, let $Y_n$ be the restriction of the universal bundle over the $2n$-skeleton of $B GL(n) \times BG$.
As in the case $\lie{g}=0$, there is an isomorphism between the Hochschild--Serre spectral sequence for the subalgebra \eqref{eqn:subalg} and the Serre spectral sequence for the $GL(n) \times G$-space $Y_n$ over the $2n$-skeleton of $BGL(n) \times BG$.
This leads to the following.

\begin{thm}
Let $G$ be a compact connected Lie group and $\lie{g}$ is complexified Lie algebra.
There is an isomorphism of graded rings
\begin{equation}
H^\bu(\lie{vect}(n) \ltimes \lie{g} \otimes \cO_n) \simeq H^\bu(Y_n) .
\end{equation}
In particular, there is an isomorphism
\begin{equation}
H^{2n+1}(\lie{vect}(n) \ltimes \lie{g} \otimes \cO_n) \simeq H^{2n+2} (BGL(n) \times BG) .
\end{equation}
\end{thm}

Notice that when $G$ is the trivial group we have $Y_n = X_n$ and this result recovers the  result of Fuks that we recollected in theorem \ref{thm:fuks}.
From this theorem we see that the space of mixed anomalies is isomorphic to $H^{2n+2}(BGL(n) \times BG)$.
As in the case of pure holomorphic diffeomorphism anomalies, we can match such cohomology classes with explicit classes in the local cohomology of $\cT(X) \ltimes \lie{g} \otimes \Omega^{0,\bu}(X)$.

Let $\ch_j \in H^{2j}(BGL(n)), j=1,\ldots,n$ be the universal Chern characters as before.
Also, let
\begin{equation}
\theta_k \in \Sym^{k} (\lie{g}^*)^G \simeq H^{2k}(BG)
\end{equation}
denote an invariant polynomial of polynomial degree $k$.
Then the degree one local functional corresponding to the class
\begin{equation}
\ch_j \otimes \theta_{n-j+1} \in H^{2n+2}(BGL(n) \times BG), \quad j=0,\ldots,n,
\end{equation}
for example, is proportional to
\begin{equation}
\int_{\C^n} \op{tr}(J \mu (\del J \mu)^{j-1}) \, \theta_{n-j+1}(\del A, \ldots, \del A) .
\end{equation}
This can further be extended to the case $j=0$.
In this case, the local functional corresponding an invariant polynomial $\theta_{n+1}$ on $\lie{g}$ of polynomial degree $n+1$ is
\begin{equation}
\int_{\C^n} \theta_{n+1}(A, \del A, \ldots, \del A) . 
\end{equation}
This type of local cocycle, which does not involve any holomorphic vector fields, was studied in \cite{GWkm} where it is shown how it relates to higher dimensional Kac--Moody algebras \cite{FHK}.

\section{Holomorphic theories and their quantum anomalies}
\label{s:hol}

\subsection{A local index theorem from free field theory}

To any elliptic complex $(\cE,Q)$ on a manifold $M$ there exists a free theory in the Batalin--Vilkovisky formalism whose complex of fields (including ghosts, fields, anti-fields, etc.) is `double' the size of $\cE$:
\begin{equation}
\T^* [-1] \cE = \cE \oplus \cE^![-1] ,
\end{equation}
see \cite[section 4.6]{CG2}.
Here $\cE^!$ is the elliptic complex which is given by sections of the bundle $E^* \otimes \op{Dens}_M$ and whose differential is $Q^* \otimes \id$; here $E$ is the bundle whose sections is the underlying graded vector space of the elliptic complex $\cE$.
A field is a section of $\T^*[-1] \cE$ which we denote by the tuple $(\gamma, \beta)$.
The BV anti-bracket on observables is determined by the natural $(-1)$-shifted symplectic structure on the shifted cotangent space---explicitly this utilizes the natural integration pairing between sections of $E$ and sections of $E^* \otimes \op{Dens}_M$.
The action functional is given by
\begin{equation}
\int_M \beta (Q \gamma) ,
\end{equation}
so that the equations of motion imply, in particular, that $\gamma$ is $Q$-closed.

Some examples of this constructions may be familiar. 
If $M$ is just a smooth manifold, then taking $\cE = \Omega^\bu(M)[1]$ to be the shifted smooth de Rham complex of $M$ results in the BV description of abelian topological $BF$ theory.
If $M = \Sigma$ is a Riemann surface then $\cE = \Omega^{0,\bu}(\Sigma, K^{\otimes r})$ recovers the spin $r$ bosonic ghost system used in string theory.
%If $M$ is a spin manifold then we can take $\cE = \Gamma(\cS)$, sections of the spinor bundle, and $Q = \slashed \del$ to be the Dirac operator.

Next, let $\cL$ be a local $L_\infty$ algebra on $M$ and suppose that the elliptic complex $\cE$ is a local $\cL$-module.
The coupling
\begin{equation}\label{eqn:SLbackground}
S^{\cL}(\alpha;\beta,\gamma) = \int_M \beta (\alpha \cdot \gamma) ,
\end{equation}
determines an element $S^{\cL} \in \op{Act}(\cL;\T^* [-1] \cE)$.
By the virtue that $\cE$ is a $\cL$-module this coupling automatically satisfies the equivariant classical master equation \eqref{eqn:equivariantmaster}.
Thus, any local $\cL$-module $\cE$ defines a classical $\cL$-background for the resulting free BV theory $\T^*[-1] \cE$.

Since $\cE$ is a free theory there is no obstruction to lifting $S^\cL$ to a quantum $\cL$-background.
There is, nevertheless, an obstruction to lifting this to an inner quantum $\cL$-background.
This obstruction admits an elegant description.

\begin{thm}[\cite{GwilliamThesis}]\label{thm:owen}
Let $(\cE,Q)$ be an elliptic complex which is equipped with a local $\cL$-action, where $\cL$ is some local Lie algebra.
Endow the BV theory $\T^*[-1] \cE$ with the structure of a classical $\cL$-background via $S^{\cL}$ in equation \eqref{eqn:SLbackground}.
The anomaly to the existence of a quantum inner $\cL$-background for $\T^*[-1] \cE$ is the trace of the action of $\cL$ on $\T^*[-1] \cE$.
\end{thm}

We specialize to when $M = X$ is a complex $n$-manifold.
The basic free holomorphic theory we consider is labeled by a holomorphic vector bundle $V$ on $X$.
The elliptic complex is the Dolbeault complex resolving the sheaf of holomorphic sections of $V$:
\begin{equation}\label{eqn:dolbeaultelliptic} 
\cE_{V} = \Omega^{0,\bu}(X, V) .
\end{equation}
The action functional $\int_X \beta \dbar \gamma$ returns the familiar free action of the $\beta\gamma$-ghost system used in string theory.
Notice that in dimension $n$, however, that the field $\beta$ is an element
\begin{equation}
\beta \in \Omega^{n,\bu}(X,V^*)[n-1],
\end{equation}
whose degree zero component is a field of Dolbeault type $(n,n-1)$.

The following will be the most important case for us.
We assume that $V \to X$ is a \textit{natural} holomorphic vector bundle; meaning a bundle built from the tangent bundle by taking duals, tensor products, direct sums, cohomological shifts etc..
This implies that the space of holomorphic sections of $V$ is equipped with the structure of a representation for the Lie algebra of holomorphic vector fields.
The action is by the Lie derivative.
This action extends in a natural way to a local $\cT_X$-module structure on the elliptic complex $\cE_V$ resolving the sheaf of holomorphic sections of $V$.

Summarizing, we have the following.

\begin{prop}
If $V \to X$ is a natural holomorphic vector bundle then the corresponding BV theory $\T^* [-1] \cE_V$ is equipped with a $\cT_X$-background defined by the coupling
\begin{equation}\label{eqn:Tbackground}
S^{\cT}(\mu ; \beta,\gamma) = \int_X \beta (L_\mu \gamma) ,
\end{equation}
where $L_\mu$ denotes the Lie derivative.
\end{prop}

In this context we can use \ref{thm:owen} to obtain a geometric description of the obstruction to this lifting to an inner $\cT_X$-background.

\subsection{Riemann--Roch theorem and anomalies}

Let $\cM$ denote the moduli stack of complex $n$-manifolds.
For the purposes of this note we will not need a precise model for this moduli space, but we will use the following features:
\begin{enumerate}
\item There is a universal complex manifold $\pi \colon \cX \to \cM$ whose fiber over an $n$-manifold $X \in \cM$ is $X$ itself.
\item Any natural bundle (one built from the holomorphic tangent bundle by taking duals, tensor products, direct sums etc.) defines a vector bundle on the universal $n$-manifold.
For example, there is a universal tangent bundle $\cT_{univ} \to \cX$ whose restriction to a complex $n$-manifold $X$ yields $\T_{X}$.
\item A model for the tangent complex of $\cM$ at a fixed complex $n$-manifold $X$ is the dg Lie algebra
\begin{equation}
\mathbb{T}_X \cM \simeq \cT_X = \Omega^{0,\bu}(X, \T_X) .
\end{equation}
\end{enumerate}

The last item is a formal version of the formalism of Kodaira and Spencer which says that the formal moduli problem for deforming complex structures is controlled by the dg Lie algebra $\cT_X$.
This means that a formal deformation of a complex $n$-manifold is a Beltrami differential
\begin{equation}
\mu \in \Omega^{0,1}(X, \T_X)
\end{equation}
which satisfies the Maurer--Cartan equation
\begin{equation}\label{eqn:beltramimc}
\dbar \mu + \frac12 [\mu,\mu] = 0.
\end{equation}
The deformed complex $n$-manifold has Dolbeault complex
\begin{equation}
\left(\Omega^{0,\bu}(X) , \dbar + \mu\right) .
\end{equation}
In other words, a formal deformation has the effect of modifying the $\dbar$ operator as $\dbar \rightsquigarrow \dbar + \mu$.
The condition that this squares to zero is precisely the Maurer--Cartan equation.

Now suppose that $V \to \cX$ is a universal holomorphic vector bundle.
We then obtain a family of elliptic complexes $\cE_{V}$ over $\cX$ whose fiber over a complex $n$-manifold $X \in \cM$ is the elliptic complex $\cE_{X,V}$ from \eqref{eqn:dolbeaultelliptic}.
To get a family over the moduli of complex structures $\cM$ we take the (derived) pushforward along $\pi \colon \cX \to \cM$ to get the family of elliptic complexes $\RR \pi_* \cE_{V}$ over $\cM$.
The determinant of this virtual bundle is a special case of the determinant, or anomaly, line bundle \cite{Freed, Quillen} associated to a family of $\dbar$-operators parameterized by a moduli of complex structures.

Now we consider the formal completion of $\cM$ at $X$.
By the expectation (3) above, the formal moduli space $\cM^{\;\Hat{}}_X$ is described by the dg Lie algebra $\cT_X$:
\begin{equation}
\cM^{\;\Hat{}}_X \simeq \text{B} \cT_X .
\end{equation}
The resulting family $\RR \pi_* \cE_V$ over the formal completion corresponds to a $\cT_X$-representation which is precisely encoded by the $\cT_X$-background \eqref{eqn:Tbackground}.

The consequence of theorem \ref{thm:owen} is that the one-loop anomaly for an inner $\cT_X$-background is the first Chern class of the virtual bundle $\RR \pi_* \cE_V$.

\begin{prop}
Let $V$ be a natural holomorphic vector bundle and consider the resulting $\cT_X$-background for the BV theory $\T^* [-1] \cE_{X,V}$.
When $X = \C^n$, the anomaly to lifting this to an inner $\cT_X$-background is given by the class
\begin{equation}
\left. \op{Td} \cdot \ch(V)\right|_{2n+2} \in H^{2n+2} (BU(n)) \simeq H^{2n+1} (\lie{vect}(n)) \hookrightarrow H^1_{loc}(\cT(X)) .
\end{equation}
\end{prop}

The consequence of this result in the complex one-dimensional case is hopefully familiar.
The ghost system for the bosonic string is the free theory based off of the complex $\cE_{\Sigma, \T_\Sigma [1]}$, where $\T_\Sigma[1]$ is the holomorphic tangent bundle shifted down by one.
The resulting anomaly in terms of universal Chern characters is
\begin{equation}
\Td \cdot \ch(\T[1])|_4 = - \left(1 + \frac12 c_1 + \frac{1}{12} c_1^2\right)\left(1 + c_1 + \frac12 c_1^2\right)|_4 = - \frac{13}{12} c_1^2 .
\end{equation}
The typical normalization for the generator of the Virasoro central charge is $\frac1{24} c_1^2$, implying that the central charge of this free system is $c = -26$ as expected.
To compare, the anomaly associated to the complex free boson CFT is $\frac1{12} c_1^2$; thus recovering the fact that the obtained by gauging $13$ complex copies of the free boson by holomorphic vector fields is anomaly free.
%We will comment more on this in section \ref{??}.

Let's move to the complex $n=2$ dimensional situation.
As an example, consider the case where $V$ is the trivial rank one bundle.
Then the universal Riemann--Roch theorem implies that the anomaly is represented by the local cocycle corresponding to the universal class 
\begin{equation}
\Td|_6 = - \frac{1}{24} \ch_1 \ch_2 + \frac{1}{48} \ch_1^3 .
\end{equation}
In other words $a^{hol}(V = triv) = -1/24$, $c^{hol}(V = triv) = 1/48$ so that
\begin{equation}
- 4 \pi^2 \Theta_{V = triv} = -\frac{1}{24} \int_{\C^2} \op{tr} ( J \mu ) \op{tr}(\del J \mu \del J \mu) + \frac{1}{48} \int_{\C^2} \op{tr}(J \mu) \op{tr}(\del J \mu) \op{tr}(\del J \mu) .
\end{equation}

We can generalize this example to an arbitrary natural line bundle which we will write as $V = K^\lambda$ for $\lambda$ a rational number, where $K$ is the canonical bundle on~$\C^2$.
We record the result here.

\begin{lem}\label{lem:grrfree}
There are the following expressions for the holomorphic central charges associated to the free holomorphic theory $\T^* [-1] \cE_{K^{\lambda}}$:
\begin{equation}
a^{hol} (K^\lambda) = \frac{1}{24} r \quad \text{and} \quad c^{hol}(K^\lambda) = - \frac{1}{48} r^3 ,
\end{equation}
where $r = 2 \lambda -1$.
\end{lem}
\begin{proof}
This follows from the expression in universal Chern classes
\begin{equation}
\left. \Td \cdot \ch (K^\lambda)\right|_6 = \frac{1}{12} \left(\lambda - \frac12\right) \ch_1 \ch_2 - \frac16 \left(\lambda - \frac12\right)^3 \ch_1^3 ,
\end{equation}
which is straightforward to verify.
\end{proof}

Observe that under $\lambda \mapsto 1- \lambda$ one has $r \mapsto - r$.
In particular, $a^{hol}$ and $c^{hol}$ satisfy 
\begin{equation}
a^{hol}(K^\lambda) = - a^{hol} (K^{1-\lambda}), \quad c^{hol}(K^\lambda) = - c^{hol} (K^{1-\lambda}) .
\end{equation}

We point out that expression for this anomaly makes sense for any non-rational $\lambda \notin \Q$.
In fact, it makes sense even for complex values of $\lambda$.
For such $\lambda$ we lose the geometric interpretation as the Chern class of some line bundle, but nevertheless the
formula for the anomaly still holds.

\subsection{Computing the anomaly using the holomorphic gauge}

Recall that the free part of a holomorphic theory is determined by the $\dbar$ operator associated to some holomorphic vector bundle.
In \cite{BWhol} it is shown that any holomorphic theory admits a natural gauge where the gauge fixing operator is $Q^{GF} = \dbar^\star$.
The corresponding renormalization is well-behaved.
On flat space $\C^n$ the main results concerning renormalization for holomorphic theories can be summarized as follows.

\begin{thm}[\cite{BWhol}]
\label{thm:bw}
Suppose $(\cE,\omega,S = S_{free} + I)$ is a holomorphic theory on $\C^n$ and let $S[L]$ denote the effective action, at scale $L$, constructed using the gauge fixing operator $Q^{GF} = \dbar^\star$ whose corresponding propagator is $P_{\epsilon <L}$. 
\begin{enumerate}
\item To first-order in $\hbar$ the effective action is finite
\begin{equation}
I[L] = \lim_{\epsilon \to 0} W(P_{\epsilon}^L , I) \mod \hbar^2
\end{equation}
In particular, all one-loop counterterms are identically zero.
\item Suppose the free part of the action is of the form $S_{free} (\Phi) = \omega(\Phi, \dbar \Phi)$.
The anomaly to solving the quantum master equation to first-order in $\hbar$ can be expressed as the sum over wheels with exactly $(d+1)$-vertices. 
Explicitly, as a local functional this anomaly is
\begin{equation}\label{eqn:generalanomaly}
\Theta_{1-loop} = \lim_{L \to 0} \lim_{\epsilon \to 0} \sum_{\Gamma \in {\rm Wheel}_{n+1}, e} W_\Gamma(P_{\epsilon < L}, K_\epsilon,I) .
\end{equation}
where the sum is over all wheels with $(n+1)$-vertices and distinguished edges thereof.
Here $K_\epsilon$ is the heat kernel associated to the generalized Laplacian built using the gauge fixing operator $\dbar^\star$.
\end{enumerate}
\end{thm}

Let's return to the context of the previous section.
We consider the free BV theory~$\cE_{V}$ on $X = \C^n$, where $V$ is some natural vector bundle, in the $\cT$-background~$S^{\cT}(\xi;\beta,\gamma)$ from~\eqref{eqn:Tbackground}.
In this case we can use the trivialization $V \simeq \C^n \times V_0$ to identify the $\dbar$-operator for $V$ with $\dbar \otimes \id$ where $\dbar$ is simply the ordinary $\dbar$-operator on $\C^n$.
Correspondingly, we choose the gauge fixing operator is $\dbar^\star \otimes \id$ where $\dbar^\star$ is Hodge adjoint of $\dbar$ constructed using the flat hermitian metric on $\C^n$. 
Explicitly, the heat kernel is given by
\begin{equation}
K_L(z,w) = \frac{1}{(2\pi i L)^n} e^{-|z-w|^2/4L} \otimes \id_V \in \cE_{V} \Hat{\otimes} \cE_V [1] 
\end{equation}
where $\id_V \in V_0 \otimes V_0^*$ represents the identity morphism $V_0 \to V_0$.
The propagator is 
\begin{equation}
P_{\epsilon<L} (z,w) = \int_{T = \epsilon}^L \d T \, (\dbar^\star \otimes \id) \, K_T(z,w) .
\end{equation}

Since $\T^*[-1]\cE_{V}$ is a free BV theory, item (1) of theorem \ref{thm:bw} implies that 
\begin{equation}
S^{\cL} [L] \define \lim_{\epsilon \to 0} W(P_{\epsilon}^L , I) \mod \hbar^2 
\end{equation}
is a one-loop quantum $\cT$-background.
Further, item (2) implies that the obstruction to lifting this to a one-loop inner $\cT$-background is
\begin{equation}
\Theta = \lim_{L \to 0} \lim_{\epsilon \to 0} \sum_{\Gamma \in {\rm Wheel}_{n+1}, e} W_\Gamma(P_{\epsilon < L}, K_\epsilon,I) ,
\end{equation}
which automatically determines a degree one cocycle in $\cloc^\bu(\cT(\C^n))$.

We specialize to complex dimension $n=2$.
In this case, the anomaly $\Theta$ is expressed as a sum over wheels with three vertices.
Since the effective action is $GL(2,\C)$-invariant it is straightforward to see that based on symmetry the anomaly local cocycle $\Theta$ is cohomologous to a linear combination of the cocycles $\Theta_a^{hol}$ and $\Theta_c^{hol}$ from proposition \ref{prop:holac}.
That is
\begin{equation}
- 4 \pi^2 \Theta_V = a^{hol}(V) \Theta_{a^{hol}} + c^{hol}(V) \Theta_{c^{hol}}
\end{equation}
for some coefficients $a^{hol}(V),c^{hol}(V)$.
Instead of computing these coefficients explicitly using the effective action, which appears to be quite cumbersome, we will refer to the Riemann--Roch theorem as outlined in the previous subsection to fix them.
%In the appendix we have worked out the coefficient using the effective action in the case~$n=1$.
%\brian{fix this citation}

\subsection{Symplectic vector fields}
Consider a complex symplectic surface $(X,\omega)$, and let $\op{div}$ be the divergence with respect to the holomorphic
two-form $\omega$.
This operator acts on holomorphic vector fields.
But, because it is holomorphic it also extends to the Dolbeault complex of the holomorphic tangent bundle.
The two-term complex 
\begin{equation}\label{}
  \cT \xto{\op{div}} \Omega^{0,\bu}(X)[-1]
\end{equation}
is a local dg Lie algebra model for the sheaf of holomorphic \textit{symplectic} vector fields on $X$.
Equivalently, this resolves divergence-free vector fields with respect to the Calabi--Yau form $\omega$.
We denote this local dg Lie algebra by $\cT^{symp}$.
Observe that there is a natural map of local Lie algebras $\cT^{symp} \to \cT$, hence any theory with a $\cT$-background
automatically defines a $\cT^{symp}$-background.

At the level of local cohomology, there is thus a map of cochain complexes 
\begin{equation}\label{}
  \cloc^\bu(\cT) \to \cloc^\bu(\cT^{symp}) .
\end{equation}
On $X = \C^2$ we will use the translation invariant volume form $\omega = \d z_1 \d z_2$.
because the three-linear representatives for $a^{hol},c^{hol}$ for $H^1_{loc}(\cT)$ involve the divergence of the
holomorphic vector field, we see that in cohomology the images of $a^{hol}, c^{hol}$ in $H^\bu_{loc}(\cT^{symp}(\C^2))
$ are trivial.

This implies that there is no notion of "central charge" for the symmetry of symplectic holomorphic vector fields in
complex dimension two.
(Or, rather, the central charge always vanishes.)

\subsection{Riemann--Roch theorem for mixed anomalies}
\label{sec:mixed2}

So far we have only discussed anomalies for the action of holomorphic vector fields on free theories within the BV formalism.
These anomalies are avatars of gravitational, or conformal, anomalies as portrayed in the physics literature.
For non-free theories, like gauge theories, there are also possible \textit{internal} anomalies, like gauge anomalies, which must be trivial in order for quantization to exist.

In this section we consider anomalies present when holomorphic gauge theory is put in a $\cT$-background.
In addition to the holomorphic gravitational anomalies we have been focused on thus far, there will also be pure gauge and mixed anomalies which must be trivialized.
To make the discussion as parallel as possible with the case of pure diffeomorphism anomalies, we consider the case that both diffeomorphisms and gauge symmetries are considered as background fields.
From this we will be able to deduce mixed anomalies for interacting gauge theories.

Let $G$ be a Lie group.
Let $\cM_G$ denote the moduli of pairs $(X,P)$ of a complex $n$-manifold $X$ together with a principal holomorphic $G$-bundle $P$ on $X$.

As in the case of complex $n$-manifolds, we will not develop a precise model for this moduli space, but we will use the following expected features:
\begin{enumerate}
\item There is a universal bundle $\pi \colon \cX_G \to \cM_G$ whose fiber over a pair $(X,P) \in \cM_G$ is the principal bundle $P \to X$ itself.
\item Any natural bundle (one built from the holomorphic tangent bundle by taking duals, tensor products, direct sums etc.) together with a representation of $G$ defines a vector bundle on the universal $n$-manifold.
%For example, there is a universal tangent bundle $\cT_{univ} \to \cX$ whose restriction to a complex $n$-manifold $X$ yields $\T_{X}$.
\item A model for the tangent complex of $\cM$ at the pair $(X,P_{triv})$, where $P_{triv}$ is the trivial $G$-bundle, is the semi-direct product dg Lie algebra
\begin{equation}
\mathbb{T}_X \cM_G \simeq = \Omega^{0,\bu}(X, \T_X) \ltimes \Omega^{0,\bu}(X) \otimes \lie{g} .
\end{equation}
This dg Lie algebra is a resolution of the sheaf of holomorphic sections of the sheaf of Lie algebras $\cT^{hol}_X \ltimes \cO^{hol} \otimes \lie{g}$.
\end{enumerate}

The last point says that a formal deformation of a pair $(X,P_{triv})$ is a Beltrami differential
$\mu \in \Omega^{0,1}(X, \T_X)$, satisfying \eqref{eqn:beltramimc}, as before together with a $(0,1)$ connection 
\begin{equation}
A \in \Omega^{0,1}(X) \otimes \lie{g}
\end{equation}
which together satisfy the Maurer--Cartan equation
\begin{equation}
(\dbar + \mu) A + \frac12 [A,A] = 0.
\end{equation}
The deformed complex $n$-manifold has Dolbeault operator $\dbar + \mu$ and the deformed principal bundle has Dolbeault operator $\dbar + A$.

\begin{prop}
\label{prop:mixedRR}
Let $V$ be a natural holomorphic vector bundle equipped with a $G$-action and consider the resulting $\cT_X \ltimes \Omega^{0,\bu}_X \otimes \lie{g}$-background for the BV theory $\T^* [-1] \cE_{X,V}$.
When $X = \C^n$, the anomaly to lifting this to an inner $\cT_X \ltimes \Omega^{0,\bu}_X \otimes \lie{g}$-background is given by the class
\begin{equation}
\left. \op{Td} \cdot \ch_{GL(n) \times G} (V)\right|_{2n+2} \in H^{2n+2} (BGL(n) \times BG) \hookrightarrow H^1_{loc}(\cT(X) \ltimes \Omega^{0,\bu}(X) \otimes \lie{g}) ,
\end{equation}
where $\ch_{GL(n) \times G} (V)$ is the $GL(n) \times G$-character of the representation $V$.
\end{prop}

Let's consider a simple example when the complex dimension $n=1$ and $G = GL_1(\C) = \C^\times$.
Suppose that $V$ is the trivial super vector bundle $W[\eps] = W \oplus \Pi W$ where $W$ is some natural vector bundle on a curve.
In this case, the pure holomorphic gravitational anomaly for the BV theory $\T^* [-1] \cE_{\C,W[\eps]}$ vanishes.
So, the anomaly corresponds to an element in
\begin{equation}
H^2(BGL_1) \otimes H^2(B G) \subset H^4(BGL_1 \times B G), 
\end{equation}
which turns out to be proportional to $c_1 \til c_1$ where $c_1$ represents the `gravitational' first Chern class and $\til c_1$ is the background gauge $G=GL_1(\C)$ class.
Explicitly, as a local functional this class is represented by
\begin{equation}
\int_\C J \mu \op{Tr}(\del A) 
\end{equation}
where $\mu$ is a background holomorphic vector field and $A$ is a background gauge field.
This anomaly was found independently in \cite{GRWthf} where it is interpreted as the famous Calabi--Yau anomaly for the two-dimensional $B$-model.
Indeed, the holomorphic theory we are considering here is a holomorphic twist of the two-dimensional $\cN=2$ chiral multiplet valued in $W$.
The $GL_1(\C) \times GL_1(\C)$ represents, at the group level, the dilations and $R$-symmetry which remains inside of the two-dimensional $\cN=2$ superconformal algebra after twisting.

\subsection{Holomorphic gauge theories}

In this section we have only discussed anomalies for \textit{background} holomorphic diffeomorphism symmetry or \textit{background} holomorphic gauge symmetry where it suffices to just consider the underlying free theory.
For non-free theories, like gauge theories, there are also possible \textit{internal} anomalies, like gauge anomalies, which must be trivial in order for quantization to exist.
In this section we explain how holomorphic diffeomorphism symmetry mixes with possible internal gauge symmetries.

The idea is the following.
We start with a holomorphic gauge theory which has a background symmetry by holomorphic vector fields.
Before discussing the issue of quantizing this background symmetry, we first need to know that the gauge theory has no internal anomaly.
Once this internal anomaly is trivialized, we can then treat the underlying free theory as a theory with a background symmetry by $\cT \ltimes \Omega^{0,\bu} \otimes \lie{g}$.
We then treat the problem just as we did before with two caveats.
First, since we have already trivialized the pure gauge anomaly, it suffices to only look at anomalies which depend non-trivially on a holomorphic vector field.
Second, the terms in the anomaly which have a nontrivial dependence on the gauge field represent the anomaly to having a quantum $\cT$-background.
Once these are trivialized, we can then contemplate the anomaly to having a quantum inner $\cT$-background; this is represented by the terms in the anomaly which are independent of the gauge field.

Let's consider an explicit example.
Let $\lie{g}$ be a Lie algebra of a compact Lie group~$G$.
The basic holomorphic gauge theory we consider is holomorphic $BF$ theory which can be defined on any complex manifold $X$.
Globally, holomorphic $BF$ theory is the shifted cotangent bundle to the moduli stack of holomorphic $G$-bundles on $X$.
Within the perturbative BV formalism the fields consist of pairs 
\begin{align*}
A & \in \Omega^{0,\bu}(X, \lie{g})[1] \\
B & \in \Omega^{n,\bu}(X, \lie{g}^*)[n-2]
\end{align*}
and the action is of standard $BF$-type: $S_{BF} = \int_X B F_A$.
This theory enjoys a classical background $\cT$-symmetry defined by
\begin{equation}
S^\cT = \int_X B (L_\mu A) .
\end{equation}

Holomorphic $BF$ theory suffers from an internal gauge anomaly.
As usual, we focus just on the case $X = \C^n$.
Using theorem \ref{thm:bw} one can show the following.

\begin{prop}
\label{prop:puregauge}
Holomorphic $BF$ theory on $\C^n$ is anomalous at one-loop in perturbation theory.
The local functional representing this anomaly is
\begin{equation}
- \frac{1}{(n+1)!}\int_{\C^n} \op{Tr}_{ad} \left(A (\del A)^n\right) ,
\end{equation}
where the trace denotes the trace is in the adjoint representation of $\lie{g}$ on itself.
\end{prop}

%The local functional representing the pure gauge anomaly is automatically a cocycle in the local complex 
%\begin{equation}
%\cloc^\bu \left( \Omega^{0,\bu}(\C^n, \lie{g}) \right)
%\end{equation}
%of cohomological degree one.
%In \cite{GWkm} an injective map of cochain complexes
%\begin{equation}
%\Sym^{n+1}(\lie{g})^{G} \hookrightarrow \cloc^\bu \left( \Omega^{0,\bu}(\C^n, \lie{g}) \right) [1] .
%\end{equation}
%The anomaly of holomorphic $BF$ theory is represented by the invariant polynomial
%\begin{equation}
%X \in \lie{g} \mapsto \op{Tr}_{ad} (X^{n+1}) ,
%\end{equation}
%which we will denote by $\op{ch}_{n+1}(\T_{B \lie{g}})$.
For example, in complex dimension one $n=1$, the holomorphic $BF$ theory associated to any semi-simple Lie algebra is anomalous.
In complex dimension two $n=2$ the anomaly for holomorphic $BF$ theory vanishes for complex semi-simple Lie algebras.
%(As is the case for twists of four-dimensional supersymmetric QCD, see section~\ref{sec:qcd}.)

We now turn to thinking of the underlying free theory as a theory with a background symmetry by $\cT \ltimes \Omega^{0,\bu} \otimes \lie{g}$.
Such anomalies to quantization will be labeled by certain elements in
\begin{equation}
H^{2n+2} (BGL(n) \times BG) 
\end{equation}
as in the last section.
The thing that distinguishes this discussion from the last section is that we are assuming that the component in $H^{2n+2}(BG)$, which we just summarized in the previous proposition, vanishes
Explicitly, this is the component $-\ch_{n+1}(\T_{B\lie{g}}) = - \ch_{n+1}^G(\lie{g}_{ad})$.

The following is a consequence of proposition \ref{prop:mixedRR}.
\begin{prop}\label{prop:Tgauge}
Suppose $\ch_{n+1}(\T_{B\lie{g}}) = 0$.
The anomaly to lifting $S^{\cT}$ to a quantum $\cT$-background is represented by the class
\begin{multline}
\label{eqn:Tgauge}
- \left. \op{Td} \cdot \op{ch}^G(\lie{g}^{ad}) \right|_{2n+2}^\star = - \sum_{j=1}^{n} \Td_{j} \ch_{n+1-j} (\T_{B \lie{g}}[1]) \\
\in \oplus_{j} H^{2j}(BGL(n)) \otimes H^{2n+2-2j}(BG) \subset H^{2n+2}(BGL(n) \times BG) 
\end{multline}
where the $\star$ indicates that we do not include the component $\Td_{2n+2}$.
\end{prop}

The reason we have not included the term $\Td_{2n+2}$ is that this term represents the anomaly to having an inner $\cT$-action, which is only well-defined once the above class vanishes.
It is very rare that pure holomorphic $BF$ theory admits a quantum $\cT$-background; the above anomaly conditions are very restrictive.
We obtain many examples however, once we include matter.
We will detail an explicit example motivated by four-dimensional supersymmetry in the next section, but for now we state the general result.

Suppose that $V$ is a $G$-equivariant natural holomorphic vector bundle on $X$.
Examples of such bundles include $K_X^{\otimes \lambda} \otimes U$ where $U$ is a $G$-representation.
In particular, on $X = \C^n$, we can consider its $GL(n) \times G$-character
\begin{equation}
\op{ch}^{GL(n) \times G} (V) \in H^\bu(GL(n) \times G) .
\end{equation}

We consider coupling to holomorphic $BF$ theory for the Lie group $G$ the following holomorphic matter system valued in $V$.
The fields, in the BV formalism, are
\begin{equation}
\gamma \in \Omega^{0,\bu}(X, V)
\end{equation}
together with the conjugate field $\beta \in \Omega^{n,\bu}(X, V)[n-1]$.
The total action functional is 
\begin{equation}
\int_X B F_A + \int_X \beta \dbar_A \gamma
\end{equation}
where $\dbar_A = \dbar + A$.
We refer to this as holomorphic BF theory coupled to the $\beta \gamma$ system with values in $V$.
The classical $\cT$-background is 
\begin{equation}
S^\cT = \int_X B (L_\mu A)  + \int_X \beta (L_\mu \gamma) .
\end{equation}
The proof of the proposition below combines the results above.

\begin{prop}
\label{prop:coefficients}
Holomorphic BF theory coupled to the $\beta \gamma$ system with values in $V$ on $\C^n$ is anomalous at one-loop in perturbation theory.
The invariant representing this anomaly is
\begin{equation}\label{eqn:anomalycoefficients}
\ch^G_{n+1} (V) - \ch^G_{n+1}(\lie{g}^{ad}) \in H^{2n+2} (BG) .
\end{equation}

Suppose the invariant \eqref{eqn:anomalycoefficients} vanishes.
The anomaly to lifting $S^{\cT}$ to a quantum $\cT$-background is represented by the class
\begin{equation}
\label{eqn:Tcoefficients}
\left. \op{Td} \cdot \left(\op{ch}^{GL(n) \times G}(V) - \op{ch}^G(\lie{g}^{ad}) \right) \right|_{2n+2}^\star 
\in H^{2n+2}(BGL(n) \times BG) 
\end{equation}
where the $\star$ indicates that we do not include the component in $H^{2n+2}(BGL(n))$.

Suppose the invariant \eqref{eqn:Tcoefficients} vanishes.
Then the $\cT$-central charge of the system is 
\begin{equation}
\left. \op{Td} \cdot \left(\op{ch}^{GL(n) \times G}(V) - \op{ch}^G(\lie{g}^{ad}) \right) \right|_{2n+2} \in H^{2n+2} (BGL(n)) .
\end{equation}
\end{prop}

\subsection{Compactification}

Suppose we have a holomorphic theory defined on $\C^n \times X$ where $X$ is some compact complex manifold of dimension $m$.
Then, we obtain a holomorphic theory on $\C^n$ via compactification along $\C^n \times X \to \C^n$.
We turn to the problem of characterizing the $\cT_{\C^n}$-anomaly polynomial from the anomaly polynomial in $n+m$ dimensions.

Recall that the space of anomalies in $(n+m)$-dimensions is
\begin{equation}
H^1_{loc}(\cT_{\C^{n+m}}) = H^{2n+2m+1}(\lie{vect}(n+m)) = H^{2n+2m+2}(BU(n+m)) .
\end{equation}
Let $X$ be a compact $m$-dimensional manifold, then we have the composition
\begin{equation}
\begin{tikzcd}
H^{2n+2m+2} (BU(n+m)) \ar[d,equal] \ar[r] & H^{2n+2m+2}(BU(n) \times BU(m)) \ar[r] & H^{2n+2}(BU(n)) \ar[d,equal] \\ 
H^{1}_{loc}(\cT_{\C^{n+m}}) \ar[rr,dotted,"\int_X"] & & H^{1}_{loc}(\cT_{\C^{n}}) .
\end{tikzcd}
\end{equation}
The first map on the top line is induced from the block diagonal $U(n) \times U(m) \to U(n+m)$ and the second map restricts along the tangent classifier $X \to BU(m)$ and then integrates along $X$.
We denote this composition by $\int_X$.

\begin{prop}
If $\Theta$ is the anomaly to a quantum $\cT$-background on $\C^n \times X$ then $\int_X \Theta$ is the anomaly to a quantum $\cT$-background on $\C^n$.
\end{prop}

As an example, consider the basic higher dimensional $\beta \gamma$ system on $\C \times \Sigma$ where $\Sigma$ is a Riemann surface. 
The fields are 
\begin{align*}
\gamma & \in \Omega^{0,\bu}(\C \times \Sigma) \\
\beta & \in \Omega^{2,\bu}(\C \times \Sigma)[1]  .
\end{align*}
The compactification along $\Sigma$ is simply the ordinary $\beta \gamma$ system on $\C$ with values in the graded vector space $H^\bu(\Sigma, \cO)$\footnote{More accurately, this is the two-dimensional bosonic $\beta\gamma$ system with values in $H^0(\Sigma, \cO)$ coupled to the two-dimensional fermionic $bc$ system with values in $H^1(\Sigma, \cO)$.}, whose fields are
\begin{align*}
\gamma_{2d}& \in \Omega^{0,\bu}(\C) \otimes H^\bu(\Sigma, \cO) \\
\beta_{2d} & \in \Omega^{1,\bu}(\C) \otimes H^{\bu}(\Sigma, K) [1]  .
\end{align*}
In particular, the the $\cT_{\C}$ anomaly polynomial is simply
\begin{equation}
\chi^{hol}(\Sigma,\cO) \cdot \frac{1}{12} c_1^2 \in H^{4}(BU(1)) ,
\end{equation}
where $\chi^{hol}(\Sigma, \cO)$ is the holomorphic Euler characteristic.

On the other hand, we have seen that the universal anomaly on $\C^2$ for this higher dimensional $\beta\gamma$ system is simply
\begin{equation}
\op{Td}|_{6} = - \frac{1}{24} \op{ch}_1 \op{ch}_2 + \frac{1}{48} \op{ch}_1^3 \in H^6(BU(2)) .
\end{equation}
Now, $\int_\Sigma \op{ch} = 1 + \op{ch}_1 + \int_\Sigma c_1(\Sigma)$ where $c_1(\Sigma)$ is the first Chern class of the tangent bundle of $\Sigma$, and $\int_\Sigma \op{ch}_2 = \frac12 \op{ch}_1^2$.
Since $\chi^{hol}(\Sigma, \cO) = \frac12 \int_\Sigma c_1(\Sigma)$ we have
\begin{equation}
\int_\Sigma \op{Td}|_6 = - \frac{1}{24} \cdot \frac{1}{2} \int_\Sigma c_1(\Sigma) \op{ch}_1^2 + \frac{1}{48} \cdot 3 \cdot \int_{\Sigma} c_1(\Sigma) \ch_1^2 = \frac{1}{12} \chi^{hol}(\Sigma, \cO) \ch_1^2 \in H^4(BU(1)) . 
\end{equation}

\section{Relationship to the $a,c$ anomalies}
\label{s:rsymmetry}

Most of the work up until now held in arbitrary complex dimension.
Now we specialize to complex dimension two, and specifically to holomorphic quantum field theories obtained from twisting four-dimensional superconformal theories.

As reviewed in the introduction, to a four-dimensional conformal theory one associates two invariants.
These are the coefficients $c$ of (Weyl)$^2$ and $a$ of (Euler) in the conformal anomaly $\<T_\mu^\mu\>$.

A four-dimensional \textit{super}conformal theory is, in part, a theory which has a symmetry by the four-dimensional superconformal algebra. 
There are variants of this algebra depending on the amount of supersymmetry, but in this section we will only need the minimal $\cN=1$ supersymmetric version.
In particular, being superconformal means that the theory has a symmetry by the so-called $R$-symmetry group $U(1)$ which commutes with supersymmetry (and conformal transformations).
Crucially, for this section, in such a four-dimensional superconformal theory, the coefficients $a,c$ are related to certain coefficients in the $R$-symmetry anomaly which we recall momentarily.

This paper concerns holomorphic quantum field theories.
To any four-dimensional supersymmetric theory there is a twist (unique up to $R$-symmetry, if it exists) which renders the theory holomorphic \cite{CostelloHol,CostelloYangian,ESW}. 
A natural question is: what structure does the holomorphic twist of a \textit{superconformal} field theory posess?
The answer to this question is one of the main results of \cite{SWsuco}.

\begin{thm}[\cite{SWsuco}]
Suppose $\sfT$ is the holomorphic twist of four-dimensional $\cN=1$ superconformal theory of Yang--Mills type.\footnote{By this, we mean a theory consisting of some number of chiral and vector multiplets with both gauge interactions and possibly a superpotential.
In particular this is not just \textit{pure} gauge theory as there are possibly matter fields as well.}
Then $\sfT$ admits a classical $\cT$-background.
\end{thm}

In other words, the holomorphic twist of a $\cN=1$ superconformal theory admits a symmetry by holomorphic vector fields.
In this sense, we argue in \cite{SWsuco} that the Lie algebra of holomorphic vector fields is an enhanced twisted superconformal algebra.

The main result of this section shows how the coefficients $a,c$ of the supersymmetric theory relate to the $\cT$-equivariant anomaly polynomial of the holomorphically twisted theory.

\begin{thm}
\label{thm:ac}
Consider the holomorphic twist of a four-dimensional superconformal theory on~$\R^4$ of Yang--Mills type and let $a,c$ be the gravitational anomaly coefficients of this supersymmetric theory.
The anomaly polynomial for $\cT$-equivariant quantization of the holomorphic twist is 
\begin{equation}\label{eqn:acholTheta}
\Theta = \frac23 (a-c) \ch_1 \ch_2 + \frac19 \left(c - \frac{5}{3} a\right) \ch_1^3 .
\end{equation}
\end{thm}

In other words, there is the following relation involving the holomorphic anomalies $a^{hol},c^{hol}$ (see equation \eqref{eqn:achol}):
\begin{align*}
a^{hol} &= \frac23 (a-c) \\
c^{hol} &= \frac{1}{9} \left(c - \frac53 a\right) 
\end{align*}
Alternatively, the expression for $a,c$ in terms of $a^{hol},c^{hol}$ is
\begin{equation}\label{eqn:fromhol}
\begin{aligned}
a & = - \frac{9}{4} \left(a^{hol} + 6 c^{hol} \right) \\
c & = - \frac{3}{4} \left(5 a^{hol} + 18 c^{hol} \right) .
\end{aligned}
\end{equation}

\subsection{$R$-symmetry and twisting data}

A four-dimensional superconformal theory is, in particular, a theory with $R$-symmetry.
The minimal amount of $R$-symmetry is with respect to the group $U(1)$, which we denote by $U(1)_R$ when speaking of $R$-symmetry.

Let $R$ be the generator of the $U(1)_R$-symmetry in the original supersymmetric theory.
We will utilize the following well-known relationship between the $a,c$ coefficients of the anomaly polynomial and the $R$-symmetry, see \cite{Anselmi:1997ys,Anselmi:1997am}:
\begin{equation}\label{eqn:ac1}
\begin{aligned}
a & = \frac{3}{32} \left(3 \op{Tr} R^3 - \op{Tr} R \right) \\
c & = \frac{1}{32} \left(9 \op{Tr} R^3 - 5 \op{Tr} R\right) .
\end{aligned}
\end{equation}
For standard multiplets, the $R$-charges appearing in the above formulas are those of the chiral fermions in the theory.
In terms of the anomaly polynomial for mixed gravitational and $R$-symmetry (in this case, $U(1)_R$) the coefficients $(\op{Tr} R^3), (\op{Tr} R)$ appear as
\begin{equation}\label{eqn:R-symmetryanomaly}
\Theta^{\cN=1} = \frac{1}{3!} \left( (\op{Tr} R^3) \til c_1^3 - \frac14 (\op{Tr} R) \til c_1 p_1\right)
\end{equation}
where $\til c_1$ is the generator of $H^2(BU(1)_R)$ and $p_1 \in H^4 (BSO(4))$ is the universal first Pontryagin class, which we have normalized with a factor of $-1/4$ to fit with physics conventions.
Our goal is to relate these coefficients to objects in the holomorphic twist.

Generally speaking, the operation of `twisting' a supersymmetric theory involves the following steps.
Throughout, we fix a supersymmetry algebra together with an $R$-symmetry group $G_R$.
\begin{enumerate}
\item Find a supercharge $Q$, which is square zero.
That is, $Q$ is an odd element of the supersymmetry algebra which satisfies $[Q,Q] = 0$.
\item Find a `grading homomorphism' $\alpha\colon U(1) \to G_R$, where $G_R$ is the $R$-symmetry group. 
The supercharge $Q$ must be weight one with respect to this homomorphism.
\item Find a `twisting homomorphism'.
This amounts to choosing a Lie group $G$, together with homomorphisms $\iota \colon G \to Spin(n)$ and $\phi \colon G \to G_R$ with the property that $Q$ is $G$-invariant with respect to the induced homomorphism $\iota \times \phi \colon G \to Spin(n) \times G_R$.
\end{enumerate}

The four-dimensional $\cN=1$ supersymmetry algebra has an essentially unique supercharge which is square-zero \cite{EStwist}.
Any other supercharge is in the same $R$-symmetry orbit.
We fix such a supercharge $Q^{hol}$.
This supercharge is \textit{holomorphic}, in the sense that the rank of the map $[Q^{hol},-]$ is two (half the dimension of spacetime).
For more details on twisting we refer to \cite{CostelloHol,ESW,SWchar}.

\begin{prop}
\label{prop:twist}
Consider a free supersymmetric theory on $\R^4$ built from chiral and vector multiplets with $R$-symmetry generator $R = (r_i)$ where $r_i$ is the $R$-charge of the $i$th multiplet.
Our convention is that for chiral (respectively, vector) multiplets, the scalar (respectively gauge) field has $R$-charge $r_i+1$ (respectively, $r_i-1$).

Then, there exists twisting data such that the holomorphic twist of of this theory is equivalent to the cotangent theory (in the BV sense) to
\begin{equation}
\oplus_i \Omega^{0,\bu}(\C^2, K^{(r_i+1)/2}) .
\end{equation}
\end{prop}

As an example, consider a single free vector multiplet with its standard $R$-charge $r = 1$ (so that the gauge field in the multiplet has vanishing $R$-charge $R(A) = 0$).
This lemma implies that the holomorphic twist is the cotangent theory to $\Omega^{0,\bu}(\C^2,K) = \Omega^{2,\bu}(\C^2)$ which consists of fields 
\begin{equation}
(B,A) \in \Omega^{2,\bu}(\C^2) \oplus \Omega^{0,\bu}(\C^2) [1],
\end{equation}
thus recovering the free limit of holomorphic $BF$ theory.

As another example, the $R$-charge for a single chiral multiplet which saturates the BPS bound for the superconformal algebra is $r = -\frac13$ (so that the scalar in the multiplet has $R$-charge $R(\phi)=\frac23$).
The holomorphic twist of this theory is the theory whose underlying space of BV fields is 
\begin{equation}
(\gamma, \beta) \in \Omega^{0,\bu}(\C^2, K^{1/3}) \oplus \Omega^{0,\bu}(\C^2, K^{2/3})[1] ,
\end{equation}
and action is $\int \beta \dbar \gamma$.
This is the two-dimensional $\beta\gamma$ system twisted by $K^{1/3}$.

\begin{proof}[Proof of theorem \ref{thm:ac}]
To compute the $\cT$-anomaly it suffices to consider the underlying free theory, hence we can appeal to proposition \ref{prop:twist}.

From \eqref{eqn:ac1} we have the following relation between the $R$-symmetry generator and the gravitational anomaly coefficients:
\begin{equation}
\op{Tr} R = 16 (a-c) , \quad \op{Tr} R^3 = \frac{16}{3} \left(\frac53 a - c\right) .
\end{equation}

From proposition \ref{prop:twist} we know that we can express the holomorphic twist as a $\beta\gamma$-system with coefficients in a sum of line bundles determined by $R$. 
Using Lemma \ref{lem:grrfree} we see that
\begin{equation}
a^{hol} = \frac{1}{24} 16 (a-c) = \frac{2}{3} (a-c) 
\end{equation}
and
\begin{equation}
c^{hol} = - \frac{1}{48} \cdot \frac{16}{3} \left(\frac53 a - c\right) = \frac19 \left(c - \frac53 a\right)
\end{equation}
as desired.

\end{proof}

There is an alternative way of deducing these holomorphic anomaly coefficients from the anomaly polynomial of the supersymmetric theory.
Indeed, we can start with the $R$-symmetry anomaly polynomial of the untwisted theory in equation \eqref{eqn:R-symmetryanomaly} and proceed with the following two steps: first, break $SO(4)$ to $MU(2)$ and second, twist by setting $\til c_1 = -\frac12 \op{ch}_1$.
The first step has the effect of setting $p_1 \mapsto 2 \op{ch}_2$ (this is the induced homomorphism $H^4(BSO(4)) \to H^4(BU(2))$ and the second step follows from the standard twisting homomorphism for four-dimensional supersymmetry, see \cite{ESW}.

%
%For $\cN=4$ supersymmetric Yang--Mills theory we know that
%\begin{equation}
%(a,c)_{\cN=4} = \left(\frac14, \frac14\right) .
%\end{equation}

\subsection{Anomalies for basic supersymmetric theories}

We unpack the anomaly polynomial for basic four-dimensional supersymmetric gauge theories.
The results, including anomalies for theories with more supersymmetry, are summarized in table \ref{tab:basic}.

\begin{table}
\centering
\begin{tabular}{ |c|c|c|c|c|c|}
 \hline
  $\cN$ & multiplet & $a$ & $c$ & $a^{hol}$ & $c^{hol}$ \\
 \hline
 \hline
 $\cN=1$   & vector   & $\frac{3}{16}$ & $\frac{1}{8}$ & $\frac{1}{24}$ & $-\frac{1}{48}$ \\
 & chiral &   $\frac{1}{48}$  & $\frac{1}{24}$   & $-\frac{1}{72}$ & $\frac{1}{1296}$ \\
 \hline
 $\cN=2$ &  vector  & $\frac{5}{24}$   & $\frac{1}{6}$ & $\frac{1}{36}$ & $-\frac{13}{648}$ \\
  & hyper & $\frac{1}{24}$ &  $\frac{1}{12}$ & $-\frac{1}{36}$ & $\frac{1}{648}$ \\ 
  \hline
  $\cN=4$  & vector & $\frac14$ & $\frac14$ & $0$ & $-\frac{1}{54}$ \\
 \hline
\end{tabular}
\caption{A list of $a,c$ and $a^{hol},c^{hol}$ for basic supersymmetric gauge theories and their twists.}
\label{tab:basic}
\end{table}

\subsubsection{$\cN=1$ gauge theory}

In $\cN=1$ gauge theory there are vector multiplets and chiral multiplets.
We have described the twist of the superconformal vector and chiral multiplet after the statement of proposition \ref{prop:twist}.
To compute the coefficients $a^{hol},c^{hol}$ we could refer to the formula \eqref{eqn:acholTheta}.
Instead, we will compute the coefficients directly from the Riemann--Roch theorem.

In fact, we have already done this.
The anomaly polynomial for the chiral multiplet is obtained by plugging $\lambda = \frac13$ into the coefficients of lemma \ref{lem:grrfree}.
Similarly, the anomaly polynomial for a single vector multiplet is obtained as the negative of the coefficients in proposition \ref{lem:grrfree} when $\lambda = 0$.
The sign arises because this is a gauge theory.

Translating back to the physical coefficients as in equation \eqref{eqn:fromhol} we obtain the expected values of $a,c$ \cite{Duff}.

\subsubsection{$\cN=2$ gauge theory}

We focus on two multiplets relevant for four-dimensional $\cN=2$ supersymmetric gauge theory.
The first is the vector multiplet, which is defined from the data of a Lie group $G$ and a principal bundle, which we take to be trivial.
The second is the hypermultiplet, which depends on the choice of a representation $R$ of $G$.

In the BV formalism, the holomorphic twist of pure gauge theory is holomorphic $BF$ theory for the holomorphic local Lie algebra whose underlying holomorphic vector bundle is 
\begin{equation}
\lie{g} \otimes \wedge^\bu K^{1/3} = \lie{g} \oplus \Pi \lie{g} \otimes K^{1/3} .
\end{equation}
The Lie algebra structure is determined by the Lie bracket on $\lie{g}$.
Note that
\begin{equation}\label{eqn:wedgeK13}
\ch\left(\lie{g}[1] \otimes \wedge^\bu K^{1/3} \right) = \left(- \frac13 \ch_1 + \frac{1}{18} \ch_1^2 - \frac{1}{162} \ch_1^3 \right) \dim G .
\end{equation}
Thus
\begin{equation}
\Td \ch\left(\lie{g}[1] \otimes \wedge^\bu K^{1/3} \right)|_6 = \left(\frac{1}{36} \ch_1 \ch_2 - \frac{13}{648} \ch_1^3 \right) \dim G .
\end{equation}
(Alternatively, note that as $\cN=1$ multiplets a $\cN=2$ vector is the same as a $\cN=1$ vector plus a $\cN=1$ chiral).

The hypermultiplet is the cotangent theory to 
\begin{equation}
R \otimes \wedge^\bu K^{1/3} \otimes K^{1/3} = R \otimes K^{1/3} \oplus \Pi R \otimes K^{2/3},
\end{equation}
From this we see that the anomaly polynomial for the hypermultiplet valued in $R$ is
\begin{equation}
\left(-\frac{1}{36} \ch_1 \ch_2 + \frac{1}{648} \ch_1^3 \right) \dim R .
\end{equation}

Translating back to the physical coefficients as in equation \eqref{eqn:fromhol} we obtain the expected values of $a,c$ \cite{Duff}.

\subsubsection{$\cN=4$ gauge theory}
Consider four-dimensional $\cN=4$ supersymmetric gauge theory for gauge group~$G$ near the trivial $G$-bundle.
In the BV formalism, the holomorphic vector bundle underlying the holomorphic twist of this theory is
\begin{equation}
\lie{g}[1] \otimes \wedge^\bu\left(K^{1/3} \otimes \C^3\right) . 
\end{equation}
Notice that in the cohomology of $BGL(2)$ we have the formal expression
\begin{equation}
\ch(K^{\lambda/3}) = 1 - \frac{\lambda}{3} \ch_1 + \frac{\lambda^2}{2 \cdot 3^2} \ch_1^2 - \frac{\lambda^3}{3! \cdot 3^3} \ch_1^3 . 
\end{equation}
where $\lambda$ is any integer.
From this we compute
\begin{align*}
\ch \wedge^\bu\left(K^{1/3} \otimes \C^3\right) & = 1 - 3 \ch (K^{1/3}) + 3 \ch (K^{2/3}) - \ch(K) \\
& = \frac{1}{27} \ch_1^3 .
\end{align*}

Thus, we see directly that for $\cN=4$ supersymmetric Yang--Mills theory we have $a^{hol} = 0$ and 
\begin{equation}
c^{hol} = -\frac{1}{2 \cdot 27} \dim G = -\frac{\dim G}{54} .
\end{equation}

Translating back to the physical coefficients as in equation \eqref{eqn:fromhol} we obtain the expected values of $a,c$ \cite{Duff}.

\section{Anomaly matching in holomorphic QCD}
\label{s:qcd}

In this section we consider anomalies in the holomorphic twist of four-dimensional $\cN=1$ supersymmetric quantum chromodynamics (QCD).

\subsection{The holomorphic theory}

Four-dimensional $\cN=1$ supersymmetric Yang--Mills theory depends on a choice of compact Lie group $G$, with complexified Lie algebra $\fg$, and a representation $\bV$ that comprises the supersymmetric matter.
%The field content of the theory on a spin Riemannian four-manifold $M$~is
%\begin{itemize}
%\item a  that consists of a gauge field $A \in \Omega^1(M) \otimes \fg $ together with fermions $\lambda \in \Gamma(M,S) \otimes \fg$, and
%\item a {\it matter multiplet} (often called the chiral multiplet), depending on a choice of a complex representation $V$ of $\fg$, that consists of a scalar $\phi \in C^\infty(M) \otimes V$ together with fermions $\psi \in \Gamma(M,S) \otimes V$. 
%Additionally, one can turn on a {\it superpotential} $W \in \cO(V)^\fg$, a $G$-invariant polynomial on~$V$. 
%\end{itemize}

Typically, in supersymmetric QCD one takes $G = SU(N_c)$ and 
\begin{equation}
\bV = (\C^{N_c})^{\oplus N_f} \oplus (\br \C^{N_c})^{\oplus N_f}
\end{equation}
where $\C^{N_c}$ (respectively, $\br \C^{N_c}$) denotes the fundamental (respectively, anti-fundamental)  $SU(N_c)$ representation.
One says that $N_c$ is the number of `colors' and $N_f$ is the number of `flavors'.

In the $\cN=1$ supersymmetry algebra there is (up to equivalence) a unique twisting supercharge.

\begin{thm}[\cite{CostelloYangian,ESW,SWchar}]
The twist of four-dimensional $\cN=1$ supersymmetric Yang--Mills theory on $\R^4$ associated to the pair $(G,\bV)$ is equivalent to holomorphic BF theory on $\C^2$ with gauge group $G_\C$ coupled to the holomorphic $\beta\gamma$ system on~$\C^2$ valued in~$\bV$.

If the supersymmetric theory is equipped with a superpotential $W$, then there is a holomorphic superpotential in the twisted theory, see below.
\end{thm}

Following this theorem, we arrive at the holomorphic version of supersymmetric QCD obtained from the previous theorem as the twist of supersymmetric QCD with $N_c$ colors and $N_f$ flavors.
Explicitly, this the holomorphic theory whose fields are:
\begin{itemize}
\item the gauge fields are those of holomorphic $BF$ theory valued in $\lie{sl}(N_c)$, whose fields are
\[
A \in \Omega^{0,\bu}(\C^2 , \lie{sl}(N_c))[1] \quad\text{and}\quad B \in \Omega^{2,\bu}(\C^2, \lie{sl}(N_c)^*);
\]
\item the ``quarks'' are fields of a holomorphic $\beta\gamma$ system valued in 
\[
V = (\C^{N_c})^{N_f},
\] 
where $\C^{N_c}$ is the fundamental $SU(N_c)$ representation whose fields are
\[
\gamma \in \Omega^{0,\bu}(\C^2, V) \quad\text{and}\quad \beta^\dag \in \Omega^{2,\bu}(\C^2 , V^*)[1];
\]
\item the ``antiquarks'' are fields of a holomorphic $\beta\gamma$ system valued in the dual representation 
\[
V^* \cong (\br \C^{N_c})^{N_f},
\]
where $\br \C^{N_c}$ is the anti-fundamental $SU(N_c)$ representation whose fields are
\[
\gamma^\dag \in \Omega^{0,\bu}(\C^2 , V^*) \quad\text{and}\quad \beta \in \Omega^{2,\bu}(\C^2 , V) [1].\footnote{The superscript $\dag$ does not refer to adjoint here.}
\]
\end{itemize}

The action functional is
\[
S_{QCD} = \int B F_A + \int \beta^\dag \dbar_A \gamma + \int \beta \dbar_A \gamma^\dag,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.

If, additionally, the supersymmetric theory is equipped with a superpotential $W$, then there is a term in the holomorphic action
\begin{equation}
\int \d^2 z \, W(\gamma) = \int \d^2 z \, \left(\frac12 W''(\gamma^0) \gamma^{0,1} \gamma^{0,1} + W'(\gamma^0) \gamma^{0,2}\right) .
\end{equation}
Notice that this depends on the choice of a holomorphic volume form and does not define a theory with a cohomological $\Z$-grading.
Both of these drawbacks stem from the fact that the superpotential breaks $R$-symmetry in the original supersymmetric theory.
%We will denote this theory by $\cT(N,F)$.

In the above description we have described the fields on flat space.
Even on flat space, a $\cT$-background will depend on which bundle the quark fields transform under.
For example, for a single superconformal chiral multiplet, the field $\gamma$ is twisted by the line bundle $K^{1/3}_{\C^2}$.

For holomorphic QCD we will do something more general.
We suppose that $\gamma$ (and $\gamma^\dag$) transform as sections of $K^{\otimes \lambda}_{\C^2} \otimes V$ (and $K^{\otimes \lambda}_{\C^2} \otimes V^*$) where $\lambda$ is some rational number.
From section \ref{s:rsymmetry}, recall that this corresponds to the twist of a chiral multiplet with $r = 2 \lambda - 1$.

The $\cT$-background is 
\begin{equation}\label{eqn:Tr}
I^{\cT,r} = \int B L_\mu A + \int \beta^\dagger L_\mu \gamma + \int \beta L_\mu \gamma^\dagger .
\end{equation}
With respect to the standard coordinates $\mu = \mu_i (z) \del_{z_i}$ and this coupling reads
\begin{equation}
I^{\cT,r} = \int B \mu_i \del_{z_i} A + (1-r) \int \beta^\dagger \mu_i \del_{z_i} \gamma + (1-r) \int \beta \mu_i \del_{z_i} \gamma^\dag + r \int \del_{z_i} \mu_i (\beta^\dagger \gamma + \beta \gamma^\dagger) .
\end{equation}

%\begin{lem}
%Let $\til \gamma = \gamma (\d^2 z)^{\otimes r}$ and $\til \beta = \frac{\del}{\del (\d^2 z)} (\beta) (\d^2 z)^{1-r}$ and similarly for $\til \gamma^\dagger,\til \beta^\dagger$.
%Then
%\begin{equation}
%I^{\cT,r}(A,B,\beta, \gamma, \beta^\dagger,\gamma^\dagger) = I^{\cT} (A,B,\til \beta, \til\gamma, \til\beta^\dagger,\til\gamma^\dagger) .
%\end{equation}
%\end{lem}
%\begin{proof}
%This follows from the formula for the Lie derivative
%\begin{equation}
%L_\mu (\gamma (\d^2 z)^r) = \left((1-r) \mu_i \del_{z_i} \gamma + r \del_{z_i} \mu_i \gamma\right) (\d^2 z)^r .
%\end{equation}
%\end{proof}
%
%This lemma implies that the generalized coupling $I^{\cT,r}$ is the standard coupling $I^{\cT}$ for the theory whose fields are `twisted' by certain powers of the canonical bundle; namely $\til \gamma \in \Omega^{0,\bu} (\C^2, K^{\otimes r})$, etc..

\subsection{There are no gauge anomalies}

Consider holomorphic QCD with gauge group $SU(N_c)$ and~$N_f$ flavors valued in the fundamental representation.
First we consider the internal anomalies.
For pure $\lie{sl}(N_c)$ holomorphic gauge theory is no pure gauge anomaly as $\op{Tr}_{adj}(X^3) = 0$ for any $X \in \lie{sl}(N_c)$, see proposition \ref{prop:puregauge}.
The mixed gauge-matter anomalies vanish since the matter comprises an equal number of fundamental and anti-fundamental representations.

\subsection{Anomaly to a quantum $\cT$-background}
\label{sec:TbackgroundQCD}

Next we consider the anomaly to having background of holomorphic vector fields $\cT$ using the generalized coupling $I^{\cT,r}$ from equation \eqref{eqn:Tr}.
We find an exact agreement with the anomaly cancelation for the $R$-symmetry current in supersymmetric QCD.

\begin{prop}
Holomorphic QCD admits a quantum $\cT$-background with classical coupling~$I^{\cT,r}$ if and only if
\begin{equation}
r = - \frac{N_c}{N_f} ,
\end{equation}
equivalently, $\lambda = \frac12 (1-\frac{N_c}{N_f})$.
\end{prop}
\begin{proof}
This is a consequence of proposition \ref{prop:coefficients}.
The graded holomorphic vector bundle underlying holomorphic QCD is 
\begin{equation}
V_{QCD} = \lie{g}[1] \oplus K^{\otimes \lambda} \otimes V \oplus K^{\otimes \lambda} \otimes V^* .
\end{equation}
In the expansion of \eqref{eqn:Tgauge} we see that since the gauge group is simple, the only the terms in anomaly live in
\begin{equation}
H^2(BGL(2)) \otimes H^4(B G) ,
\end{equation}
where here $G = SU(N_c)$.
Explicitly, this is the term
\begin{equation}\label{eqn:td0td1}
\op{Td}_0 \ch_3^{GL(2) \times G}(V_{QCD}) + \op{Td}_1 \ch_2^{G}(V_{QCD}) .
\end{equation}

Using the form of $V_{QCD}$ above, we see that the first term in equation \eqref{eqn:td0td1} is
\begin{equation}
2 F \ch_2(K^{\otimes \lambda}) = - 2\lambda F \ch_1 \op{ch}^G_2(fun) .
\end{equation}
We have used the relation $\op{ch}_1(K^{\otimes \lambda}) = - \lambda \ch_1$ where, as usual, $\op{ch}_1$ is the standard generator of $H^2(BGL(2))$. 
The factor of two comes from the fact that we have quarks and anti-quarks.

Likewise, the second term in \eqref{eqn:td0td1} is
\begin{equation}
\frac{1}{2} \ch_1 \left(-\op{ch}^G_2(adj) + \cdot 2 F \cdot \ch_2^G(fun)\right) .
\end{equation}

In total we see that the anomaly to a quantum $\cT$-background is
\begin{equation}
\ch_1 \left(-\frac12 \ch_2^{G}(adj) + 2 \left(-\lambda + \frac12\right) F \ch_2^{G}(fun) \right).
\end{equation}
For any $X \in \lie{sl}(N_c)$ we have the relation $\op{Tr}_{adj}(X^2) = 2 N_c \op{Tr}_{fun}(X^2)$.
In other words, for $G = SU(N_c)$, we have $\op{ch}_2^G(adj) = 2 N_c \op{ch}_2^G(fun)$. 
Using this relation, the result follows.
%%that the wheels with two legs labeled by the gauge field $A$ and one leg labeled by a vector field $\mu$ vanish.
%Indeed, the total contribution of the anomaly is
%\begin{equation}
%-\int \op{tr}(J \mu) \op{Tr}(\del A \del A) + 2 N_f (1-r) \int \op{tr}(J \mu) \op{tr}(\del A \del A) = 0 .
%\end{equation}
%The first term comes from the contribution of the gauge propagators; using the Riemann-Roch theorem it corresponds to the universal class $- c_1 \cdot \ch_2(\T_{B G})$, where $G  = SU(N_c)$ here.
%The second term comes from the contribution of the matter propagators and corresponds to the class $c_1 \cdot \ch_2(V_Q + V_Q^*)$.
%Anomaly cancellation then requires 
%\begin{equation}
%- N_c (N_c^2 - 1) + 2 N_f \frac{N_c^2 - 1}{2 N_c} N_c (1-r) = 0 ,
%\end{equation}
%which completes the proof.
\end{proof}

\subsection{$a,c$ for QCD}

We are now in a position to compute the values of $a^{hol},c^{hol}$ for holomorphic QCD.
As always, this only depends on the underlying holomorphic vector bundle of holomorphic QCD
\begin{equation}
V_{QCD} = \ul{\lie{g}}[1] \oplus K^{\otimes \lambda} \otimes V \oplus K^{\otimes \lambda} \otimes V^* ,
\end{equation}
where, as we found in the last section, one has $\lambda = \frac12 (r+1) = \frac12 \left(1 - \frac{N}{F}\right)$ in order to guarantee anomaly cancellation for the $\cT$-background.

According to this decomposition, the $a^{hol}$ coefficient decomposes as $a^{hol}_{QCD} = a^{hol}_{gauge} + a^{hol}_{quark} + a^{hol}_{anti-quark}$, and similarly for $c^{hol}$.
Notice that $a^{hol}_{quark} = a^{hol}_{anti-quark}$ and $c^{hol}_{quark} = c^{hol}_{anti-quark}$ as they transform identically under the action of holomorphic vector fields.
We read these coefficients directly.

First
$a^{hol}_{gauge} = \frac{1}{24} \dim \lie{g} = \frac{1}{24} \left(N_c^2 -1\right)$,
as read off from table \ref{tab:basic}.
From lemma \ref{lem:grrfree} we see
\begin{equation}
a^{hol}_{quark} = \frac{1}{24} \left(- \frac{N_c}{N_f} \right) \dim V = - \frac{1}{24} N_c^2 .
\end{equation}
Thus in total we see that
\begin{equation}\label{eqn:aqcdhol}
a^{hol}_{QCD} = - \frac{1}{24} \left(N_c^2 + 1\right)
\end{equation}
Interestingly, this is independent of the number of flavors $N_f$.

Similarly, from table \ref{tab:basic}, $c^{hol}_{gauge} = -\frac{1}{48} \dim \lie{g} = - \frac{1}{48} (N^2 - 1)$,
and from \ref{lem:grrfree} we see
\begin{equation}
c^{hol}_{quark} = - \frac{1}{48} \left(- \frac{N_c}{N_f}\right)^3 \dim V = \frac{1}{48} \frac{N_c^4}{N_f^2} .
\end{equation}
Thus
\begin{equation}\label{eqn:cqcdhol}
c^{hol}_{QCD} = \frac{1}{48N_f^2}\left(2N_c^4 - N_c^2 N_f^2+N_f^2\right).
\end{equation}

Plugging into equation \eqref{eqn:fromhol} we recover the expected physical values for these coefficients
\begin{align*}
a_{QCD} & = -\frac{3}{16 N_f^2} \left(3N_c^4-2N_c^2 N_f^2+N_f^2\right) \\
c_{QCD} & = - \frac{1}{16 N_f^2} \left(9 N_c^4 - 7 N_c^2 N_f^2 + 2 N_f^2 \right) .
\end{align*}

\subsection{Magnetic anomalies}

In \cite{Seiberg}, Seiberg discovered a duality in four-dimensional supersymmetric gauge theory that posits an equivalence between $\cN=1$ supersymmetric QCD for gauge group $SU(N_c)$, called the `electric' theory, and another $\cN=1$ supersymmetric QCD, called the `magnetic' theory.

The magnetic theory has gauge group $SU(N_f - N_c)$ and the matter consists of $N_f$ fundamental chiral multiplets together with $N_f^2$ `mesons' which transform trivially under the gauge group.
There is also a superpotential which we will not need so do not comment any further on.
Therefore, at the level of the holomorphic twist, the bundle underlying the magnetic dual to holomorphic QCD is thus of the form
\begin{equation}
\til V_{QCD} = \ul{\til{\lie{g}}}[1] \oplus K^{\otimes \til \lambda} \otimes \til V \oplus K^{\otimes \til \lambda} \otimes \til V^* \oplus K^{\otimes \lambda_M} \otimes \op{End}(\C^F) ,
\end{equation}
where $\til{\lie{g}} = \lie{sl}(N_f-N_c)$ and the matter is labeled by the representation $\til V = (\C^{N_f - N_c})^{N_f}$.

Since the holomorphic mesons transform trivially under $\til{\lie{g}}$ they do not contribute to any possible gauge anomalies.
In particular, we can compute the anomaly to a quantum $\cT$-background just as we did in section \ref{sec:TbackgroundQCD}.
We find that a quantum $\cT$-background exists if and only if
\begin{equation}
\til \lambda = \frac{N_c}{2 N_f},
\end{equation}
equivalently $\til r = - \frac{N_f - N_c}{N_f}$.

From this, we can proceed as above to calculate the $a,c$ anomalies for the magnetic version of QCD.
As a function of $r_M = 2\lambda_M-1$, we find
\begin{align*}
\til a^{hol}_{QCD} & = \frac{1}{24} \left(-1 + 2 N_f N_c - N_c^2 + N_f^2(r_M - 1) \right) \\
\til c^{hol}_{QCD} & = \frac{1}{48 N_f^2}\left(N_f^2 + N_f^4 - 6 N_f^3 N_c + 11N_f^2 N_c^2-8 N_f N_c^3+2N_c^4-r_M^3 N_f^4\right) .
\end{align*}

\begin{prop}
The $a,c$ anomalies match for the holomorphic twists of Seiberg dual theories
\begin{equation}
a_{QCD} = \til a_{QCD}, \quad c_{QCD} = \til c_{QCD}
\end{equation}
if and only if $r_M = 1 - \frac{2N_c}{N_f}$. 
\end{prop}
\begin{proof}
It suffices to prove the statement for the holomorphic coefficients $a^{hol},c^{hol}$. 
Immediate computation shows that $a_{QCD}^{hol}$ from equation \eqref{eqn:aqcdhol} matches with $\til a^{hol}_{QCD}$ if and only if $r_M = 1 - \frac{2N_c}{N_f}$.
Plugging this value of $r_M$ into $\til c_{QCD}^{hol}$ we find a match with equation \eqref{eqn:cqcdhol}.
\end{proof}

%\subsection{Holomorphic flavor symmetry}

%\newcommand{\sfa}{\mathsf{a}} 
%
%In addition to a classical $\cT$-symmetry, holomorphic QCD enjoys a holomorphic `flavor' symmetry \cite{GWkm}.
%In other words, exhibits a natural $\lie{sl}(N_f) \otimes \Omega^{0,\bu}(\C^2)$-background defined by the coupling
%\begin{equation}
%I^{flav} = \int \beta^\dag(\sfa \cdot \gamma) + \int \beta (\sfa \cdot \gamma^\dag) ,
%\end{equation} 
%where $\sfa \in \lie{sl}(N_f) \otimes \Omega^{0,\bu}(\C^2)$ denotes a background holomorphic gauge field.

\printbibliography

\end{document}

\appendix

\section{Local Lie algebras and their modules}

\section{Riemann--Roch polynomial in complex dimension one}

\section{Conformal anomalies}

Let $g$ be a metric.
For a positive function $\gamma >0$ we obtain a new metric by 
\begin{equation}
g \mapsto e^{2 \gamma} g .
\end{equation}
Such a transformation is called a Weyl, or conformal, transformation.
A theory which depends on a metric is said to be conformally invariant if its action functional is left invariant by the above sort of transformations.
Such a theory is equipped with a stress tensor $T$ which, classically, is traceless
\begin{equation}
\tr T = 0.
\end{equation}

Suppose we work near a fixed conformal class of metric $[g]$ on a manifold $M$.
Then, a Weyl invariant theory is one which can be put in a classical $\cL_{Weyl}^g$-background where $\cL^g_{Weyl}$ is the following local $L_\infty$ algebra.
As a complex of bundles $\cL^g_{Weyl}$ is of the form
\begin{equation}
\begin{tikzcd}
\ul{0} & \ul{1} \\
\op{Vect}(M) \ar[r,"L g"] & \op{Sym}^2(\T^*M) \\
C^\infty(M) \ar[ur,"g"] .
\end{tikzcd}
\end{equation}
The Lie bracket is so that vector fields act on everything by Lie derivative.
This local Lie algebra describes the tangent complex to the derived moduli space of conformal structures on $M$ at $[g]$.

A classical $\cL_{Weyl}^g$-background is described by a local functional $S^{Weyl}$ as above.
This is a local version of the stress energy tensor.

Let us consider an example, the free scalar field on a Riemannian manifold $(M,g)$.
The field is simply a scalar $\phi \in C^\infty(M)$ and the action functional is
\begin{equation}
S(\phi) = \frac12 \int_M \left(\phi \Delta_g \phi - \xi R_g \phi^2\right) \dvol_g .
\end{equation}
Here $\Delta_g$ is the Hodge Laplacian and $R_g$ is the scalar curvature.
A short calculation shows that when $\xi = (d-2)/4(d-1)$ this action is invariant under global Weyl transformations where the field $\phi$ transforms as
\begin{equation}
\phi (x) \mapsto e^{-(d-2)/2 \, \gamma(x)} \phi (x) .
\end{equation}

\begin{prop}
The free scalar field on $M$ admits a classical $\cL^{g}_{Weyl}$ background described by the coupling
\begin{multline}
S^{Weyl}(\phi ; X, f, \alpha) = \int_M \phi^+ (X \phi) + (d-2) \int_M \phi^+ f \phi \\
+ \frac12 \int_M \left( \phi (\Delta_{g+\alpha} - \Delta_g) \phi - \xi (R_{g+\alpha} - R_g) \phi^2 \right) \dvol_g ,
\end{multline}
where $\phi^+ \in \Omega^d(M)$ denotes the anti-field to $\phi$.
\end{prop}

\subsection{Two dimensions}

When $d=2$ the local functional representing the conformal anomaly is of the form
\begin{equation}
\frac{1}{24 \pi} \int f R .
\end{equation}

Let $\Sigma$ be a Riemann surface and $\cT_\Sigma = \Omega^{0,\bu}(\Sigma, \T^{1,0})$ the local dg Lie algebra controlling deformations of complex structures.
Let $[g]$ be the conformal class of metric corresponding to this complex structure.

\section{Junk}
\subsection{As a conserved current}

Note that
\begin{equation}
\left(\br \T^* \otimes \T\right)^! = \wedge^n \T^* \otimes \wedge^{n-1} \br \T^* \otimes \T^* .
\end{equation}
Thus, in a holomorphic theory of dimension $n$, the holomorphic stress tensor is a section
\begin{equation}
T \in \Gamma(\wedge^n \T^* \otimes \wedge^{n-1} \br \T^* \otimes \T^*) .
\end{equation}
When $n=1$ this is simply the $zz$ component of the stress tensor
\begin{equation}
T_{zz} \in \Gamma(\T^* \otimes \T^*) .
\end{equation}
When $n=2$, the holomorphic stress tensor can be written in coordinates as
\begin{equation}
T = T_{[ij] \br k \ell} \; (\d z^i \wedge \d z^j) \otimes \d \zbar^{\br k} \otimes \d z^\ell .
\end{equation}

\subsection{Improvements}

Let $X$ be a Calabi--Yau twofold with holomorphic volume form $\Omega$.
Consider the $\beta\gamma$ system defined on $X$ with free action $\int \beta \dbar \gamma$ where
\begin{align*}
\gamma & \in \Omega^{0,\bu}(X) \\
\beta & \in \Omega^{2,\bu}(X)[1] \simeq_\Omega \Omega^{0,\bu}(X)[1] .
\end{align*}
Let $W$ be a polynomial in one variable and consider the Lagrangian
\begin{equation}
I_W (\gamma) = \int \Omega \wedge W(\gamma) .
\end{equation}

\begin{lem}
The $\beta \gamma$ system with Lagrangian
\begin{equation}
S_W(\beta,\gamma) = \int \beta \dbar \gamma + I_W(\gamma)
\end{equation}
can be placed in a $\cT_X$-background with coupling
\begin{equation}
S^{\cT} (\mu ; \gamma, \beta) = \int_X \beta (\mu \vee \del \gamma) + \int_X \Omega \; \nu \, W(\gamma) .
\end{equation}
\end{lem}
\begin{proof}
We have
\begin{equation}
\d_{\cT} S^{\cT} = \frac12 \int \beta([\mu,\mu] \vee \del \gamma) + \int \Omega (\mu \vee \del \nu) W(\gamma) + \int \Omega \; \div \mu \, W(\gamma) .
\end{equation}
Next
\begin{equation}
\{S^{\cT}, S_W\} = \int (\mu \vee \del \gamma) W'(\gamma) = \int \Omega (\mu \vee \del W(\gamma)) .
\end{equation}
And finally
\begin{equation}
\frac12 \{S^{\cT}, S^{\cT}\} = \frac12 \int \beta ([\mu,\mu] \vee \del \gamma) + \int (\mu \vee \del \gamma) \nu W'(\gamma)
\end{equation}
The first term in the first line cancels with the first term in the third line.
The second term in the first line cancels with the second term in the third line.
The final term in the first line cancels with the term in the second line.
\end{proof}

\subsection{Derived supersymmetry}

\begin{thm}[\cite{Zaffaroni,..}]
\label{thm:background}
Let $(X,g)$ be a four-dimensional Riemannian manifold equipped with a spin$^c$ structure whose determinant line bundle is $\cL$.
\begin{itemize}
\item[(1)] A non-vanishing chiral spinor $\eta_+ \in \cS_+$ defines an almost complex structure on $X$.
\item[(2)] For such an $\eta_+$ there exists a $U(1)$-connection $A$ for $\cL$ compatible with the metric, unique up to a gauge transformation, such that
\begin{equation}
\eta_+ \;\; \text{is\;integrable} \quad \iff \quad \slashed{P}_A \eta_+ = 0.
\end{equation}
\end{itemize}
Such a pair $(\eta_+,A)$ determines a consistent conformal supergravity background.
\end{thm}

\begin{thm}
Let $X, \eta_+, A$ be as in theorem \ref{thm:background}.
The $\eta$-twist $\cJ^{\eta}_A$ of the infinitesimal superconformal multiplet near the $U(1)$-connection $A$ is equivalent to the local Lie algebra $\cT_X$ resolving holomorphic vector fields on $X$.
\end{thm}

\subsection{Mixed symmetries}
\label{sec:mixed1}

\brian{Flavor multiplet, then couple stress tensor}

The flavor multiplet in four-dimensional $\cN=1$ supersymmetry consists of a flavor current $j_\mu$ and its supersymmetric partners which combine into a real linear multiplet.
In total, there is an adjoint-valued vector $j = (j_\mu)$, an adjoint-valued bosonic scalar $J$, and a fermion $\mathsf{j}$ which is simply an adjoint-valued spinor.

The underlying local Lie algebra is
\begin{equation}
    \begin{tikzcd}
        & 0 & 1 \\ \hline
        even &\lie{g} \otimes C^\infty_c \ar[r,"\d"] &  \lie{g} \otimes \Omega^1_A \\
        even &  & \lie{g} \otimes C^\infty_D \\
        odd &  & \lie{g} \otimes \Gamma(S)_\lambda \\
    \end{tikzcd}
\end{equation}

\end{document}
